---
title: "Tutorial"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(ggplot2)
library(dplyr)
library(tidyr)
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction

### Agenda

<hr>

- build scatter plots
- modify point
    - color
    - fill
    - alpha
    - shape
    - size
- fit regression line


## Plot

<hr>

```{r scat2, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Scatter Plot'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg))
```

### Add Jitter

<hr>

```{r scat22, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Add Jitter'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg), position = 'jitter')
```

```{r scat3, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Add Jitter'}
ggplot(mtcars) +
  geom_jitter(aes(disp, mpg))
```

## Aesthetics

### Introduction

<hr>

Now let us modify the aesthetics of the points. There are two ways:

- map them to variables using the `aes()` function
- specify values

## Color

### Map Color to Variable (Categorical)

<hr>

```{r scat4, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Color'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, color = factor(cyl)), 
             position = 'jitter')
```

### Map Color to Variable (Continuous)

<hr>

```{r scat5, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Color'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, color = hp), 
             position = 'jitter')
```

### Specify Value for Color

<hr>

```{r scat6, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Color'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg), color = 'blue', 
             position = 'jitter')
```

### Specify Value for Alpha

<hr>

```{r scat7, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Alpha'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg), color = 'blue', alpha = 0.4, 
             position = 'jitter')
```

## Shape

### Map Shape to Variable

<hr>

```{r scat8, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Shape'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, shape = factor(cyl)),
             position = 'jitter')
```

### Specify Value for Shape

<hr>

```{r scat9, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Shape'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg), shape = 3,
             position = 'jitter')
```

## Size

### Map Size to Variable

<hr>

```{r scat10, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Shape'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, size = hp), color = 'blue',
             position = 'jitter')
```

### Specify Value for Size

<hr>

```{r scat11, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Shape'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg), size = 3,
             position = 'jitter')
```

## Regression Line

### Introduction

<hr>

### Linear Regression

```{r aes12, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Regression Line'}
ggplot(mtcars, aes(disp, mpg)) +
  geom_point(position = 'jitter') +
  geom_smooth(method = 'lm', se = FALSE)
```

### Regression Line - Conf. Interval

<hr>

```{r aes13, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Conf. Interval'}
ggplot(mtcars, aes(disp, mpg)) +
  geom_point(position = 'jitter') +
  geom_smooth(method = 'lm', se = TRUE)
```

### Regression Line - Loess Method

<hr>

```{r aes14, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Loess Method'}
ggplot(mtcars, aes(disp, mpg)) +
  geom_point(position = 'jitter') +
  geom_smooth(method = 'loess', se = FALSE)
```

### Fit Line - Intercept & Slope

<hr>

```{r aes17, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Intercept & Slope'}
ggplot(mtcars, aes(disp, mpg)) +
  geom_point(position = 'jitter') +
  geom_abline(slope = 29.59985, intercept = -0.04122)
```