---
title: "Readable Code with Pipes"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(dplyr)
library(magrittr)
knitr::opts_chunk$set(echo = FALSE)
ecom <- readr::read_csv('https://raw.githubusercontent.com/rsquaredacademy/datasets/master/web.csv')
```

## Introduction

<hr>

When you are dealing with a sequence of multiple operations, R code can get a bit cramped and not so easy on the eyes. The [magrittr](https://CRAN.R-project.org/package=magrittr) package by Stefan Milton Bache provides pipes enabling us to write R code that is readable.

- especially useful when you have nested functions
- similar in spirit to javascript's method chaining
- functions taking multiple arguments can be confusing and messy to read
- with magrittr, you program from left to right

## Pipes

<hr>

R being a functional language, code contains a lot of parentheses. Complex code results in nested functions making them hard to read and maintain. If you are using tidyverse packages, magrittr will be automatically loaded. We will look at 3 different types of 
pipes:

- `%>%` : pipe a value forward into an expression or function call
- `%<>%`: result assigned to left hand side object instead of returning it 
- `%$%` : expose names within left hand side objects to right hand side expressions

## Data

### View Data

<hr>

```{r show, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'View Data'}
ecom
```

## Data Dictionary

<hr>

- id: row id
- referrer: referrer website/search engine
- os: operating system
- browser: browser
- device: device used to visit the website
- n_pages: number of pages visited
- duration: time spent on the website (in seconds)
- repeat: frequency of visits
- country: country of origin
- purchase: whether visitor purchased
- order_value: order value of visitor (in dollars)

## %>%

## %<>%

## %$%

