---
title: "Legend - Part 7"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(ggplot2)
library(dplyr)
library(tidyr)
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction

### Agenda

<hr>

Learn to modify legend

- title
- label

## Alignment

### Introduction

<hr>

- alignment
    - 0 (left)
    - 1 (right)

### Example

<hr>

```{r leg2eg, echo=FALSE, collapse=FALSE, fig.align='center'}
ggplot(mtcars) + geom_point(aes(disp, mpg, color = factor(cyl))) +
  scale_color_manual(values = c("red", "blue", "green"),
    guide = guide_legend(title = "Cylinders", title.hjust = 0.5))
```

### Instructions

<hr>

```{r leg2, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Title Alignment'}
ggplot(mtcars) + geom_point(aes(disp, mpg, color = factor(cyl))) +
  scale_color_manual(values = c("red", "blue", "green"),
    guide = guide_legend(title = "Cylinders", title.hjust = 0.5))
```

```{r leg2-solution}
ggplot(mtcars) + geom_point(aes(disp, mpg, color = factor(cyl))) +
  scale_color_manual(values = c("red", "blue", "green"),
    guide = guide_legend(title = "Cylinders", title.hjust = 0.5))
```

## Position

### Introduciton

<hr>

- position
    - top
    - bottom
    - left
    - right

### Example

<hr>

```{r leg3eg, echo=FALSE, collapse=FALSE, fig.align='center'}
ggplot(mtcars) + geom_point(aes(disp, mpg, color = factor(cyl))) +
  scale_color_manual(values = c("red", "blue", "green"),
    guide = guide_legend(title = "Cylinders", title.hjust = 0.5, 
      title.position = "top"))
```

### Instructions

<hr>

```{r leg3, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Title Position'}
ggplot(mtcars) + geom_point(aes(disp, mpg, color = factor(cyl))) +
  scale_color_manual(values = c("red", "blue", "green"),
    guide = guide_legend(title = "Cylinders", title.hjust = 0.5, 
      title.position = "top"))
```

```{r leg3-solution}
ggplot(mtcars) + geom_point(aes(disp, mpg, color = factor(cyl))) +
  scale_color_manual(values = c("red", "blue", "green"),
    guide = guide_legend(title = "Cylinders", title.hjust = 0.5, 
      title.position = "top"))
```

## Position

### Introduction

<hr>

- position
    - top
    - bottom
    - left 
    - right

### Example

<hr>

```{r leg4eg, echo=FALSE, collapse=FALSE, fig.align='center'}
ggplot(mtcars) + geom_point(aes(disp, mpg, color = factor(cyl))) +
  scale_color_manual(values = c("red", "blue", "green"),
    guide = guide_legend(label.position = "right"))
```

### Instructions

<hr>

```{r leg4, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Label Position'}
ggplot(mtcars) + geom_point(aes(disp, mpg, color = factor(cyl))) +
  scale_color_manual(values = c("red", "blue", "green"),
    guide = guide_legend(label.position = "right"))
```

```{r leg4-solution}
ggplot(mtcars) + geom_point(aes(disp, mpg, color = factor(cyl))) +
  scale_color_manual(values = c("red", "blue", "green"),
    guide = guide_legend(label.position = "right"))
```

## Label

## Alignment

### Introduction

<hr>

- alignment 
    - 0 (left)
    - 1 (right)


### Example

<hr>

```{r leg5eg, echo=FALSE, collapse=FALSE, fig.align='center'}
ggplot(mtcars) + geom_point(aes(disp, mpg, color = factor(cyl))) +
  scale_color_manual(values = c("red", "blue", "green"),
    guide = guide_legend(label.hjust = 0.5))
```

### Instructions

<hr>

```{r leg5, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Label Alignment'}
ggplot(mtcars) + geom_point(aes(disp, mpg, color = factor(cyl))) +
  scale_color_manual(values = c("red", "blue", "green"),
    guide = guide_legend(label.hjust = 0.5))
```

```{r leg5-solution}
ggplot(mtcars) + geom_point(aes(disp, mpg, color = factor(cyl))) +
  scale_color_manual(values = c("red", "blue", "green"),
    guide = guide_legend(label.hjust = 0.5))
```

## Direction

### Introduction

<hr>

- direction
    - horizontal
    - vertical

### Example

<hr>

```{r leg6eg, echo=FALSE, collapse=FALSE, fig.align='center'}
ggplot(mtcars) + geom_point(aes(disp, mpg, color = factor(cyl))) +
  scale_color_manual(values = c("red", "blue", "green"),
    guide = guide_legend(direction = "horizontal"))
```

### Instructions

<hr>

```{r leg6, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Direction'}
ggplot(mtcars) + geom_point(aes(disp, mpg, color = factor(cyl))) +
  scale_color_manual(values = c("red", "blue", "green"),
    guide = guide_legend(direction = "horizontal"))
```

```{r leg6-solution}
ggplot(mtcars) + geom_point(aes(disp, mpg, color = factor(cyl))) +
  scale_color_manual(values = c("red", "blue", "green"),
    guide = guide_legend(direction = "horizontal"))
```

## Rows

<hr>

### Example

<hr>

```{r leg7eg, echo=FALSE, collapse=FALSE, fig.align='center'}
ggplot(mtcars) + geom_point(aes(disp, mpg, color = factor(cyl))) +
  scale_color_manual(values = c("red", "blue", "green"),
    guide = guide_legend(nrow = 2))
```

### Instructions

<hr>

```{r leg7, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Rows'}
ggplot(mtcars) + geom_point(aes(disp, mpg, color = factor(cyl))) +
  scale_color_manual(values = c("red", "blue", "green"),
    guide = guide_legend(nrow = 2))
```

```{r leg7-solution}
ggplot(mtcars) + geom_point(aes(disp, mpg, color = factor(cyl))) +
  scale_color_manual(values = c("red", "blue", "green"),
    guide = guide_legend(nrow = 2))
```

## Reverse

### Introduction

<hr>

- reverse
    - TRUE
    - FALSE

### Example

<hr>

```{r leg8eg, echo=FALSE, collapse=FALSE, fig.align='center'}
ggplot(mtcars) + geom_point(aes(disp, mpg, color = factor(cyl))) +
  scale_color_manual(values = c("red", "blue", "green"),
    guide = guide_legend(reverse = TRUE))
```

### Instructions

<hr>

```{r leg8, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Reverse'}
ggplot(mtcars) + geom_point(aes(disp, mpg, color = factor(cyl))) +
  scale_color_manual(values = c("red", "blue", "green"),
    guide = guide_legend(reverse = TRUE))
```

```{r leg8-solution}
ggplot(mtcars) + geom_point(aes(disp, mpg, color = factor(cyl))) +
  scale_color_manual(values = c("red", "blue", "green"),
    guide = guide_legend(reverse = TRUE))
```

## Guides

<hr>

### Example

<hr>

```{r leg20eg, echo=FALSE, collapse=FALSE, fig.align='center'}
ggplot(mtcars) + geom_point(aes(disp, mpg, color = factor(cyl))) +
  scale_color_manual(values = c("red", "blue", "green"),
    guide = guide_legend(title = "Cylinders", title.hjust = 0.5, 
      title.position = "top", label.position = "right", 
      direction = "horizontal", label.hjust = 0.5, nrow = 2, reverse = TRUE)
  )
```

### Instructions

<hr>

```{r leg20, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Guides'}
ggplot(mtcars) + geom_point(aes(disp, mpg, color = factor(cyl))) +
  scale_color_manual(values = c("red", "blue", "green"),
    guide = guide_legend(title = "Cylinders", title.hjust = 0.5, 
      title.position = "top", label.position = "right", 
      direction = "horizontal", label.hjust = 0.5, nrow = 2, reverse = TRUE)
  )
```

```{r leg20-solution}
ggplot(mtcars) + geom_point(aes(disp, mpg, color = factor(cyl))) +
  scale_color_manual(values = c("red", "blue", "green"),
    guide = guide_legend(title = "Cylinders", title.hjust = 0.5, 
      title.position = "top", label.position = "right", 
      direction = "horizontal", label.hjust = 0.5, nrow = 2, reverse = TRUE)
  )
```

## Title Alignment 

<hr>

### Example

<hr>

```{r leg22eg, echo=FALSE, collapse=FALSE, fig.align='center'}
ggplot(mtcars) + geom_point(aes(disp, mpg, color = hp)) +
  scale_color_continuous(guide = guide_colorbar(
    title = "Horsepower", title.position = "top", title.vjust = 1))
```

### Instructions

<hr>

```{r leg22, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Title Alignment'}
ggplot(mtcars) + geom_point(aes(disp, mpg, color = hp)) +
  scale_color_continuous(guide = guide_colorbar(
    title = "Horsepower", title.position = "top", title.vjust = 1))
```

```{r leg22-solution}
ggplot(mtcars) + geom_point(aes(disp, mpg, color = hp)) +
  scale_color_continuous(guide = guide_colorbar(
    title = "Horsepower", title.position = "top", title.vjust = 1))
```

## Labels Alignment 

<hr>

### Example

<hr>

```{r leg23eg, echo=FALSE, collapse=FALSE, fig.align='center'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, color = hp)) +
  scale_color_continuous(guide = guide_colorbar(
    label.vjust = 0.8))
```

### Instructions

<hr>

```{r leg23, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Label Alignment'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, color = hp)) +
  scale_color_continuous(guide = guide_colorbar(
    label.vjust = 0.8))
```

```{r leg23-solution}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, color = hp)) +
  scale_color_continuous(guide = guide_colorbar(
    label.vjust = 0.8))
```