---
title: "Text Annotations"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction

There are occassions when you want to display additional information in a plot. This is usually achieved by adding text either inside the plot or on the margins. For example, you might want to label a line/bar or add formulas to better communicate what is shown in the plot. The idea is to use the available space within/outside the plot to provide additional information that can be useful to the end users. 


### Agenda

<hr>

We will learn to add text inside as well as on the margins of the plot. This is accomplished using the following two functions:

- `text()` : add text inside the plot
- `mtext()` : add text on the margins of the plot


## Syntax

<hr>

### Text

<hr>

```{r text-syntax, eval=FALSE, echo=TRUE, collapse=FALSE}
text(x, y = NULL, labels = seq_along(x$x), adj = NULL,
     pos = NULL, offset = 0.5, vfont = NULL,
     cex = 1, col = NULL, font = NULL, ...)
```

### Marginal Text

<hr>

```{r mtext-syntax, eval=FALSE, echo=TRUE, collapse=FALSE}
mtext(text, side = 3, line = 0, outer = FALSE, at = NA,
      adj = NA, padj = NA, cex = NA, col = NA, font = NA, ...)
```


## Text Inside the Plot

### Introduction

<hr>

To add text inside a plot, the following arguments must be supplied to the `text()` function:

- `labels` : the text to be displayed
- `x` : x axis coordinate
- `y` : y axis coordinate

### Example

<hr>

```{r textintro, echo=TRUE, collapse=FALSE, fig.align='center', fig.width=5, fig.height=5}
plot(mtcars$disp, mtcars$mpg)
text(x = 340, y = 30, labels = 'Sample Text')
```

### Instructions

<hr>

- set `x axis` coordinate to `240`
- set `y axis` coordinate to `24`
- set `labels` to `'Text'`

```{r text1, fig.align='center', fig.width=5, fig.height=5, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Text Annotations'}
plot(mtcars$disp, mtcars$mpg)
text(x = , y = , labels = )
```

```{r text1-solution}
plot(mtcars$disp, mtcars$mpg)
text(x = 240, y = 24, labels = 'Text')
```

## Text Color

### Introduction

<hr>

### Example

<hr>

```{r tcolor, echo=TRUE, collapse=FALSE, fig.align='center', fig.width=5, fig.height=5}
plot(mtcars$disp, mtcars$mpg)
text(x = 340, y = 30, labels = 'Sample Text', col = 'blue')
```

### Instructions

<hr>

- set `x axis` coordinate to `240`
- set `y axis` coordinate to `24`
- set `labels` to `'Text'`
- set `col` to `'red'`

```{r text2, fig.align='center', fig.width=5, fig.height=5, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Text Color'}
plot(mtcars$disp, mtcars$mpg)
text(x = , y = , labels = , col = )
```

```{r text2-solution}
plot(mtcars$disp, mtcars$mpg)
text(x = 240, y = 25, labels = 'Text', col = 'red')
```

## Font Type

### Introduction

<hr>

### Example

<hr>

```{r text4eg, echo=TRUE, collpase=FALSE, fig.align='center', fig.width=5, fig.height=5}
plot(mtcars$disp, mtcars$mpg)
text(x = 340, y = 30, labels = 'Sample Text', font = 2)
```

### Instructions

<hr>

- set `font` to `4`

```{r text4, fig.align='center', fig.width=5, fig.height=5, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Text Font'}
plot(mtcars$disp, mtcars$mpg)
text(x = 340, y = 30, labels = 'Sample Text', font = )
```

```{r text4-solution}
plot(mtcars$disp, mtcars$mpg)
text(x = 340, y = 30, labels = 'Sample Text', font = 4)
```

## Font Family

### Introduction

<hr>

### Example

<hr>

```{r text6eg, echo=TRUE, collapse=FALSE, fig.align='center', fig.width=5, fig.height=5}
plot(mtcars$disp, mtcars$mpg)
text(x = 340, y = 30, labels = 'Sample Text', family = 'mono')
```

### Instructions

<hr>

- set `family` to `'serif'`

```{r text6, fig.align='center', fig.width=5, fig.height=5, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Text Font Family'}
plot(mtcars$disp, mtcars$mpg)
text(x = 340, y = 30, labels = 'Sample Text',  family = )
```

```{r text6-solution}
plot(mtcars$disp, mtcars$mpg)
text(x = 340, y = 30, labels = 'Sample Text', family = 'serif')
```

## Font Size

### Introduction

<hr>

### Example

<hr>

```{r text8eg, echo=TRUE, collapse=FALSE, fig.align='center', fig.width=5, fig.height=5}
plot(mtcars$disp, mtcars$mpg)
text(x = 340, y = 30, labels = 'Sample Text', cex = 2)
```

### Instructions

<hr>

- set `cex` to 1.5

```{r text8, fig.align='center', fig.width=5, fig.height=5, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Text Font Size'}
plot(mtcars$disp, mtcars$mpg)
text(x = 340, y = 30, labels = 'Sample Text', cex = )
```

```{r text8-solution}
plot(mtcars$disp, mtcars$mpg)
text(x = 340, y = 30, labels = 'Sample Text', cex = 1.5)
```

## Text on the Margins

### Introduction

<hr>

The `mtext()` function allows the user to place the text on the margins of the plot. It allows the user to modify the location of the text in multiple ways and we will explore them one by one. To beign with, let us add text to the plot using the `mtext()` function. The minimum input you need to provide is the text itself. Below is a simple example:

### Example

<hr>

```{r mtext1eg, echo=TRUE, collapse=FALSE, fig.align='center', fig.width=5, fig.height=5}
plot(mtcars$disp, mtcars$mpg)
mtext('Sample Text')
```

### Instructions

<hr>

- add `Text` on the margins using `mtext()`

```{r mtext1, fig.align='center', fig.width=5, fig.height=5, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Text on the Margins'}
plot(mtcars$disp, mtcars$mpg)
mtext()
```

```{r mtext1-solution}
plot(mtcars$disp, mtcars$mpg)
mtext('Text')
```

## Specify Margin

### Introduction

<hr>

### Example

<hr>

```{r mtext2eg, echo=TRUE, collapse=FALSE, fig.align='center', fig.width=5, fig.height=5}
plot(mtcars$disp, mtcars$mpg)
mtext('Sample Text', side = 1)
```

### Instructions

<hr>

- set `side` to 2

```{r mtext2, fig.align='center', fig.width=5, fig.height=5, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Specify Margin'}
plot(mtcars$disp, mtcars$mpg)
mtext('Sample Text', side = )
```

```{r mtext2-solution}
plot(mtcars$disp, mtcars$mpg)
mtext('Sample Text', side = 2)
```

## Vertical Alignment

### Introduction

<hr>

### Example

<hr>

```{r mtext4eg, echo=TRUE, collapse=FALSE, fig.align='center', fig.width=5, fig.height=5}
plot(mtcars$disp, mtcars$mpg)
mtext('Sample Text', line = 1)
```

### Instructions

<hr>

- set `line` to `-1`

```{r mtext4, fig.align='center', fig.width=5, fig.height=5, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Vertical Alignment'}
plot(mtcars$disp, mtcars$mpg)
mtext('Sample Text', line = )
```

```{r mtext4-solution}
plot(mtcars$disp, mtcars$mpg)
mtext('Sample Text', line = -1)
```

## Horizontal Alignment

### Introduction

<hr>

### Example

<hr>

```{r mtext7eg, echo=TRUE, collapse=FALSE, fig.align='center', fig.width=5, fig.height=5}
plot(mtcars$disp, mtcars$mpg)
mtext('Sample Text', adj = 0)
```

### Instructions

<hr>

- set `adj` to `1`

```{r mtext7, fig.align='center', fig.width=5, fig.height=5, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Horizontal Alignment'}
plot(mtcars$disp, mtcars$mpg)
mtext('Sample Text', adj = )
```

```{r mtext7-solution}
plot(mtcars$disp, mtcars$mpg)
mtext('Sample Text', adj = 1)
```

