---
title: "Legends - Part 1"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)
year <- seq(2010, 2014, 1)
india <- c(10.3, 6.6, 5.6, 6.6, 7.2)
china <- c(10.6, 9.5, 7.8, 7.7, 7.3)
russia <- c(4.5, 4.3, 3.5, 1.3, 0.7)
brazil <- c(7.5, 3.9, 1.9, 3.0, 0.1)
s_africa <- c(3.2, 3.2, 2.2, 2.2, 1.5)
gdp <- data.frame(year, india, china, russia, brazil, s_africa, stringsAsFactors = FALSE)
```

## Agenda

<hr>

Learn to add legend to a plot using the `legend()` function. Specifically

- position the legend within the plot
- modify the layout using `ncol` and `horiz` arguments
- add title using the `title.` set of arguments
- modify the appearance and position of the legend box
- modify the appearance of the text in the legend box


## Introduction

### Compare

<hr>

```{r compare, fig.align='center', fig.width= 7, fig.height=7, echo=FALSE, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Compare'}
init <- par(no.readonly = TRUE)
par(mfrow = c(1, 2))
{plot(gdp$year, gdp$india, type = 'l', ylim = c(-5, 15), xlab = 'Year',
      ylab = 'Growth Rate', col = 'blue', main = 'BRICS: Growth Rate')
lines(gdp$year, gdp$china, col = 'red')}
{plot(gdp$year, gdp$india, type = 'l', ylim = c(-5, 15), xlab = 'Year',
      ylab = 'Growth Rate', col = 'blue', main = 'BRICS: Growth Rate')
lines(gdp$year, gdp$china, col = 'red')
legend(x = 2012, y = 14, legend = c('india', 'china'), lty = 1, col = c('blue', 'red'))}
```


## Data

<hr>

```{r data, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Data'}
gdp
```

## Plot

<hr>

```{r line1, fig.align='center', fig.width= 7, fig.height=5, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Line Graph'}
{plot(gdp$year, gdp$india, type = 'l', ylim = c(-5, 15), xlab = 'Year',
      ylab = 'Growth Rate', col = 'blue', main = 'BRICS: Growth Rate')
lines(gdp$year, gdp$china, col = 'red')
lines(gdp$year, gdp$russia, col = 'green')
lines(gdp$year, gdp$brazil, col = 'yellow')
lines(gdp$year, gdp$s_africa, col = 'violet')}
```

## Location - 1

<hr>

- use x and y axis coordinates
- use keywords
    - top
    - bottom
    - left
    - right
    - center
    - bottomright
    - bottomleft
    - topright
    - topleft

```{r leg2, fig.align='center', fig.width=7, fig.height=7, echo=FALSE, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Legend Location'}
init <- par(no.readonly = TRUE)
par(mfrow = c(3, 3))
values <- c('top', 'bottom', 'left', 'right', 'center',
            'bottomright', 'bottomleft', 'topright', 'topleft')
for (i in values) {
  plot(gdp$year, gdp$india, type = 'l',
      ylim = c(-5, 15), xlab = 'Year',
      ylab = 'Growth Rate', col = 'blue',
      main = 'BRICS: Growth Rate')
  lines(gdp$year, gdp$china, col = 'red')
  legend(x = i, legend = c('india', 'china'))
  mtext(paste("x = ", i), side = 3, col = "blue")
}
```

## Location - 2

```{r leg1, fig.align='center', fig.height=5, fig.width=5, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Legend Location'}
{plot(gdp$year, gdp$india, type = 'l', ylim = c(-5, 15), xlab = 'Year',
      ylab = 'Growth Rate', col = 'blue', main = 'BRICS: Growth Rate')
lines(gdp$year, gdp$china, col = 'red')
legend(x = 2013, y = 14, legend = c('india', 'china'))}
```

## Lines

<hr>

```{r leg3, fig.align='center', fig.height=5, fig.width=5, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Lines'}
{plot(gdp$year, gdp$india, type = 'l', ylim = c(-5, 15), xlab = 'Year',
      ylab = 'Growth Rate', col = 'blue', main = 'BRICS: Growth Rate')
lines(gdp$year, gdp$china, col = 'red')
legend(x = 2012, y = 14, legend = c('india', 'china'), lty = 1, col = c('blue', 'red'))}
```

## Points

<hr>

```{r leg4, fig.align='center', fig.height=5, fig.width=5, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Points'}
{plot(gdp$year, gdp$india, type = 'l', ylim = c(-5, 15), xlab = 'Year',
      ylab = 'Growth Rate', col = 'blue', main = 'BRICS: Growth Rate')
points(gdp$year, gdp$india, pch = 2, col = 'blue')
lines(gdp$year, gdp$china, col = 'red')
points(gdp$year, gdp$china, pch = 2, col = 'red')
legend(x = 2012, y = 14, legend = c('india', 'china'), lty = 1, pch = 2, col = c('blue', 'red'))}
```

## Text Placement - 1

### Introduction

```{r leg7, fig.align='center', fig.width=7, fig.height=10, echo=FALSE, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Text Placement'}
init <- par(no.readonly = TRUE)
par(mfrow = c(2, 2))
values <- c(1, 2, 3, 4)
for (i in values) {
  plot(gdp$year, gdp$india, type = 'l',
      ylim = c(-5, 15), xlab = 'Year',
      ylab = 'Growth Rate', col = 'blue',
      main = 'BRICS: Growth Rate')
  lines(gdp$year, gdp$china, col = 'red')
  lines(gdp$year, gdp$russia, col = 'green')
  lines(gdp$year, gdp$brazil, col = 'yellow')
  legend(x = 2010, y = 0, legend = c('india', 'china', 'russia','brazil'),
       lty = 1, col = c('blue', 'red', 'green', 'yellow'),
       ncol = i)
  mtext(paste("ncol = ", i), side = 3, col = "blue")
}
```

## Text Placement - 2

<hr>

```{r leg5, fig.align='center', fig.height=4, fig.width=6, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Text Placement'}
{plot(gdp$year, gdp$india, type = 'l', ylim = c(-5, 15), xlab = 'Year',
      ylab = 'Growth Rate', col = 'blue', main = 'BRICS: Growth Rate')
lines(gdp$year, gdp$china, col = 'red')
legend(x = 2011, y = 14, legend = c('india', 'china'), 
      lty = 1, col = c('blue', 'red'), horiz = TRUE)}
```

## Text Placement - 3

<hr>

```{r leg6, fig.align='center', fig.width= 6, fig.height=4, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Text Placement'}
{plot(gdp$year, gdp$india, type = 'l', ylim = c(-5, 25), xlab = 'Year',
      ylab = 'Growth Rate', col = 'blue', main = 'BRICS: Growth Rate')
lines(gdp$year, gdp$china, col = 'red')
lines(gdp$year, gdp$russia, col = 'green')
lines(gdp$year, gdp$brazil, col = 'yellow')
legend(x = 2012, y = 20, legend = c('india', 'china', 'russia', 'brazil'),
       lty = 1, col = c('blue', 'red', 'green', 'yellow'), ncol = 2)}
```

