---
title: "Readable Code with Pipes"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(dplyr)
library(magrittr)
knitr::opts_chunk$set(echo = FALSE)
ecom <- readr::read_csv('https://raw.githubusercontent.com/rsquaredacademy/datasets/master/web.csv')
```

## Introduction

<hr>

When you are dealing with a sequence of multiple operations, R code can get a bit cramped and not so easy on the eyes. The [magrittr](https://CRAN.R-project.org/package=magrittr) package by Stefan Milton Bache provides pipes enabling us to write R code that is readable.

- especially useful when you have nested functions
- similar in spirit to javascript's method chaining
- functions taking multiple arguments can be confusing and messy to read
- with magrittr, you program from left to right

## Visualization

### Introduction

<hr>

Let us look at a visualization example. From the ecommerce data set, we have the distribution of referrers (for those who have purchased/converted). We can decompose the code into the following steps:

- `subset` data for those who have purchased/converted
- extract the referrer column using `$`
- compute the frequency using `table()`
- pass the data to `barplot()`

```{r mag21, fig.align='center', fig.height=4, fig.width=6, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Visualize'}
barplot(table(subset(ecom, purchase == 'true')$referrer))
```

## Visualization - Using Pipe

<hr>

Let us build a barplot from `mtcars` data.

```{r mag30, eval=FALSE, echo=TRUE}
# without pipe
barplot(table(subset(mtcars, cyl == 8)$am))

# with pipe
mtcars %>%`
  subset(cyl == 8) %$%
  am %>%
  table() %>%
  barplot()
```
## Visualization - Practice

### Instructions

<hr>

Let us now use pipes to build the same plot. We have written the partial code for you:

- pass on the referrer data to `table()` using `%>%`
- pass on the result from the previous step to `barplot()` using `%>%`

```{r mag7, fig.align='center', fig.height=4, fig.width=6, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Visualize - Using Pipe'}
ecom %>%
  subset(purchase == 'true') %$%
  referrer


```

```{r mag7-solution}
ecom %>%
  subset(purchase == 'true') %$%
  referrer %>%
  table() %>%
  barplot()
```

## Regression

### Introduction

<hr>

```{r mag8, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Regression'}
summary(lm(duration ~ n_pages, data = ecom))
```

## Regression - Using Pipe

<hr>

```{r mag31, eval=FALSE, echo=TRUE}
# without pipe
summary(lm(disp ~ mpg, data = mtcars))

# with pipe
mtcars %$%`
  lm(disp ~ mpg) %>%
  summary()
```

## Regression - Practice

### Instructions

<hr>

- expose `duration` and `n_pages` from `ecom` using `%$%` 
- pass them onto `lm()` 
- pass the result from `lm()` to `summary()` using `%>%`

```{r mag22, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Regression - Using Pipe'}
ecom %$%
  
```

```{r mag22-solution}
ecom %$%
  lm(duration ~ n_pages) %>%
  summary()
```

## String Manipulation

### Introduction

<hr>

```{r mag9, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'String Manipulation'}
email <- 'jovialcann@anymail.com'

# without pipe
toupper(strtrim(strsplit(email, '@')[[1]][1], 6))
```

## String Manipulation - With Pipe

### Instructions

```{r mag99, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'String Manipulation'}
email %>%
  strsplit(split = '@') %>%
  extract2(1) %>%
  extract(1) %>%
  strtrim(width = 6) %>%
  toupper()
```

