---
title: "Readable Code with Pipes"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(dplyr)
library(magrittr)
knitr::opts_chunk$set(echo = FALSE)
ecom <- readr::read_csv('https://raw.githubusercontent.com/rsquaredacademy/datasets/master/web.csv')
```

## Introduction

<hr>

When you are dealing with a sequence of multiple operations, R code can get a bit cramped and not so easy on the eyes. The [magrittr](https://CRAN.R-project.org/package=magrittr) package by Stefan Milton Bache provides pipes enabling us to write R code that is readable.

- especially useful when you have nested functions
- similar in spirit to javascript's method chaining
- functions taking multiple arguments can be confusing and messy to read
- with magrittr, you program from left to right

## Pipes

<hr>

R being a functional language, code contains a lot of parentheses. Complex code results in nested functions making them hard to read and maintain. If you are using tidyverse packages, magrittr will be automatically loaded. We will look at 3 different types of 
pipes:

- `%>%` : pipe a value forward into an expression or function call
- `%<>%`: result assigned to left hand side object instead of returning it 
- `%$%` : expose names within left hand side objects to right hand side expressions

## Data

### View Data

<hr>

```{r show, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'View Data'}
ecom
```

### Data Dictionary

<hr>

- id: row id
- referrer: referrer website/search engine
- os: operating system
- browser: browser
- device: device used to visit the website
- n_pages: number of pages visited
- duration: time spent on the website (in seconds)
- repeat: frequency of visits
- country: country of origin
- purchase: whether visitor purchased
- order_value: order value of visitor (in dollars)

## Case Study

### Data Overview

<hr>

```{r mag1, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'View Data'}
head(ecom, 10)

# using pipe
ecom %>% head(10)
```

## Square Root 

<hr>

```{r mag3, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Square Root'}
y <- ecom$n_pages
y <- sqrt(y)
head(y)
```

### Square Root - Using pipe

<hr>

```{r mag4, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Square Root'}
# select n_pages variable and assign it to y
y <- ecom %$% n_pages
head(y)

# compute square root of y and assign it to y 
y %<>% sqrt()
head(y)
```

### Square Root - Using pipe

<hr>

```{r mag5, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Square Root'}
y <- ecom %$% 
  n_pages %>% 
  sqrt()
head(y)
```

## Correlation

<hr>

```{r mag6, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Correlation'}
# without pipe
ecom1 <- subset(ecom, purchase == 'true')
cor(ecom1$n_pages, ecom1$duration)

# with pipe
ecom %>%
  subset(purchase == 'true') %$% 
  cor(n_pages, duration)
```

## Visualization

<hr>

```{r mag21, fig.align='center', fig.height=4, fig.width=6, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Visualize'}
barplot(table(subset(ecom, purchase == 'true')$referrer))
```

### Visualization - Using pipe

<hr>

```{r mag7, fig.align='center', fig.height=4, fig.width=6, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Visualize - Using Pipe'}
ecom %>%
  subset(purchase == 'true') %>%
  extract('referrer') %>%
  table() %>%
  barplot()
```

## Regression

<hr>

```{r mag8, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Regression'}
summary(lm(duration ~ n_pages, data = ecom))
```

### Regression - Using pipe

<hr>

```{r mag22, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Regression - Using Pipe'}
ecom %$%
  lm(duration ~ n_pages) %>%
  summary()
```

## String Manipulation

<hr>

```{r mag9, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'String Manipulation'}
email <- 'jovialcann@anymail.com'

# without pipe
toupper(strtrim(strsplit(email, '@')[[1]][1], 6))

# with pipe
email %>%
  strsplit(split = '@') %>%
  extract2(1) %>%
  extract(1) %>%
  strtrim(width = 6) %>%
  toupper()
```

## Data Extraction

### Introduction

<hr>

- `extract()`
- `extract2()`
- `use_series()`

### Extract Column By Name

<hr>

```{r mag10, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Extract Column'}
head(ecom['n_pages'], 3)

ecom %>%
  extract('n_pages') %>%
  head(3)
```

### Extract Column By Position

<hr>

```{r mag23, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Extract Column'}
head(ecom[6], 3)

ecom %>%
  extract(6) %>%
  head(3)
```

### Extract Column (as vector)

<hr>

```{r mag11, , exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Extract Column'}
head(ecom$n_pages)

ecom %>%
  use_series('n_pages') %>%
  head()
```

### Extract List Element By Name

<hr>

```{r mag12, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Extract List Element'}
mt <- as.list(mtcars)

mt[['mpg']]

mt %>%
  extract2('mpg')
```

### Extract List Element By Position

<hr>

```{r mag13, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Extract List Element'}
mt <- as.list(mtcars)

mt[[1]]

mt %>%
  extract2(1)
```

### Extract List Element (as vector)

<hr>

```{r mag14, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Extract List Element'}
mt <- as.list(mtcars)

mt$mpg

mt %>%
  use_series(mpg)
```

## Arithmetic Operations

### Introduction

<hr>

- `add()`
- `subtract()`
- `multiply_by()`
- `multiply_by_matrix()`
- `divide_by()`
- `divide_by_int()`
- `mod()`
- `raise_to_power()`


### Addition

<hr>

```{r mag15, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Addition'}
1:10 %>%
  `+`(1)

1:10 %>%
  add(1)
```

### Multiplication

<hr>

```{r mag16, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Multiplication'}
1:10 %>%
  `*`(3)

1:10 %>%
  multiply_by(3)
```

### Division

<hr>

```{r mag17, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Division'}
1:10 %>%
  `/`(2)

1:10 %>%
  divide_by(2)
```

### Power

<hr>

```{r mag18, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Power'}
1:10 %>%
  `^`(2)

1:10 %>%
  raise_to_power(2)
```

## Logical Operators

### Introduction

<hr>

- `and()`
- `or()`
- `equals()`
- `not()`
- `is_greater_than()`
- `is_weakly_greater_than()`
- `is_less_than()`
- `is_weakly_less_than()`

### Greater Than

<hr>

```{r mag19, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Greater Than'}
1:10 %>%
  `>`(5)

1:10 %>%
  is_greater_than(5)
```

### Weakly Greater Than

<hr>

```{r mag20, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Weakly Greater Than'}
1:10 %>%
  `>=`(5)

1:10 %>%
  is_weakly_greater_than(5)
```
