---
title: "Themes - Part 1"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(ggplot2)
library(dplyr)
library(tidyr)
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction

### Agenda

<hr>

Use `theme()` to modify the appearance of 

- axis title
- axis text
- axis font
- axis ticks
- axis line

## Plot

### Introduction

<hr>

```{r theme1, echo=TRUE, collapse=FALSE, fig.align='center'}
p <- ggplot(mtcars) +
  geom_point(aes(disp, mpg))
p
```

## Axis Title

### Introduction

<hr>

### Example

<hr>

```{r theme2eg, echo=TRUE, collapse=FALSE, fig.align='center'}
p + theme(axis.title.x = element_text(color = "red", size = 10))
```

### Instructions

<hr>

```{r theme2, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Axis Title'}
p + theme(axis.title.x = element_text(color = "red", size = 10))
```

```{r theme2-solution}
p + theme(axis.title.x = element_text(color = "red", size = 10))
```

## Axis Text

### Introduction

<hr>

### Example

<hr>

```{r theme3eg, echo=TRUE, collapse=FALSE, fig.align='center'}
p + theme(axis.text.x = element_text(color = "red", size = 10))
```

### Instructions

<hr>

```{r theme3, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Axis Text'}
p + theme(axis.text.x = element_text(color = "red", size = 10))
```

```{r theme3-solution}
p + theme(axis.text.x = element_text(color = "red", size = 10))
```

## Axis Font

### Introduction

<hr>

### Example

<hr>

```{r theme4eg, echo=TRUE, collapse=FALSE, fig.align='center'}
p + theme(axis.text = element_text(color = "red", size = 10, face = "italic"))
```

### Instructions

<hr>

```{r theme4, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Axis Font'}
p + theme(axis.text = element_text(color = "red", size = 10, face = "italic"))
```

```{r theme4-solution}
p + theme(axis.text = element_text(color = "red", size = 10, face = "italic"))
```

## Axis Ticks

### Introduction

<hr>

### Example

<hr>

```{r theme5eg, echo=TRUE, collapse=FALSE, fig.align='center'}
p + theme(axis.ticks = element_line(color = 'blue', size = 1.25, linetype = 2), 
          axis.ticks.length = unit(1, "cm"))
```

### Instructions

<hr>

```{r theme5, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Axis Ticks'}
p + theme(axis.ticks = element_line(color = 'blue', size = 1.25, linetype = 2), 
          axis.ticks.length = unit(1, "cm"))
```

```{r theme5-solution}
p + theme(axis.ticks = element_line(color = 'blue', size = 1.25, linetype = 2), 
          axis.ticks.length = unit(1, "cm"))
```

## Axis Line

### Introduction

<hr>

### Example

<hr>

```{r theme6eg, echo=TRUE, collapse=FALSE, fig.align='center'}
p + theme(axis.line = element_line(color = 'red', size = 1.5, linetype = 3))
```

### Instructions

<hr>

```{r theme6, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Axis Line'}
p + theme(axis.line = element_line(color = 'red', size = 1.5, linetype = 3))
```

```{r theme6-solution}
p + theme(axis.line = element_line(color = 'red', size = 1.5, linetype = 3))
```




