---
title: "ggplot2: Themes"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(ggplot2)
library(dplyr)
library(tidyr)
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction

Use `theme()` to modify the appearance of all non data components of the plot such as

- axis
- legend
- panel
- plot area
- background
- margin
- facets

### Agenda

<hr>

In this module, we will learn to 

- modify theme components
- use different themes 

## Axis

### Introduction

<hr>

```{r theme1, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Axis'}
p <- ggplot(mtcars) +
  geom_point(aes(disp, mpg))
p
```

### Axis Title

<hr>

```{r theme2, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Axis Title'}
p + theme(axis.title.x = element_text(color = "red", size = 10))
```

### Axis Text

<hr>

```{r theme3, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Axis Text'}
p + theme(axis.text.x = element_text(color = "red", size = 10))
```

### Axis Font

<hr>


```{r theme4, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Axis Font'}
p + theme(axis.text = element_text(color = "red", size = 10, face = "italic"))
```

### Axis Ticks

<hr>

```{r theme5, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Axis Ticks'}
p + theme(axis.ticks = element_line(color = 'blue', size = 1.25, linetype = 2), 
          axis.ticks.length = unit(1, "cm"))
```

### Axis Line

<hr>

```{r theme6, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Axis Line'}
p + theme(axis.line = element_line(color = 'red', size = 1.5, linetype = 3))
```

## Legend

### Introduction

<hr>

```{r theme7, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Legend'}
p <- ggplot(mtcars) +
  geom_point(aes(disp, mpg, color = factor(cyl), shape = factor(gear)))
p
```

### Background 

<hr>

```{r theme30, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Background'}
p + theme(legend.background = element_rect(fill = 'gray', linetype = 3,  
          color = "black"))
```

### Margin 

<hr>

```{r theme31, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Margin'}
p + theme(legend.margin = margin(4, 8, 4, 8))
```

### Spacing 

<hr>

```{r theme32, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Spacing'}
p + theme(legend.spacing = unit(1.5, "cm"))
```

### Key 

<hr>

```{r theme33, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Key'}
p + theme(legend.key = element_rect(fill = 'red'),
          legend.key.size = unit(0.4, "cm"))
```

### Text 

<hr>

```{r theme34, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Text'}
p + theme(legend.text = element_text(color = 'green', face = 'italic'))
```

### Title 

<hr>

```{r theme35, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Title'}
p + theme(legend.title = element_text(color = 'blue', face = 'bold'),
          legend.title.align = 0.1)
```

### Position 

<hr>

```{r theme36, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Position'}
p + theme(legend.position = "top")
```

### Direction 

<hr>

```{r theme37, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Direction'}
p + theme(legend.direction = "horizontal")
```

### Box 

<hr>

```{r theme38, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Box'}
p + theme(legend.box = "horizontal",
  legend.box.background = element_rect(fill = "gray"),
  legend.box.spacing = unit(1, "cm"), legend.box.just = "left",
  legend.box.margin = margin(4, 8, 4, 8))
```

## Panel

### Introduction

<hr>

```{r theme9, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Panel'}
p <- ggplot(mtcars) +
  geom_point(aes(disp, mpg))
p
```

### Panel Background

<hr>

```{r theme10, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Panel Background'}
p + theme(panel.background = element_rect(fill = 'gray'))
```

### Panel Border

<hr>

```{r theme24, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Panel Border'}
p + theme(panel.border = element_rect(fill = NA, color = 'blue', 
          linetype = 1, size = 2))
```

### Panel Grid

<hr>

```{r theme25, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Panel Grid'}
p + theme(panel.grid = element_line(color = 'blue', linetype = 2, size = 0.5))
```

### Panel Grid (Major)

<hr>

```{r theme12, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Panel Grid (Major)'}
p + theme(panel.grid.major.x = element_line(color = 'blue', 
          linetype = 2, size = 0.5))
```


### Panel Grid (Minor, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Panel Grid (Minor)')

<hr>

```{r theme26, fig.align='center'}
p + theme(panel.grid.minor.y = element_line(color = 'red', 
          linetype = 3, size = 0.2))
```


## Plot Area

### Introduction

<hr>

```{r theme13, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Plot Area'}
p <- ggplot(mtcars) +
  geom_point(aes(disp, mpg)) + 
  ggtitle('Theme Modification')
p
```

### Plot Background

<hr>

```{r theme14, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Plot Background'}
p + theme(plot.background = element_rect(color = 'blue', 
          fill = '#4682B4'))
```

### Plot Title

<hr>

```{r theme27, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Plot Title'}
p + theme(plot.title = element_text(color = 'red'))
```

### Plot Margin

<hr>

```{r theme28, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Plot Margin'}
p + theme(plot.margin = unit(c(1, 1, 1, 1), "cm"))
```

## Facets

### Introduction

<hr>

```{r theme15, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Facets'}
p <- ggplot(mtcars) +
  geom_point(aes(disp, mpg)) + 
  facet_grid(~cyl)
p
```

### Strip Background

<hr>

```{r theme16, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Strip Background'}
p + theme(strip.background = element_rect(color = 'red', 
          fill = '#4682B4'))
```

### Strip Text

<hr>

```{r theme29, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Strip Text'}
p + theme(strip.text = element_text(face = 'italic', size = 8,
          color = 'red'))
```

## Themes

### Introduction

<hr>

### Classic Dark on Light

<hr>

```{r theme17, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Classic Dark on Light'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg)) +
  theme_bw()
```

### Default Gray

<hr>

```{r theme18, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Default Gray'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg)) +
  theme_gray()
```

### Light

<hr>

```{r theme19, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Light'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg)) +
  theme_light()
```

### Minimal

<hr>

```{r theme20, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Minimal'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg)) +
  theme_minimal()
```

### Dark

<hr>

```{r theme21, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Dark'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg)) +
  theme_dark()
```

### Classic

<hr>

```{r theme22, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Classic'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg)) +
  theme_classic()
```

### Void (Empty)

<hr>

```{r theme23, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Void'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg)) +
  theme_void()
```

