---
title: "Readable Code with Pipes"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(dplyr)
library(magrittr)
knitr::opts_chunk$set(echo = FALSE)
ecom <- readr::read_csv('https://raw.githubusercontent.com/rsquaredacademy/datasets/master/web.csv')
```

## Introduction

<hr>

When you are dealing with a sequence of multiple operations, R code can get a bit cramped and not so easy on the eyes. The [magrittr](https://CRAN.R-project.org/package=magrittr) package by Stefan Milton Bache provides pipes enabling us to write R code that is readable.

- especially useful when you have nested functions
- similar in spirit to javascript's method chaining
- functions taking multiple arguments can be confusing and messy to read
- with magrittr, you program from left to right


## Arithmetic Operations

### Introduction

<hr>

- `add()`
- `subtract()`
- `multiply_by()`
- `multiply_by_matrix()`
- `divide_by()`
- `divide_by_int()`
- `mod()`
- `raise_to_power()`


## Addition

<hr>

```{r mag15, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Addition'}
1:10 %>%
  `+`(1)

1:10 %>%
  add(1)
```

## Multiplication

<hr>

```{r mag16, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Multiplication'}
1:10 %>%
  `*`(3)

1:10 %>%
  multiply_by(3)
```

## Division

<hr>

```{r mag17, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Division'}
1:10 %>%
  `/`(2)

1:10 %>%
  divide_by(2)
```

## Power

<hr>

```{r mag18, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Power'}
1:10 %>%
  `^`(2)

1:10 %>%
  raise_to_power(2)
```

## Logical Operators

### Introduction

<hr>

- `and()`
- `or()`
- `equals()`
- `not()`
- `is_greater_than()`
- `is_weakly_greater_than()`
- `is_less_than()`
- `is_weakly_less_than()`

## Greater Than

<hr>

```{r mag19, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Greater Than'}
1:10 %>%
  `>`(5)

1:10 %>%
  is_greater_than(5)
```

## Weakly Greater Than

<hr>

```{r mag20, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Weakly Greater Than'}
1:10 %>%
  `>=`(5)

1:10 %>%
  is_weakly_greater_than(5)
```

