---
title: "Facet - Part 1"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)
```

## Agenda

In this section, we will learn to combine multiple graphs in a single frame using the following functions:

- `par()` 
- `layout()`


## Introduction

Often, it is useful to have multiple plots in the same frame as it allows us to get a comprehensive view of a particular variable or compare among different variables. The Graphics package offers two methods to combine multiple plots. `par()` can be used to set graphical parameters regarding plot layout using the mfcol and mfrow arguments. `layout()` serves the same purpose but offers more flexibility by allowing us to modify the height and width of rows and columns.

`par()` allows us to customize the graphical parameters(title, axis, font, color, size) for a particular session. For combining multiple plots, we can use the graphical parameters mfrow and mfcol. These two parameters create a matrix of plots filled by rows and columns respectively. Let us combine plots using both the above parameters.

|Option|Description|Arguments|
|:-------|:--------|:-----|
|mfrow  |Fill by rows     |Number of rows and columns|
|mfcol  |Fill by columns  |Number of rows and columns|


mfrow combines plots filled by rows i.e it takes two arguments, the number of rows and number of columns and then starts filling the plots by row. Below is the syntax for mfrow.

```{r facetsyntax, eval=FALSE}
# mfrow syntax
mfrow(number of rows, number of columns)
```

Let us begin by combining 4 plots in 2 rows and 2 columns:

## Case Study 1

Let us begin by combining 4 plots in 2 rows and 2 columns. The plots will be filled by rows as we are using the mfrow function:

```{r facet1,fig.align='center',fig.height=7,fig.width=7, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Case Study 1'}
# store the current parameter settings in init
init <- par(no.readonly=TRUE)
 
# specify that 4 graphs to be combined and filled by rows
par(mfrow = c(2, 2))
 
# specify the graphs to be combined
plot(mtcars$mpg)
plot(mtcars$disp, mtcars$mpg)
hist(mtcars$mpg)
boxplot(mtcars$mpg)
 
# restore the setting stored in init
par(init)
```

## Case Study 2

Combine 2 plots in 1 row and 2 columns. 

```{r facet2,fig.align='center',fig.height=7,fig.width=7, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Case Study 2'}
# store the current parameter settings in init
init <- par(no.readonly=TRUE)
 
# specify that 2 graphs to be combined and filled by rows
par(mfrow = c(1, 2))
 
# specify the graphs to be combined
hist(mtcars$mpg)
boxplot(mtcars$mpg)
 
# restore the setting stored in init
par(init)
```

## Case Study 3

Combine 2 plots in 2 rows and 1 column. 

```{r facet3,fig.align='center',fig.height=7,fig.width=7, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Case Study 3'}
# store the current parameter settings in init
init <- par(no.readonly=TRUE)
 
# specify that 2 graphs to be combined and filled by rows
par(mfrow = c(2, 1))
 
# specify the graphs to be combined
hist(mtcars$mpg)
boxplot(mtcars$mpg)
 
# restore the setting stored in init
par(init)
```

## Case Study 4

Combine 3 plots in 1 row and 3 columns. 

```{r facet4,fig.align='center',fig.height=7,fig.width=7, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Case Study 4'}
# store the current parameter settings in init
init <- par(no.readonly=TRUE)
 
# specify that 3 graphs to be combined and filled by rows
par(mfrow = c(1, 3))
 
# specify the graphs to be combined
plot(mtcars$disp, mtcars$mpg)
hist(mtcars$mpg)
boxplot(mtcars$mpg)
 
# restore the setting stored in init
par(init)
```

## Case Study 5

Combine 3 plots in 3 rows and 1 column. 

```{r facet5,fig.align='center',fig.height=7,fig.width=7, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Case Study 5'}
# store the current parameter settings in init
init <- par(no.readonly=TRUE)
 
# specify that 3 graphs to be combined and filled by rows
par(mfrow = c(3, 1))
 
# specify the graphs to be combined
plot(mtcars$disp, mtcars$mpg)
hist(mtcars$mpg)
boxplot(mtcars$mpg)
 
# restore the setting stored in init
par(init)
```

## mfcol

mfcol combines plots filled by columns i.e it takes two arguments, the number of rows and number of columns and then starts filling the plots by columns. Below is the syntax for mfrow:

```{r facetsyntax2, eval=FALSE}
# mfcol syntax
mfcol(number of rows, number of columns)
```

Let us begin by combining 4 plots in 2 rows and 2 columns:

## Case Study 6

Combine 3 plots in 3 rows and 1 column. 

```{r facet6,fig.align='center',fig.height=7,fig.width=7, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Case Study 6'}
# store the current parameter settings in init
init <- par(no.readonly=TRUE)
 
# specify that 4 graphs to be combined and filled by columns 
par(mfcol = c(2, 2))
 
# specify the graphs to be combined
plot(mtcars$mpg)
plot(mtcars$disp, mtcars$mpg)
hist(mtcars$mpg)
boxplot(mtcars$mpg)
 
# restore the setting stored in init
par(init)
```

## Special Cases

What happens if we specify lesser or more number of graphs? In the next two examples, we will specify lesser or more number of graphs than we ask the par() function to combine. Let us see what happens in such instances:

Case 1: Lesser number of graphs specified
We will specify that 4 plots need to be combined in 2 rows and 2 columns but provide only 3 graphs.

Case 2: Extra graph specified
We will specify that 4 plots need to be combined in 2 rows and 2 columns but specify 6 graphs instead of 4.


## Case Study 7

```{r facet7,fig.align='center',fig.height=7,fig.width=7, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Case Study 7'}
 store the current parameter settings in init
init <- par(no.readonly=TRUE)
 
# specify that 4 graphs to be combined and filled by rows
par(mfrow = c(2, 2))
 
# specify the graphs to be combined
plot(mtcars$disp, mtcars$mpg)
hist(mtcars$mpg)
boxplot(mtcars$mpg)
 
# restore the setting stored in init
par(init)
```

## Case Study 8

```{r facet8,fig.align='center',fig.height=7,fig.width=7, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Case Study 8'}
# store the current parameter settings in init
init <- par(no.readonly=TRUE)
 
# specify that 4 graphs to be combined and filled by rows
par(mfrow = c(2, 2))
 
# specify the graphs to be combined
plot(mtcars$mpg)
plot(mtcars$disp, mtcars$mpg)
hist(mtcars$mpg)
boxplot(mtcars$mpg)
plot(mtcars$disp, mtcars$mpg)
boxplot(mtcars$mpg)

# restore the setting stored in init
par(init)
```