---
title: "Intro to tibbles - Part 2"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(tibble)
library(dplyr)
tutorial_options(exercise.timelimit = 0, exercise.cap = 'Sandbox')
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

## Membership Testing

We can test if an object is a tibble using `is_tibble()`.

### Instructions

<hr>

- use `is_tibble()` to test if `mtcars` is a tibble
- coerce `mtcars` to a tibble using `as_tibble()` and then repeat the above step

```{r tibbles15, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'tribble'}
is_tibble()
is_tibble()
```

```{r tibbles15-solution}
is_tibble(mtcars)
is_tibble(as_tibble(mtcars))
```

## Column Names

Names of columns in tibbles need not be valid R variable names. They may contain unusual characters such as a smiley or a space but must be enclosed in ticks.

### Instructions

<hr>

- create a tibble with 3 columns using `tibble()`
- the column names must be 
    - space
    - 2
    - :)

```{r tibbles14, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'tribble'}
tibble(
 


)
```

```{r tibbles14-solution}
tibble(
  ` ` = 'space',
  `2` = 'integer',
  `:)` = 'smiley'
)
```

## Add Rows

### Introduction

<hr>

Rows and columns can be added to a tibble using 

- `add_row()`
- `add_column()`

Let us say we have a tibble with data about website traffic driven by different browsers.

```{r browsers, echo=TRUE, collapse=FALSE}
browsers <- enframe(c(chrome = 40, firefox = 20))
browsers
```

Now, if we want to add another row of data for Internet Explorer, we can use `add_row()`

```{r browsers2, eval=TRUE, echo=TRUE}
add_row(browsers, name = 'IE', value = 30)
```

### Instructions

<hr>

- add data related to **Safari** browser to the web traffic data 
- set `name` to `'Safari'`
- and `value` to `10`

```{r tibbles17, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'tribble'}
browsers <- add_row(browsers, name = , value = )
browsers
```

```{r tibbles17-solution}
add_row(browsers, name = 'safari', value = 10)
```

In order to add the rows or columns at a specific index, use the following arguments

- `.before`
- `.after`

If we want to add the data at a particular row, we can specify the row number using the `.before` argument. Let us add the data related to Internet Explorer in the second row instead of the last row.

```{r browsers3, eval=TRUE, echo=TRUE}
add_row(browsers, name = "IE", value = 30, .before = 2)
```

If we want to add the data at a particular row, we can specify the row number using the `.after` argument. Let us add the data related to Internet Explorer after the first row.

```{r browsers4, eval=TRUE, echo=TRUE}
add_row(browsers, name = "IE", value = 30, .after = 1)
```

### Instructions

<hr>

- add data related to **Safari** browser to the web traffic data 
- set `name` to `'Safari'`
- and `value` to `10`
- add data after the second row

```{r tibbles18, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'tribble'}
add_row(browsers, name = , value = , .after = )
```

```{r tibbles18-solution}
add_row(browsers, name = "safari", value = 10, .after = 2)
```

## Add Columns

### Introduction

<hr>


## Rownames

<hr>

The [tibble](tibble.tidyverse.org) package provides a set of functions to deal with rownames. Remember, `tibble` does not have `rownames` unlike `data.frame`. To check whether a data set has rownames, use `has_rownames()`.

```{r tibble25, eval=TRUE, echo=TRUE}
has_rownames(mtcars)
```

### Instructions

<hr>

## Remove Rownames

<hr>

```{r tibble26, eval=TRUE, echo=TRUE}
remove_rownames(mtcars)
```

### Instructions

<hr>


## Rownames to Column

<hr>

```{r tibble27, eval=TRUE, echo=TRUE}
head(rownames_to_column(mtcars))
```

### Instructions

<hr>


## Column to Rownames

<hr>

To convert the first column in the data set to rownames, use `column_to_rownames()`:

```{r tibble28, eval=TRUE, echo=TRUE}
mtcars_tbl <- rownames_to_column(mtcars)
column_to_rownames(mtcars_tbl)
```

### Instructions

<hr>


## Glimpse

<hr>

Use `glimpse()` to get an overview of the data.

```{r tibble 29, eval=TRUE, echo=TRUE}
glimpse(mtcars)
```

### Instructions

<hr>


## Check Column 

<hr>

`has_name()` can be used to check if a tibble has a specific column.

```{r tibble30, eval=TRUE, echo=TRUE}
has_name(mtcars, 'cyl')
has_name(mtcars, 'gears')
```

### Instructions

<hr>


## Summary

### Manipulating tibbles

<hr>

- use `add_row()` to add a new row
- use `add_column()` to add a new column
- use `remove_rownames()` to remove rownames from data
- use `rownames_to_colum()` to coerce rowname to first column
- use `column_to_rownames()` to coerce first column to rownames

### Miscellaneous

<hr>

- use `is_tibble()` to test if an object is a tibble
- use `has_rownames()` to check whether a data set has rownames
- use `has_name()` to check if tibble has a specific column 
- use `glimpse()` to get an overview of data
