---
title: "Legends - Part 2"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)
year <- seq(2010, 2014, 1)
india <- c(10.3, 6.6, 5.6, 6.6, 7.2)
china <- c(10.6, 9.5, 7.8, 7.7, 7.3)
russia <- c(4.5, 4.3, 3.5, 1.3, 0.7)
brazil <- c(7.5, 3.9, 1.9, 3.0, 0.1)
s_africa <- c(3.2, 3.2, 2.2, 2.2, 1.5)
gdp <- data.frame(year, india, china, russia, brazil, s_africa, stringsAsFactors = FALSE)
```

## Introduction

<hr>

Learn to add legend to a plot using the `legend()` function. Specifically

- position the legend within the plot
- modify the layout using `ncol` and `horiz` arguments
- add title using the `title.` set of arguments
- modify the appearance and position of the legend box
- modify the appearance of the text in the legend box

## Title

### Introduction

<hr>

```{r leg8, fig.align='center', fig.height=4, fig.width=6, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Title'}
{plot(gdp$year, gdp$india, type = 'l', ylim = c(-5, 15), xlab = 'Year',
      ylab = 'Growth Rate', col = 'blue', main = 'BRICS: Growth Rate')
lines(gdp$year, gdp$china, col = 'red')
legend(x = 2012, y = 14, legend = c('india', 'china'),
       lty = 1, col = c('blue', 'red'), title = 'Nations')}
```

## Title Color

<hr>

```{r leg9, fig.align='center', fig.height=4, fig.width=6, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Title Color'}
{plot(gdp$year, gdp$india, type = 'l', ylim = c(-5, 15), xlab = 'Year',
      ylab = 'Growth Rate', col = 'blue', main = 'BRICS: Growth Rate')
lines(gdp$year, gdp$china, col = 'red')
legend(x = 2012, y = 3, legend = c('india', 'china'), lty = 1, 
      col = c('blue', 'red'), title = 'Nations', title.col = 'red')}
```

## Title Position - 1

<hr>

```{r leg11, fig.align='center', fig.width=7, fig.height=10, echo=FALSE, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Title Position'}
init <- par(no.readonly = TRUE)
par(mfrow = c(2, 2))
values <- c(0.2, 0.4, 0.6, 0.8)
for (i in values) {
  plot(gdp$year, gdp$india, type = 'l',
      ylim = c(-5, 15), xlab = 'Year',
      ylab = 'Growth Rate', col = 'blue',
      main = 'BRICS: Growth Rate')
  lines(gdp$year, gdp$china, col = 'red')
  legend(x = 2010, y = 0, legend = c('india', 'china'),
       lty = 1, col = c('blue', 'red'), horiz = TRUE,
       title = 'Nations', title.adj = i)
  mtext(paste("title.adj = ", i), side = 3, col = "blue")
}
```

## Title Position - 2

<hr>

```{r leg10, fig.align='center', fig.height=4, fig.width=6, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Title Position'}
{plot(gdp$year, gdp$india, type = 'l', ylim = c(-5, 15), xlab = 'Year',
      ylab = 'Growth Rate', col = 'blue', main = 'BRICS: Growth Rate')
lines(gdp$year, gdp$china, col = 'red')
legend(x = 2012, y = 3, legend = c('india', 'china'), lty = 1, 
      col = c('blue', 'red'), horiz = TRUE, title = 'Nations', title.adj = 0.1)}
```

## Box Appearance

### Syntax

<hr>

```{r kable, echo=FALSE}
option <- c('Box Type', 'Background Color', 'Border Line Type',
            'Border Line Width', 'Border Line Color', 
            'Horizontal Justification', 'Vertical Justification',
            'Text Color', 'Text Font')
argument <- c('bty', 'bg', 'box.lty', 'box.lwd', 'box.col',
              'xjust', 'yjust', 'text.col', 'text.font')
values <- c('o, n', 'blue, #0000ff', '1:5', '0.5, 1, 1.5',
            'blue, #0000ff', '0:1', '0:1', 'blue, #0000ff',
            '1:5')
legend <- data.frame(option, argument, values)
knitr::kable(legend, format = "markdown", caption = "Legend Box Options")
```

## Box Type

<hr>

```{r leg12, fig.align='center', fig.width=7, fig.height=5, echo=FALSE, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Box Type'}
init <- par(no.readonly = TRUE)
par(mfrow = c(1, 2))
values <- c('o', 'n')
for (i in values) {
  plot(gdp$year, gdp$india, type = 'l',
      ylim = c(-5, 15), xlab = 'Year',
      ylab = 'Growth Rate', col = 'blue',
      main = 'BRICS: Growth Rate')
  lines(gdp$year, gdp$china, col = 'red')
  legend(x = 2012, y = 0, legend = c('india', 'china'),
       lty = 1, col = c('blue', 'red'), bty = i,
       title = 'Nations')
  mtext(paste("bty = ", i), side = 3, col = "blue")
}
```

## Background Color

<hr>

```{r leg13, fig.align='center', fig.height=4, fig.width=6, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Background Color'}
{plot(gdp$year, gdp$india, type = 'l', ylim = c(-8, 15), xlab = 'Year',
      ylab = 'Growth Rate', col = 'blue', main = 'BRICS: Growth Rate')
lines(gdp$year, gdp$china, col = 'red')
legend(x = 2012, y = 3, legend = c('india', 'china'),
       lty = 1, col = c('blue', 'red'), bg = '#ffff66', title = 'Nations')}
```

## Border

### Introduction

<hr>

The following arguments can be used to modify the border of the legend box:

- `box.lty`: line type
- `box.lwd`: line width
- `box.col`: color

### Border

<hr>

```{r leg14, fig.align='center', fig.height=4, fig.width=6, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Border'}
{plot(gdp$year, gdp$india, type = 'l', ylim = c(-8, 15), xlab = 'Year',
      ylab = 'Growth Rate', col = 'blue', main = 'BRICS: Growth Rate')
lines(gdp$year, gdp$china, col = 'red')
legend(x = 2012, y = 3, legend = c('india', 'china'),
       lty = 1, col = c('blue', 'red'), title = 'Nations',
       box.lty = 3, box.lwd = 1.5, box.col = 'green')}
```

## Horizontal Justification

<hr>
 
```{r leg15, fig.align='center', fig.width=7, fig.height=7, echo=FALSE, , exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Horizontal Justification'}
init <- par(no.readonly = TRUE)
par(mfrow = c(1, 3))
values <- c(0, 0.5, 1)
for (i in values) {
  plot(gdp$year, gdp$india, type = 'l',
      ylim = c(-5, 15), xlab = 'Year',
      ylab = 'Growth Rate', col = 'blue',
      main = 'BRICS: Growth Rate')
  lines(gdp$year, gdp$china, col = 'red')
  legend(x = 2012, y = 0, legend = c('india', 'china'),
       lty = 1, col = c('blue', 'red'), xjust = i,
       title = 'Nations')
  mtext(paste("xjust = ", i), side = 3, col = "blue")
}
```

## Vertical Justification

<hr>

```{r leg16, fig.align='center', fig.width=7, fig.height=7, echo=FALSE, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Vertical Justification'}
init <- par(no.readonly = TRUE)
par(mfrow = c(1, 3))
values <- c(0, 0.5, 1)
for (i in values) {
  plot(gdp$year, gdp$india, type = 'l',
      ylim = c(-5, 15), xlab = 'Year',
      ylab = 'Growth Rate', col = 'blue',
      main = 'BRICS: Growth Rate')
  lines(gdp$year, gdp$china, col = 'red')
  legend(x = 2012, y = 0, legend = c('india', 'china'),
       lty = 1, col = c('blue', 'red'), yjust = i,
       title = 'Nations')
  mtext(paste("xjust = ", i), side = 3, col = "blue")
}
```


## Text Appearance

<hr>

```{r leg17, fig.align='center', fig.height=4, fig.width=6, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Text Appearance'}
{plot(gdp$year, gdp$india, type = 'l', ylim = c(-8, 15), xlab = 'Year',
      ylab = 'Growth Rate', col = 'blue', main = 'BRICS: Growth Rate')
lines(gdp$year, gdp$china, col = 'red')
legend(x = 2012, y = 3, legend = c('india', 'china'),
       lty = 1, col = c('blue', 'red'), title = 'Nations',
       text.col = 'green', text.font = 3)}
```

