---
title: "Box Plot - Part 2"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)
mpg_split <- split(mtcars$mpg, mtcars$cyl)
```

## Outliers - 1

<hr>

#### Introduction

<hr>

```{r box9, fig.align='center', fig.width=6, fig.height=5, echo=FALSE, eval=TRUE}
init <- par(no.readonly = TRUE)
par(mfrow = c(1, 2))
values <- c(TRUE, FALSE)
for (i in values) {
  boxplot(mtcars$mpg, outline = i, range = 1)
  mtext(paste("outline = ", i), side = 3, col = "blue")
}
```

## Outliers - 2

#### Introduction

<hr>

Box plots are extremely useful when it comes to detecting outliers in data. If you want the plot to display the outliers,
set the `outline` argument to `TRUE`.

<br>

#### Example

<hr>

```{r box18, eval=FALSE, echo=TRUE}
boxplot(mtcars$mpg, outline = TRUE)
```

<br>

#### Instructions

<hr>

- apply the `boxplot()` function to `disp` variable from the `mtcars` data
- set the value of `outline` to `TRUE`

<br>

#### Script

<hr>

```{r box8, fig.align='center', fig.width=5, fig.height=5, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Outliers'}
# plot outliers
```

```{r box8-solution}
boxplot(mtcars$disp, range = 1, outline = FALSE)
```


## Compare Distributions - 1

<hr>

#### Introduction

<hr>

Another reason box plots are very popular is because they allow us to compare the distribution of continuous data across 
different categories. Let us say we want to compare the distribution of miles per gallon across different cylinder types.

<br>

#### Example

<hr>

```{r box19, eval=FALSE, echo=TRUE}
boxplot(mtcars$mpg ~ mtcars$cyl)
```

<br>

#### Instructions

<hr>

- compare distribution of `mpg` across different `gear` types

<br>

#### Script

<hr>

```{r box11, fig.align='center', fig.width=5, fig.height=5, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Box Plot'}
# compare distribution of mpg across gear types

```

```{r box11-solution}
boxplot(mtcars$mpg ~ mtcars$gear)
```


## Compare Distributions - 2

<hr>

#### Introduction

<hr>

In the previous section, we used a continuous variable and a categorical variable to compare distribution of the continuous variable across different categories. What if you had 3 continuous variable instead of a grouping variable? How would you create the box plot in such cases?

<br>

#### Example

<hr>

```{r box20, eval=FALSE, echo=TRUE}
mpg_split <- split(mtcars$mpg, mtcars$cyl)
mpg_4 <- mpg_split$`4`
mpg_6 <- mpg_split$`6`
mpg_8 <- mpg_split$`8`
boxplot(mpg_4, mpg_6, mpg_8)
```

<br>

#### Instructions

<hr>

<br>

#### Script

<hr>

```{r box13, fig.align='center', fig.width=5, fig.height=5, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Box Plot'}
mpg_split <- split(mtcars$mpg, mtcars$cyl)
mpg_split
mpg_4 <- mpg_split$`4`
mpg_6 <- mpg_split$`6`
mpg_8 <- mpg_split$`8`
boxplot(mpg_4, mpg_6, mpg_8)
```

```{r box13-solution}
boxplot(mpg_4, mpg_6, mpg_8)
```


## Color 

<hr>

#### Introduction

<hr>

Use the `col` argument to add color to a boxplot. 

<br>

#### Example

<hr>

```{r box21, eval=FALSE, echo=TRUE}
boxplot(mtcars$mpg ~ mtcars$cyl, col = 'blue')
```

<br>

#### Instructions

<hr>

- set `col` to `'blue`' and run the code
- next specify different colors to the boxes in the plot (red, blue and yellow)

<br>

#### Script

<hr>

```{r box14, fig.align='center', fig.width=5, fig.height=5, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Color'}
# modify box color to blue

# modify box color to red, blue and yellow
```

```{r box14-solution}
boxplot(mtcars$mpg ~ mtcars$cyl, col = 'blue')
boxplot(mtcars$mpg ~ mtcars$cyl, 
        col = c('red', 'blue', 'yellow'))
```

## Compare Medians

<hr>

```{r box16, fig.align='center', fig.width=5, fig.height=5, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Compare Medians'}
hsb <- read.table('https://stats.idre.ucla.edu/wp-content/uploads/2016/02/hsb2-2.csv', header=T, sep=",")
boxplot(hsb$read ~ hsb$female, notch = TRUE, 
        col = c('red', 'blue'))
```

## Practice

<hr>

```{r box17, fig.align='center', fig.width=5, fig.height=5, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Title & Axis Labels'}
boxplot(mtcars$mpg ~ mtcars$cyl, range = 1, outline = TRUE, 
        horizontal = TRUE, col = c('red', 'blue', 'yellow'),
        main = 'Miles Per Gallon by Cylinders', 
        ylab = 'Number of Cylinders', xlab = 'Miles Per Gallon',
        names = c('Four', 'Six', 'Eight'))
```

