---
title: "Readable Code with Pipes"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(dplyr)
library(magrittr)
knitr::opts_chunk$set(echo = FALSE)
ecom <- readr::read_csv('https://raw.githubusercontent.com/rsquaredacademy/datasets/master/web.csv')
```

## Introduction

<hr>

When you are dealing with a sequence of multiple operations, R code can get a bit cramped and not so easy on the eyes. The [magrittr](https://CRAN.R-project.org/package=magrittr) package by Stefan Milton Bache provides pipes enabling us to write R code that is readable.

- especially useful when you have nested functions
- similar in spirit to javascript's method chaining
- functions taking multiple arguments can be confusing and messy to read
- with magrittr, you program from left to right

## Data Extraction

### Introduction

<hr>

- `extract()`
- `extract2()`
- `use_series()`

## Extract Column By Name

<hr>

```{r mag10, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Extract Column'}
head(ecom['n_pages'], 3)

ecom %>%
  extract('n_pages') %>%
  head(3)
```

## Extract Column By Position

<hr>

```{r mag23, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Extract Column'}
head(ecom[6], 3)

ecom %>%
  extract(6) %>%
  head(3)
```

## Extract Column (as vector)

<hr>

```{r mag11, , exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Extract Column'}
head(ecom$n_pages)

ecom %>%
  use_series('n_pages') %>%
  head()
```

## Extract List Element By Name

<hr>

```{r mag12, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Extract List Element'}
mt <- as.list(mtcars)

mt[['mpg']]

mt %>%
  extract2('mpg')
```

## Extract List Element By Position

<hr>

```{r mag13, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Extract List Element'}
mt <- as.list(mtcars)

mt[[1]]

mt %>%
  extract2(1)
```

## Extract List Element (as vector)

<hr>

```{r mag14, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Extract List Element'}
mt <- as.list(mtcars)

mt$mpg

mt %>%
  use_series(mpg)
```

