---
title: "Hacking strings with stringr"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(stringr)
library(tibble)
library(magrittr)
library(purrr)
library(dplyr)
knitr::opts_chunk$set(echo = FALSE)
mockstring <- readr::read_csv("https://raw.githubusercontent.com/rsquaredacademy/datasets/master/mock_strings.csv")
```

## Introduction

<hr>

In this module, we will learn to work with string data in R using [stringr](http://stringr.tidyverse.org). As we did in the earlier modules, we will use a case study to explore the various features of the stringr package. You can
download the data for the case study from [here](https://raw.githubusercontent.com/rsquaredacademy/datasets/master/mock_strings.csv) or directly import the data using the readr package.  Let us begin by installing and loading stringr and a set of other pacakges we will be using.

## Extract File Type - Introduction

### Introduction

<hr>

```{r str14, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Extract File Type'}
mockstring$url[1:3]
```

## Extract File Type - Steps

### Introduction

<hr>

- check if there are only 2 dots in the URL
- check if there is only 1 question mark in the URL
- detect the location of the second dot 
- detect the location of the first question mark
- use the locations to specify the index position for extracting file type

## Extract File Type - Step 1

### Check if there are only 2 dots in the URL

<hr>

### Instructions 

<hr>

```{r str9, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'File Type - Step 1'}
mockstring$url[1:3] %>%
  str_locate_all(pattern = "\\.") %>%
  map_int(nrow) %>%
  is_greater_than(2) %>%
  sum()
```

## Extract File Type - Step 2

### Check if there is only 1 question mark in the URL

<hr>

### Instructions 

<hr>

```{r str10, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'File Type - Step 2'}  
mockstring$url[1:3] %>%
  str_locate_all(pattern = "[?]") %>%
  map_int(nrow) %>%
  is_greater_than(1) %>%
  sum()
```

## Extract File Type - Step 3

### Detect the location of the second dot

<hr>

### Instructions 

<hr>

```{r str11, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'File Type - Step 3'}
d <- mockstring$url[1:3] %>%
  str_locate_all(pattern = "\\.") %>%
  map_int(extract(2)) %>%
  add(1)

d
```

## Extract File Type - Step 4

### Detect the location of the first question mark

<hr>

### Instructions 

<hr>

```{r str12, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'File Type - Step 4'}
q <- mockstring$url[1:3] %>%
  str_locate_all(pattern = "[?]") %>%
  map_int(extract(1)) %>%
  subtract(1)

q
```

## Extract File Type - Step 5

### Specify the index position for extracting file type

<hr>

### Instructions 

<hr>

```{r str13, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'File Type - Step 5'}
mockstring$url[1:3] %>%
  str_sub(start = d, end = q)
```


