---
title: "ggplot2: Histogram"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(ggplot2)
library(dplyr)
library(tidyr)
knitr::opts_chunk$set(echo = FALSE)
ecom <- readr::read_csv('https://raw.githubusercontent.com/rsquaredacademy/datasets/master/web.csv')
```

## Introduction

### Agenda

<hr>

- build histogram
- specify bins
- modify 
    - color
    - fill
    - alpha
    - bin width
    - line type
    - line size
- map aesthetics to variables

## Data 

### Introduction

<hr>

```{r import, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Data'}
ecom
```

### Data Dictionary

<hr>

- id: row id
- referrer: referrer website/search engine
- os: operating system
- browser: browser
- device: device used to visit the website
- n_pages: number of pages visited
- duration: time spent on the website (in seconds)
- repeat: frequency of visits
- country: country of origin
- purchase: whether visitor purchased
- order_value: order value of visitor (in dollars)


## Histogram

### Introduction

<hr>

```{r hist2, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Histogram'}
ggplot(ecom) +
  geom_histogram(aes(n_visit))
```

### Specify Bins

<hr>

```{r hist4, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Specify Bins'}
ggplot(ecom) +
  geom_histogram(aes(n_visit), bins = 7)
```

### Fill

<hr>

```{r hist3, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Fill'}
ggplot(ecom) +
  geom_histogram(aes(n_visit), bins = 7, fill = 'blue')
```

### Alpha

<hr>

```{r hist11, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Alpha'}
ggplot(ecom) +
  geom_histogram(aes(n_visit), bins = 7, fill = 'blue', alpha = 0.3)
```

### Color

<hr>

```{r hist8, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Color'}
ggplot(ecom) +
  geom_histogram(aes(n_visit), bins = 7, fill = 'white', color = 'blue')
```

### Bins, Color & Fill

<hr>

```{r hist9, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Bins, Color & Fill'}
ggplot(ecom) +
  geom_histogram(aes(n_visit), bins = 7, fill = 'blue', color = 'white')
```


### Bin Width

<hr>

```{r hist5, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Bin Width'}
ggplot(ecom) +
  geom_histogram(aes(n_visit), binwidth = 2, fill = 'blue', color = 'black')
```

### Line Type

<hr>

```{r hist6, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Line Type'}
ggplot(ecom) +
  geom_histogram(aes(n_visit), bins = 5, fill = 'white', 
    color = 'blue', linetype = 3)
```

### Line Size

<hr>

```{r hist10, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Line Size'}
ggplot(ecom) +
  geom_histogram(aes(n_visit), bins = 5, fill = 'white', 
    color = 'blue', size = 1.25)
```

### Map Fill to Variable

<hr>

```{r hist7, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Map Fill to Variable'}
ggplot(ecom) +
  geom_histogram(aes(n_visit, fill = device), bins = 7)
```
