---
title: "How to work with dates in R?"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(lubridate)
library(dplyr)
library(magrittr)
knitr::opts_chunk$set(echo = FALSE)
transact <- readr::read_csv('https://raw.githubusercontent.com/rsquaredacademy/datasets/master/transact.csv')
```

## Introduction

<hr>

 In this module, we will learn to work with date/time data in R using [lubridate]( https://CRAN.R-project.org/package=lubridate), an R package that makes it easy to work with dates and time. Let us begin by installing and loading the lubridate pacakge.


## Leap Year

### Introduction

<hr>

```{r lubb5, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Leap year - Part 1'}
this_day %>%
  year %>%
  leap_year
```


## Practice - I

<hr>

```{r lub5, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Leap year - Part 1'}
transact %>%
  mutate(
    due_year = year(Due),
    is_leap = leap_year(due_year)
  )
```

## Days In Month

### Introduction

<hr>

```{r lubb6, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Leap Year - Part 2'}
this_day %>%
  month %>%
  days_in_month
```

## Practice - II

### Introduction

<hr>

### Instructions

<hr>

```{r lub6, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Leap Year - Part 2'}
transact %>%
  mutate(
    due_day = day(Due),
    due_month = month(Due),
    days_due_month = days_in_month(due_month),
    due_year = year(Due),
    is_leap = leap_year(due_year)
  ) %>%
  select(-(Invoice), -(Payment)) %>%
  filter(due_month == 2)
```

## Shift Date

### Introduction

<hr>

```{r lubb7, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Settlement Date - Part 1'}
# course start date
course_start

# shift date by 2 days
course_start + days(2)

# shift date by 1 week
course_start + weeks(1)

# shift date by 1 year
course_start + years(1)
```

## Interval

### Introduction

<hr>

```{r lubb71, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Settlement Date - Part 1'}
# course interval
interval(course_start, course_end)
```

## Shift Interval

### Introduction

<hr>

```{r lubb72, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Settlement Date - Part 1'}
# shift interval by days
course_interval <- interval(course_start, course_end)
course_interval %>%
  int_shift(by = days(1))

# shift interval by weeks
course_interval %>%
  int_shift(by = weeks(1))

# shift interval by years
course_interval %>%
  int_shift(by = years(1))
```

## Overlapping Intervals

### Introduction

<hr>

```{r lubb73, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Settlement Date - Part 1'}
# overlapping intervals
vacation_start <- as_date('2017-04-19')
vacation_end <- as_date('2017-04-25')
vacation_interval <- interval(vacation_start, vacation_end)
int_overlaps(course_interval, vacation_interval)
```

## Practice - III

### How many invoices were settled within due date?

<hr>

```{r lub7, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Settlement Date - Part 1'}
transact %>%
  mutate(
    inv_due_interval = interval(Invoice, Due),
    due_next = Due + days(1),
    due_pay_interval = interval(due_next, Payment),
    overlaps = int_overlaps(inv_due_interval, due_pay_interval)
  ) %>%
  select(inv_due_interval, due_next, due_pay_interval, overlaps)
```

## Practice - IV

### How many invoices were settled within due date?

<hr>

````{r lub12, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Settlement Date - Part 2'}
# using int_shift
transact %>%
  mutate(
    inv_due_interval = interval(Invoice, Due),
    due_pay_interval = interval(Due, Payment),  
    due_pay_next = int_shift(due_pay_interval, by = days(1)),
    overlaps = int_overlaps(inv_due_interval, due_pay_next)
  ) %>%
  select(inv_due_interval, due_pay_next, overlaps)
```

## Within

### Introduction

<hr>

```{r lubb75, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Settlement Date - Part 3'}
conference <- as_date('2017-04-15')
conference %within% interval(course_start, course_end)
```

## Practice - V

### How many invoices were settled within due date?

<hr>

```{r lub13, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Settlement Date - Part 3'}
transact %>%
  mutate(
    inv_due_interval = interval(Invoice, Due),
    overlaps = Payment %within% inv_due_interval
  ) %>%
  select(Due, Payment, overlaps)
```

