---
title: "Hacking strings with stringr"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(stringr)
library(tibble)
library(magrittr)
library(purrr)
library(dplyr)
knitr::opts_chunk$set(echo = FALSE)
mockstring <- readr::read_csv("https://raw.githubusercontent.com/rsquaredacademy/datasets/master/mock_strings.csv")
```

## Introduction

<hr>

In this module, we will learn to work with string data in R using [stringr](http://stringr.tidyverse.org). As we did in the earlier modules, we will use a case study to explore the various features of the stringr package. You can
download the data for the case study from [here](https://raw.githubusercontent.com/rsquaredacademy/datasets/master/mock_strings.csv) or directly import the data using the readr package.  Let us begin by installing and loading stringr and a set of other pacakges we will be using.


## Extract Image Dimension - Introduction

### Introduction

<hr>

## Extract Image Dimension - Step 1

### Locate numbers in string

<hr>

```{r str_case4_1, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Image Dimension'}
img %>%
  str_locate(pattern = "[0-9]") 
```

## Extract Image Dimension - Step 2

### View Image Dimension

<hr>

```{r str_case4_2, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Image Dimension'}
img %>%
  str_sub(start = 23) 
```

## Extract Image Dimension - Step 3

### Split image dimension and image type

<hr>

```{r str_case4_3, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Image Dimension'}
img %>%
  str_sub(start = 23) %>%
  str_split(pattern = '\\.') 
```

## Extract Image Dimension - Step 4

### Extract image dimension

<hr>

```{r str_case4_4, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Image Dimension'}
img %>%
  str_sub(start = 23) %>%
  str_split(pattern = '\\.') %>%
  map_chr(extract(1))
```

## Extract HTTP Protocol - Introduction
  
### Introduction

<hr>

## Extract HTTP Protocol - Step 1

### View URL

<hr>

### Instructions

<hr>

```{r str_case5_1, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'HTTP Protocol'}
url1 <- mockstring %>%
  pull(url) %>%
  first
url1
```

## Extract HTTP Protocol - Step 2

### Split protocol from rest of the URL

<hr>

### Instructions

<hr>

```{r str_case5_2, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'HTTP Protocol'}
url1 %>%
  str_split(pattern = '://') 
```

## Extract HTTP Protocol - Step 3

### Extract protocol

<hr>

### Instructions

<hr>

```{r str_case5_3, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'HTTP Protocol'}
url1 %>%
  str_split(pattern = '://') %>%
  map_chr(extract(1))
```

