---
title: "Legend - Part 4"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(ggplot2)
library(dplyr)
library(tidyr)
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction

If the aesthetics are mapped to variables, ggplot2 automatically creates legends wherever applicable. 
You may want to modify the appearance of legends. In this module, we will learn to modify the legends when
`size` is mapped to categorical variables.

### Agenda

<hr>

Modify legend when `size` is mapped to variables. Specifically

- title
- breaks
- limits
- range
- labels
- values
- symbol type


## Plot

<hr>

```{r leg36, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Scatter Plot'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, size = hp))
```

## Title

<hr>

```{r leg37, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Legend Title'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, size = hp)) +
  scale_size_continuous(name = "Horsepower")
```

## Range

<hr>

```{r leg38, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Legend Range'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, size = hp)) +
  scale_size_continuous(range = c(3, 6))
```

## Limits

<hr>

```{r leg39, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Legend Limits'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, size = hp)) +
  scale_size_continuous(limits = c(0, 400))
```

## Breaks

<hr>

```{r leg40, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Legend Breaks'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, size = hp)) +
  scale_size_continuous(breaks = c(100, 200, 300, 400))
```

## Labels

<hr>

```{r leg41, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Legend Labels'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, size = hp)) +
  scale_size_continuous(breaks = c(100, 200, 300, 400),
    labels = c("Hundred", "2 Hundred", "3 Hundred", "4 Hundred"))
```

## Summary

<hr>

```{r leg42, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Size Continuous'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, size = hp)) +
  scale_size_continuous(name = "Horsepower", range = c(3, 6), 
    limits = c(0, 400), breaks = c(100, 200, 300, 400),
    labels = c("Hundred", "2 Hundred", "3 Hundred", "4 Hundred"))
```

