---
title: "Legend - Part 4"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(ggplot2)
library(dplyr)
library(tidyr)
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction

If the aesthetics are mapped to variables, ggplot2 automatically creates legends wherever applicable. 
You may want to modify the appearance of legends. In this module, we will learn to modify the legends when
`size` is mapped to categorical variables.

### Agenda

<hr>

Modify legend when `size` is mapped to variables. Specifically

- title
- breaks
- limits
- range
- labels
- values
- symbol type


## Plot

### Introduction

<hr>

```{r leg36, echo=TRUE, collapse=FALSE, fig.align='center'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, size = hp))
```

## Title

### Introduction

<hr>

### Example

<hr>

```{r leg37eg, echo=TRUE, collapse=FALSE, fig.align='center'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, size = hp)) +
  scale_size_continuous(name = "Horsepower")
```

### Instructions

<hr>

```{r leg37, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Legend Title'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, size = hp)) +
  scale_size_continuous(name = "Horsepower")
```

```{r leg37-solution}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, size = hp)) +
  scale_size_continuous(name = "Horsepower")
```

## Range

### Introduction

<hr>

### Example

<hr>

```{r leg38eg, echo=TRUE, collapse=FALSE, fig.align='center'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, size = hp)) +
  scale_size_continuous(range = c(3, 6))
```

### Instructions

<hr>

```{r leg38, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Legend Range'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, size = hp)) +
  scale_size_continuous(range = c(3, 6))
```

```{r leg38-section}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, size = hp)) +
  scale_size_continuous(range = c(3, 6))
```

## Limits

### Introduction

<hr>

### Example

<hr>

```{r leg39eg, echo=TRUE, collapse=FALSE, fig.align='center'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, size = hp)) +
  scale_size_continuous(limits = c(0, 400))
```

### Instructions

<hr>

```{r leg39, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Legend Limits'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, size = hp)) +
  scale_size_continuous(limits = c(0, 400))
```

```{r leg39-section}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, size = hp)) +
  scale_size_continuous(limits = c(0, 400))
```

## Breaks

### Introduction

<hr>

### Example

<hr>

```{r leg40eg, echo=TRUE, collapse=FALSE, fig.align='center'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, size = hp)) +
  scale_size_continuous(breaks = c(100, 200, 300, 400))
```

### Instructions

<hr>

```{r leg40, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Legend Breaks'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, size = hp)) +
  scale_size_continuous(breaks = c(100, 200, 300, 400))
```

```{r leg40-solution}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, size = hp)) +
  scale_size_continuous(breaks = c(100, 200, 300, 400))
```

## Labels

### Introduction

<hr>

### Example

<hr>

```{r leg41eg, echo=TRUE, collapse=FALSE, fig.align='center'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, size = hp)) +
  scale_size_continuous(breaks = c(100, 200, 300, 400),
    labels = c("Hundred", "2 Hundred", "3 Hundred", "4 Hundred"))
```

### Instructions

<hr>

```{r leg41, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Legend Labels'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, size = hp)) +
  scale_size_continuous(breaks = c(100, 200, 300, 400),
    labels = c("Hundred", "2 Hundred", "3 Hundred", "4 Hundred"))
```

```{r leg41-solution}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, size = hp)) +
  scale_size_continuous(breaks = c(100, 200, 300, 400),
    labels = c("Hundred", "2 Hundred", "3 Hundred", "4 Hundred"))
```

## Summary

```{r leg42, echo=TRUE, collapse=FALSE, fig.align='center'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, size = hp)) +
  scale_size_continuous(name = "Horsepower", range = c(3, 6), 
    limits = c(0, 400), breaks = c(100, 200, 300, 400),
    labels = c("Hundred", "2 Hundred", "3 Hundred", "4 Hundred"))
```

