---
title: "Histogram - Part 2"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction

## Intervals

<hr>

We will learn more about frequency density in a bit. Before we end this section, we need to learn about one more way to specify the intervals of the histogram, algorithms. The `hist()` function allows us to specify the following algorithms:

- Sturges (default)
- Scott
- Freedman-Diaconis (FD)

```{r hist10, fig.align='center', fig.width=5, fig.height=5, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Intervals'}
init <- par(no.readonly = TRUE)
par(mfrow = c(1, 3))
values <- c("Sturges", "Scott", "FD")
for (i in values) {
    hist(mtcars$mpg, breaks = i)
    mtext(paste("algo = ", i), side = 3, col = "blue")
}
```

## Frequency Distribution 

<hr>

```{r hist11, fig.align='center', fig.width=5, fig.height=5, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Frequency Distribution'}
init <- par(no.readonly = TRUE)
par(mfrow = c(1, 2))
values <- c(TRUE, FALSE)
for (i in values) {
    hist(mtcars$mpg, freq = i)
    mtext(paste("freq = ", i), side = 3, col = "blue")
}
```

## Probability

<hr>

```{r hist12, fig.align='center', fig.width=5, fig.height=5, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Probability'}
hist(mtcars$mpg, probability = TRUE)
```

## Color

<hr>

```{r hist13, fig.align='center', fig.width=5, fig.height=5, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Color'}
hist(mtcars$mpg, col = 'blue')
```


## Border Color

<hr>

```{r hist16, fig.align='center', fig.width=5, fig.height=5, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Border Color'}
hist(mtcars$mpg, border = c('red', 'blue', 'green', 'yellow', 'brown'))
```

## Labels - 1

<hr>

```{r hist17, fig.align='center', fig.width=5, fig.height=5, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Labels - 1'}
hist(mtcars$mpg, labels = TRUE)
```

## Labels - 2

<hr>

```{r hist18, fig.align='center', fig.width=5, fig.height=5, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Labels - 2'}
hist(mtcars$mpg, labels = c("6", "12", "8", "2", "4"))
```

## Normal Distribution

<hr>

```{r hist1, fig.align='center', fig.width=5, fig.height=5, exercise = TRUE, exercise.eval = TRUE, exercise.cap = 'Normal Distribution'}
hist(rbeta(10000, 5, 5), ann = FALSE, col = 'blue')
```

## Skewed Distribution

<hr>

```{r hist2, fig.align='center', fig.width=10, fig.height=6, exercise = TRUE, exercise.eval = TRUE, exercise.cap = 'Skewed Distribution'}
init <- par(no.readonly = TRUE)
par(mfrow = c(1, 2))
hist(rbeta(10000, 2, 5), ann = FALSE, col = 'blue')
hist(rbeta(10000, 5, 2), ann = FALSE, col = 'blue')
```


## Summary

<hr>

```{r hist19, fig.align='center', fig.width=5, fig.height=5, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Summary'}
hist(mtcars$mpg, labels = TRUE, prob = TRUE,
     ylim = c(0, 0.1), xlab = 'Miles Per Gallon',
     main = 'Distribution of Miles Per Gallon',
     col = rainbow(5))
```
