---
title: "ggplot2: Line Graph"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(ggplot2)
library(dplyr)
library(tidyr)
knitr::opts_chunk$set(echo = FALSE)
gdp <- readr::read_csv('https://raw.githubusercontent.com/rsquaredacademy/datasets/master/gdp.csv')
gdp2 <- gdp %>% 
  select(year, growth, india, china) %>% 
  gather(key = country, value = gdp, -year)
```

## Introduction

<hr>

Line charts are used to examine trend over time.

### Agenda

<hr>

- build 
    - simple line chart
    - grouped line chart
- map aesthetics to variables
- modify line
    - color
    - type
    - size

## Case Study

### Introduction

<hr>

We will use a data set related to GDP growth rate. You can download it from [here](https://github.com/rsquaredacademy/datasets/blob/master/gdp.csv). It contains GDP (Gross Domestic Product) growth data for the BRICS (Brazil, Russia, India, China, South Africa) for the years 2000 to 2005.

### Data

<hr>

```{r import2, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Data'}
gdp
```

## Line Chart

### Introduction

<hr>

```{r line100, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Line Chart'}
ggplot(gdp, aes(year, india)) +
  geom_line()
```

### Line Color

<hr>

```{r line1, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Line Color'}
ggplot(gdp, aes(year, india)) +
  geom_line(color = 'blue')
```

### Line Type

<hr>

- 0 : blank
- 1 : solid
- 2 : dashed
- 3 : dotted
- 4 : dotdash
- 5 : longdash
- 6 : twodash


```{r line2, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Line Type'}
ggplot(gdp, aes(year, india)) +
  geom_line(linetype = 2)
```

### Line Type (Dashed)

<hr>

```{r line3, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Line Type'}
ggplot(gdp, aes(year, india)) +
  geom_line(linetype = 'dashed')
```

### Line Size

<hr>

```{r line4, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Line Size'}
ggplot(gdp, aes(year, india)) +
  geom_line(size = 2)
```

## Modify Data

<hr>

Now let us map the aesthetics to the variables. The data used in the above example cannot be used as we need a variable with country names. We will use `gather()` function from the `tidyr` package to reshape the data.

```{r line5, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Data'}
gdp2
```

### Grouped Line Chart

<hr>

```{r line6, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Grouped Line Chart'}
ggplot(gdp2, aes(year, gdp, group = country)) +
  geom_line()
```

### Map Color to Country

<hr>

```{r line7, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Color'}
ggplot(gdp2, aes(year, gdp, group = country)) +
  geom_line(aes(color = country))
```

### Map Line Type to Country

<hr>

```{r line8, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Line Type'}
ggplot(gdp2, aes(year, gdp, group = country)) +
  geom_line(aes(linetype = country))
```

### Map Line Width to Country

<hr>

```{r line9, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Line Width'}
ggplot(gdp2, aes(year, gdp, group = country)) +
  geom_line(aes(size = country))
```

