---
title: "dplyr Verbs"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(dplyr)
knitr::opts_chunk$set(echo = FALSE)
ecom <- readr::read_csv('https://raw.githubusercontent.com/rsquaredacademy/datasets/master/web.csv')
```


## Introduction

<hr>

According to  a [survey](http://visit.crowdflower.com/rs/416-ZBE-142/images/CrowdFlower_DataScienceReport_2016.pdf) by [CrowdFlower](https://www.crowdflower.com/), data scientists spend most of their time cleaning and manipulating data rather than mining or modeling them for insights. As such, it becomes important to have tools that make data manipulation faster and easier. In today's post, we introduce you to [dplyr](http://dplyr.tidyverse.org/), a grammar of data manipulation.


## AOV by Devices

### Introduction

<hr>

Let us combine all the code from the previous steps:

```{r dplyr17, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'AOV by Devices'}
ecom1 <- filter(ecom, purchase == "true")
ecom2 <- select(ecom1, device, order_value, order_items)
ecom3 <- group_by(ecom2, device)
ecom4 <- summarise_all(ecom3, funs(sum))
ecom5 <- mutate(ecom4, aov = order_value / order_items)
ecom6 <- select(ecom5, device, aov)
ecom6
```

## Using Pipe - Filter

## Using Pipe - Select

## Using Pipe - Group Data

## Using Pipe - Summarize

## Using Pipe - Mutate

## Putting it all together..

<hr>

If you observe, at each step we create a new variable(data frame) and then use it as an input in the next step i.e. the output from one function becomes the input for another function. Can we achieve the final outcome i.e. `ecom6` without creating the intermediate data frames (ecom1 - ecom5)? Yes, we can. We will use the `%>%` operator to chain the above steps so that we can avoid creating the intermediate data frames. Let us see how to do that.

```{r dplyr18, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Solution'}
ecom %>%
  filter(purchase == 'true') %>%
  select(device, order_value, order_items) %>%
  group_by(device) %>%
  summarise_all(funs(sum)) %>%
  mutate(
    aov = order_value / order_items
  ) %>%
  select(device, aov)
```

In the above code, we take the output from each step and use it as an input for the next step using the pipe `%>%` operator. It reduces the intermediate data frames and makes the code readable. Take the `ecom` data frame `->` filter the purchasers `->` select device, order_value and order_items variables `->` group the resulting data frame by device type `->` compute the sum of all the variables in the grouped data frames `->` compute the average order value `->` select device type and aov


It is the same as the steps we wrote at the beginning of this module. Now you realize how powerful dplyr is along with the `%>%` operator. There are other functions in dplyr but we will cover them in another module. You are encouraged to use the above approach to answer the questions we have listed below.

## Practice Questions

<hr>

- what is the average number of pages visited by purchasers and non-purchasers?
- what is the average time on site for purchasers vs non-purchasers?
- what is the average number of pages visited by purchasers and non-purchasers using mobile?
