---
title: "Tutorial"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(dplyr)
knitr::opts_chunk$set(echo = FALSE)
ecom <- readr::read_csv('https://raw.githubusercontent.com/rsquaredacademy/datasets/master/web.csv')
```

## Introduction

In this module, we will explore a set of helper functions in order to:

- extract unique rows 
- rename columns
- sample data
- extract columns
- slice rows
- arrange rows
- compare tables
- extract/mutate data using predicate functions
- count observations for different levels of a variable

## Case Study

### Introduction

<hr>

Let us look at a case study (e-commerce data) and see how we can use dplyr helper functions to answer questions we have about and to modify/transform the underlying data set. You can download the data from [here](https://github.com/rsquaredacademy/datasets/blob/master/web.csv) or import it directly using `read_csv()` from the [readr](readr.tidyverse.org) package.

### Data

<hr>

```{r show, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Data'}
ecom
```

### Data Dictionary

<hr>

- id: row id
- referrer: referrer website/search engine
- os: operating system
- browser: browser
- device: device used to visit the website
- n_pages: number of pages visited
- duration: time spent on the website (in seconds)
- repeat: frequency of visits
- country: country of origin
- purchase: whether visitor purchased
- order_value: order value of visitor (in dollars)


## Data Sanitization

### Introduction

<hr>

### Traffic Sources

<hr>

```{r dplyr2, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Traffic Sources'}
ecom %>%
  distinct(referrer)
```

### Device Types

<hr>

```{r dplyr30, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Device Types'}
ecom %>%
  distinct(device)
```

### Rename Columns

<hr>

```{r dplyr3, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Rename Columns'}
ecom %>%
  rename(time_on_site = duration)
```

## Sampling Data

### Introduction

<hr>

```{r dplyr4, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Sampling - Part 1'}
ecom %>%
  sample_n(700)
```

### Sampling Data

<hr>

```{r dplyr5, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Sampling - Part 2'}
ecom %>%
  group_by(referrer) %>%
  sample_n(100)
```

### Sampling Data

<hr>

```{r dplyr6, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Sampling - Part 3'}
ecom %>%
  sample_frac(size = 0.7)
```

### Sampling Data

<hr>

```{r dplyr7, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Sampling - Part 4'}
ecom %>%
  group_by(referrer) %>%
  sample_frac(0.3)
```


## Extract Columns

### Introduction

<hr>

### Extract Device Column

<hr>

```{r dplyr8, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Extract Column - Part 1'}
ecom %>%
  pull(device)
```

### Extract First Column

<hr>

```{r dplyr9, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Extract Column - Part 2'}
ecom %>%
  pull(1)
```

### Extract Last Column

<hr>

```{r dplyr10, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Extract Column - Part 3'}
ecom %>%
  pull(-1)
```

### Extract First 20 Rows

<hr>

```{r dplyr11, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Extract Column - Part 4'}
ecom %>%
  slice(1:20)
```

### Extract Last Row

<hr>

```{r dplyr12, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Extract Column - Part 5'}
ecom %>%
  slice(n())
```

## Total Observations in Data

<hr>

```{r dplyr13, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Tabulate - Part 1'}
ecom %>%
  tally()
```

### Tabulate Referrers

<hr>

```{r dplyr14, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Tabulate - Part 2'}
ecom %>%
  group_by(referrer) %>%
  tally()
```

### Tabulate referrers and bouncers

<hr>

```{r dplyr15, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Tabulate - Part 3'}
ecom %>%
  group_by(referrer, bouncers) %>%
  tally()
```

### Tabulate referrers and purchasers

<hr>

```{r dplyr16, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Tabulate - Part 4'}
ecom %>%
  group_by(referrer, purchase) %>%
  tally()
```

### Tabulate Referrers & Converts

<hr>

```{r dplyr25, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Tabulate - Part 5'}
ecom %>%
  group_by(referrer, purchase) %>%
  tally() %>%
  filter(purchase == 'true')
```

### Count

<hr>

```{r dplyr17, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Tabulate - Part 6'}
ecom %>%
  count(referrer, purchase)
```

### Top 2 referrers by orders

<hr>

```{r dplyr18, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Tabulate - Part 7'}
ecom %>%
  count(referrer, purchase) %>%
  filter(purchase == 'true') %>%
  arrange(desc(n)) %>%
  top_n(n = 2)
```

## Others

### Between

<hr>

```{r dplyr19, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Between'}
ecom %>%
  pull(n_pages) %>%
  between(5, 15) 
```

### Case When

<hr>

```{r dplyr20}
mtcars %>%
  select(mpg, disp, cyl, gear, carb) %>%
  mutate(
    type = case_when(
      disp > 200 ~ 'High',
      cyl == 8 ~ 'Eight',
      TRUE ~ 'True'
    )
  )
```

### Select First Observation

<hr>

```{r dplyr21, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Select - Part 1'}
ecom %>%
  pull(referrer) %>%
  nth(1)

ecom %>%
  pull(referrer) %>%
  first()
```

### Select 1000th Observation

<hr>

```{r dplyr22, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Select - Part 2'}
ecom %>%
  pull(referrer) %>%
  nth(1000)
```

### Select Last Observation

<hr>

```{r dplyr23, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Select - Part 3'}
ecom %>%
  pull(referrer) %>%
  last()
```