---
title: "Hacking strings with stringr"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(stringr)
library(tibble)
library(magrittr)
library(purrr)
library(dplyr)
knitr::opts_chunk$set(echo = FALSE)
mockstring <- readr::read_csv("https://raw.githubusercontent.com/rsquaredacademy/datasets/master/mock_strings.csv")
```

## Introduction

<hr>

In this module, we will learn to work with string data in R using [stringr](http://stringr.tidyverse.org). As we did in the earlier modules, we will use a case study to explore the various features of the stringr package. You can
download the data for the case study from [here](https://raw.githubusercontent.com/rsquaredacademy/datasets/master/mock_strings.csv) or directly import the data using the readr package.  Let us begin by installing and loading stringr and a set of other pacakges we will be using.


## Case Study

### Introduction

<hr>

- extract domain name from random email ids
- extract image type from url
- extract image dimension from url
- extract extension from domain name
- extract http protocol from url
- extract domain name from url
- extract extension from url
- extract file type from url


## Data

### Introduction

<hr>

```{r show, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Data'}
mockstring
```

### Data Dictionary

<hr>

## Splitting Strings

### Introduction

<hr>

## Extract Domain Name - Part 1

### Let us look at the email column

<hr>

```{r str_case1_1, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Domain Name'}
emails <- mockstring %>%
  pull(email) %>%
  head 
emails
```

## Extract Domain Name - Part 2

### Split user name and domain name

```{r str_case1_2, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Domain Name'}
emails %>%
  str_split(pattern = '@')
```

## Extract Domain Name - Part 3

### Extract domain name

```{r str_case1_3, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Domain Name'}
emails %>%
  str_split(pattern = '@') %>%
  map_chr(2)
```

## Extract Domain Name - Part 4

### Split domain name and extension 

```{r str_case1_4, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Domain Name'}
emails %>%
  str_split(pattern = '@') %>%
  map_chr(2) %>%
  str_split(pattern = '\\.')
```

## Extract Domain Name - Part 5

### Extract domain name

```{r str_case1_5, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Domain Name'}
emails %>%
  str_split(pattern = '@') %>%
  map_chr(2) %>%
  str_split(pattern = '\\.') %>%
  map_chr(extract(1))
```

## Your Turn

### Extract Domain Extension

<hr>

### Instructions 

<hr>

```{r str8, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Domain Extension'}
mockstring$url[1:5] %>%
  str_sub(end = n) %>%
  str_split(pattern = "\\.") %>%
  map_chr(extract(2)) %>%
  str_split(pattern = "/") %>%
  map_chr(extract(1))
```
