---
title: "ggplot2: Geoms"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(ggplot2)
library(dplyr)
knitr::opts_chunk$set(echo = FALSE)
ecom <- readr::read_csv('https://raw.githubusercontent.com/rsquaredacademy/datasets/master/web.csv')
gdp <- readr::read_csv('https://raw.githubusercontent.com/rsquaredacademy/datasets/master/gdp.csv')
```

## Introduction

### Agenda

<hr>

Create some of the most routinely used plots to explore data using the `geom_*` functions:

- Scatter Plot
- Bar Plot
- Box Plot
- Histogram
- Line Chart
- Regression Line

### Data

<hr>

```{r use, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Data'}
ecom
```

### Data Dictionary

<hr>

- id: row id
- referrer: referrer website/search engine
- os: operating system
- browser: browser
- device: device used to visit the website
- n_pages: number of pages visited
- duration: time spent on the website (in seconds)
- repeat: frequency of visits
- country: country of origin
- purchase: whether visitor purchased
- order_value: order value of visitor (in dollars)


## Scatter Plot

### Introduction

<hr>

A scatter plot displays the relationship between two continuous variables. In ggplot2, we can build a scatter plot using `geom_point()`. Scatterplots can show you visually 

- the strength of the relationship between the variables 
- the direction of the relationship between the variables 
- and whether outliers exist

### Point

<hr>

```{r geoms2, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Point'}
ggplot(ecom, aes(x = n_pages, y = duration)) + 
  geom_point()
```

### Regression Line

<hr>

Fit a regression line or using 

- `geom_abline()`
- `geom_smooth()`

### Intercept & Slope

<hr>

```{r geoms5, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Intercept & Slope'}
ggplot(mtcars, aes(x = wt, y = mpg)) +
  geom_point() + 
  geom_abline(intercept = 37.285, slope = -5.344)
```

### Linear Regression

<hr>

```{r geoms6, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Linear Regression'}
ggplot(mtcars, aes(x = wt, y = mpg)) +
  geom_smooth(method = 'lm', se = TRUE)
```

### Loess Regression

<hr>

```{r geoms7, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Loess Regression'}
ggplot(mtcars, aes(x = wt, y = mpg)) +
  geom_smooth(method = 'loess', se = FALSE)
```

### Horizontal/Vertical Lines

<hr>

Add horizontal or vertical lines using

- `geom_hline()`
- `geom_vline()`


### Horizontal Line

<hr>

```{r geoms4, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Horizontal Line'}
ggplot(mtcars, aes(x = wt, y = mpg)) +
  geom_point() +
  geom_hline(yintercept = 30) 
```

### Vertical Line

<hr>

```{r geoms3, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Vertical Line'}
ggplot(mtcars, aes(x = wt, y = mpg)) +
  geom_point() +
  geom_vline(xintercept = 5) 
```

## Bar Plot

### Introduction

<hr>

Bar plots present grouped data with rectangular bars. The bars may represent the frequency of the groups or values. Bar plots can be: 

- horizontal 
- vertical
- grouped
- stacked 
- proportional


### Frequency

<hr>

```{r geoms8, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Frequency'}
ggplot(ecom, aes(x = factor(device))) +
  geom_bar()
```

### Weight

<hr>

```{r geoms9, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Weight'}
ggplot(ecom, aes(x = factor(device))) +
  geom_bar(aes(weight = order_value))
```

### Stacked Bar Plot

<hr>

```{r geoms10, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Stacked Bar Plot'}
ggplot(ecom, aes(x = factor(device))) +
  geom_bar(aes(fill = purchase))
```

### Horizontal Bar Plot

<hr>

```{r geoms11, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Horizontal Bar Plot'}
ggplot(ecom, aes(x = factor(device))) +
  geom_bar(aes(fill = purchase)) +
  coord_flip()
```

### Columns

<hr>

```{r geoms12, fig.align='center', fig.height=4, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Columns'}
device <- c('laptop', 'mobile', 'tablet')
visits <- c(30000, 12000, 5000)
traffic <- tibble::tibble(device, visits)
ggplot(traffic, aes(x = device, y = visits)) +
  geom_col(fill = 'blue') 
```

## Boxplot

### Introduction

<hr>

- examine the distribution of a variable  
- detect outliers, boxplots are very handy

```{r geoms13, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Box Plot'}
ggplot(ecom, aes(x = factor(device), y = n_pages)) +
  geom_boxplot()
```

### Add Jitter

<hr>

```{r geoms14, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Add Jitter'}
ggplot(ecom, aes(x = factor(device), y = n_pages)) +
  geom_boxplot() +
  geom_jitter()
```

## Histogram

### Introduction

<hr>

Histograms are used to examine:

- distribution of a continuous variable
- skewness and kurtosis

```{r geoms15, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Histogram'}
ggplot(ecom, aes(x = duration)) +
  geom_histogram()
```

### Bins

<hr>

```{r geoms16, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Histogram Bins'}
ggplot(ecom, aes(x = duration)) +
  geom_histogram(bins = 5)
```

## Line

### Introduction

<hr>

Line charts are used to examine trends over time.


### Data

<hr>

```{r import2, , exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Data'}
gdp
```

### Line Chart

<hr>

```{r geomline1, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Line Chart'}
ggplot(gdp, aes(year, india)) +
  geom_line()
```

### Line Color & Type 

<hr>

```{r geomline2, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Line Color & type'}
ggplot(gdp, aes(year, india)) +
  geom_line(color = 'blue', linetype = 'dashed')
```

## Jitter

### Introduction

<hr>

```{r geoms17, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Jitter'}
ggplot(ecom, aes(x = factor(device), y = duration)) +
  geom_jitter()
```

### Jitter Width & Height

<hr>

```{r geoms18, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Jitter Width & Height'}
ggplot(ecom, aes(x = factor(device), y = duration)) +
  geom_jitter(width = 0.25, height = 0.5)
```

## Label

<hr>

```{r geoms20, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Label'}
ggplot(mtcars, aes(disp, mpg, label = rownames(mtcars))) +
  geom_label()
```

## Text

### Introduction

<hr>

```{r geoms19, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Text'}
ggplot(mtcars, aes(disp, mpg, label = rownames(mtcars))) +
  geom_text(check_overlap = TRUE, size = 2)
```

### Text

<hr>

```{r geoms21, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Text'}
ggplot(mtcars, aes(x = disp, y = mpg, label = rownames(mtcars))) +
  geom_point() + 
  geom_text(aes(color = cyl), hjust = 0, nudge_x = 0.05, 
            size = 2, angle = 45)
```
