---
title: "Bar Charts - Part 2"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)
cyl_freq <- table(mtcars$cyl)
cyl_gear <- table(mtcars$cyl, mtcars$gear)
```

## Agenda

<hr>

- create 
    - simple bar plot
    - stacked bar plot
    - grouped bar plot
- modify bar
    - direction
    - color
    - line color
    - width
    - labels
- modify axis range
- remove axes from the plot
- specify the line type of the X axes
- offset the Y axes
- modify legend


## Introduction

A bar plot represents data in rectangular bars. The length of the bars are proportional to the values they represent. Bar plots can be either horizontal or vertical. The X axis of the plot represents the levels or the categories and the Y axis represents the frequency/count of the variable. 

## Stacked Bar Plot

<hr>

```{r bar21, fig.align='center', fig.height=5, fig.width=5, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Stacked Bar Plot'}
barplot(cyl_gear)
```

## Grouped Bar Plot

<hr>

```{r bar24, fig.align='center', fig.height=5, fig.width=5, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Grouped Bar Plot'}
barplot(cyl_gear, beside = TRUE)
```


## Color

<hr>

```{r bar22, fig.align='center', fig.height=5, fig.width=5, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Bar Color'}
barplot(cyl_gear, col = c('blue', 'red', 'green'))
```

## Legend

<hr>

```{r bar23, fig.align='center', fig.height=5, fig.width=5, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Legend'}
barplot(cyl_gear, legend.text = TRUE)
```


## Axis Line Type

<hr>

```{r bar16, fig.align='center', fig.height=5, fig.width=5, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Axis Line Type'}
barplot(cyl_freq, axis.lty = 3)
```

## Offset Axes

<hr>

```{r bar17, fig.align='center', fig.height=5, fig.width=5, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Offset Y Axes'}
barplot(cyl_freq, offset = 5)
```

## Remove Axes

<hr>

```{r bar15, fig.align='center', fig.height=5, fig.width=5, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Remove Axes'}
barplot(cyl_freq, axes = FALSE)
```


## Summary

<hr>

```{r bar20, fig.align='center', fig.height=5, fig.width=5, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Title & Axis Labels'}
barplot(cyl_freq, col = c('blue', 'red', 'green'), horiz = TRUE, axis.lty = 2,
        width = c(1, 1, 2), names.arg = c('Four', 'Six', 'Eight'), offset = 2)
title(main = 'Distribution of Cylinders',
      xlab = 'Frequency', ylab = 'Number of Cylinders')
```
