---
title: "Import Data in R - Part 2"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(readxl)
library(haven)
library(foreign)
library(sas7bdat)
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction

<hr>

Importing data is the first step in any data analysis workflow. If you cannot import data from differernt sources or file formats, you cannot proceed with data analysis. R allows you to import data from several sources and a variety of file formats. In this module, we will focus on 

- xls
- xlsx
- SAS
- SPSS
- STATA

## Overview

### Introduction

<hr>

- list sheets in an excel file
- read data from an excel sheet
- read specific cells from an excel sheet
- read a single row
- read a single column
- read several rows
- read several columns

## List Sheets

<hr>

```{r import55, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'List Sheets'}
excel_sheets('sample.xls')
```

## Read Sheet

<hr>

```{r import56, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Read Sheets'}
readxl::read_excel('sample.xls', sheet = 1)
```

## Read Specific Cells - Part 1

### Introduction

<hr>

```{r import58, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Read Specific Cells'}
readxl::read_excel('sample.xls', sheet = 1, range = "B1:C4")
```

### Instructions

<hr>

```{r import59, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Read Specific Cells'}
readxl::read_excel('sample.xls', sheet = 1, range = "A1:C5")
```

## Read Specific Cells - Part 2

<hr>

```{r import61, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Read Specific Cells'}
readxl::read_excel('sample.xls', sheet = 1, col_names = FALSE,
  range = anchored("A4", dim = c(3, 2)))
```

## Read Specific Cells - Part 3

<hr>

```{r import65, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Read Specific Cells'}
readxl::read_excel('sample.xls', sheet = 1,
  range = cell_limits(c(1, 2), c(NA, NA)))
```

## Read Specific Cells - Part 4

### Introduction

<hr>

Use cell_limits to specify one end of the rectangle such as top left or top right.

```{r import66, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Read Specific Cells'}
readxl::read_excel('sample.xls', sheet = 1,
  range = cell_limits(c(1, NA), c(NA, 2)))
```

## Read Single Row

<hr>

```{r import60, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Read Single Row'}
readxl::read_excel('sample.xls', sheet = 1, range = "A1:C4")
```

## Read Single Column

<hr>

```{r import64, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Read Single Column'}
readxl::read_excel('sample.xls', sheet = 1, range = cell_cols(2))
```


## Specify Rows

<hr>

```{r import62, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Specify Rows'}
readxl::read_excel('sample.xls', sheet = 1, range = cell_rows(1:4))
```

## Specify Columns

<hr>

```{r import63, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Specify Columns'}
readxl::read_excel('sample.xls', sheet = 1, range = cell_cols(2:3))
```
