---
title: "ggplot2: Aesthetics"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(ggplot2)
library(dplyr)
library(tidyr)
knitr::opts_chunk$set(echo = FALSE)
# gdp <- readr::read_csv('https://raw.githubusercontent.com/rsquaredacademy/datasets/master/gdp.csv')
# ecom <- readr::read_csv('https://raw.githubusercontent.com/rsquaredacademy/datasets/master/web.csv')
# gdp2 <- gdp %>% 
#  select(year, growth, india, china) %>% 
#  gather(key = country, value = gdp, -year)
```

## Agenda

<hr>

Explore aesthetics such as 

- color
- shape
- size
- fill
- alpha
- width


## Introduction

In this module, we will focus on the aesthetics i.e. color, shape, size, alpha, line type, line width etc. We can map these to variables or specify values for them. If we want to map the above to variables, we have to specify them within the `aes()` function. We will look at both methods.

## Data

### Introduction

<hr>

```{r use, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Data'}
ecom
```

### Data Dictionary

<hr>

- id: row id
- referrer: referrer website/search engine
- os: operating system
- browser: browser
- device: device used to visit the website
- n_pages: number of pages visited
- duration: time spent on the website (in seconds)
- repeat: frequency of visits
- country: country of origin
- purchase: whether visitor purchased
- order_value: order value of visitor (in dollars)


## Color


#### Instructions

<hr>

- map `color` to `cyl`
- set `color` to `'blue'`

```{r aes2, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Color'}
# map color to cyl
ggplot(mtcars, aes(x = disp, y = mpg)) +
  geom_point(____)

# set color to 'blue'
ggplot(mtcars, aes(x = disp, y = mpg)) +
  geom_point(____)
```

```{r aes2-solution}
# map color to cyl
ggplot(mtcars, aes(x = disp, y = mpg)) +
  geom_point(aes(color = cyl))

# set color to 'blue'
ggplot(mtcars, aes(x = disp, y = mpg)) +
  geom_point(color = 'blue')
```


## Shape

<hr>

### Instructions

- map `shape` to `cyl`
- set `shape` to `5`

```{r aes5, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Shape'}
# map shape to cyl
ggplot(mtcars, aes(x = disp, y = mpg)) +
  geom_point(____)

# set shape to 5
ggplot(mtcars, aes(x = disp, y = mpg)) +
  geom_point(____)
```

```{r aes5-solution}
# map shape to cyl
ggplot(mtcars, aes(x = disp, y = mpg)) +
  geom_point(aes(shape = cyl))

# set shape to 5
ggplot(mtcars, aes(x = disp, y = mpg)) +
  geom_point(shape = 5)
```


## Fill

<hr>

### Instructions

- set `fill` to `'blue'`
- map `fill` to `purchase`
- set `color` to `blue`

```{r aes9, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Fill'}
# set fill to 'blue'
ggplot(mtcars, aes(x = disp, y = mpg)) +
  geom_point(shape = 5, fill = ____)

# set fill to 'blue'
ggplot(mtcars, aes(x = disp, y = mpg)) +
  geom_point(shape = 22, fill = ____)

# map fill to purchase
ggplot(ecom) +
  geom_bar(aes(device, fill = ____))

# set color to 'blue'
ggplot(mtcars, aes(x = disp, y = mpg)) +
  geom_point(shape = 22, color = ____)
```

```{r aes9-solution}
ggplot(mtcars, aes(x = disp, y = mpg)) +
  geom_point(shape = 5, fill = 'blue')

ggplot(mtcars, aes(x = disp, y = mpg)) +
  geom_point(shape = 22, fill = 'blue')

ggplot(ecom, aes(device, fill = purchase)) +
  geom_bar()

ggplot(mtcars, aes(x = disp, y = mpg)) +
  geom_point(shape = 22, color = 'blue')
```


## Size

<hr>

### Instructions

- map `size` to `hp`
- set `size` to `4`

```{r aes12, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Size'}
ggplot(mtcars) +
  geom_point(aes(x = disp, y = mpg, ____))

ggplot(mtcars, aes(x = disp, y = mpg)) +
  geom_point(____)
```

```{r aes12-solution}
ggplot(mtcars) +
  geom_point(aes(x = disp, y = mpg, size = hp))

ggplot(mtcars, aes(x = disp, y = mpg)) +
  geom_point(size = 4)
```

## Alpha

<hr>

### Instructions

- map `alpha` to `cyl`
- set `alpha` to `0.3`

```{r aes14, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Alpha'}
ggplot(mtcars, aes(x = disp, y = mpg)) +
  geom_point(aes(______), color = 'blue')
```

```{r aes14-solution}
ggplot(mtcars, aes(x = disp, y = mpg)) +
  geom_point(aes(alpha = factor(cyl)), color = 'blue')
```




