---
title: "Import Data in R - Part 4"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(jsonlite)
library(xml2)
library(XML)
library(tibble)
library(purrr)
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction

<hr>

Importing data is the first step in any data analysis workflow. If you cannot import data from differernt sources or file formats, you cannot proceed with data analysis. R allows you to import data from several sources and a variety of file formats. In this module, we will focus on 

- XML
- JSON
- HTML


## XML - Introduction

## XML - Read Data

<hr>

```{r imp15, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Read XML'}
books <- read_xml('books.xml')
```

## XML - Node Names

<hr>

```{r imp16, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Node Names'}
xml_name(books)
```

## XML - Child Nodes

<hr>

```{r imp17, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Child Nodes'}
xml_children(books)
```

### Child Node

<hr>

```{r imp18, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Child Nodes'}
xml_child(books)
```

## XML - Contents

<hr>

```{r imp19, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Contents'}
xml2::xml_contents(books)
```

## XML - Structure

<hr>

```{r imp21, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Structure'}
xml2::xml_structure(books)
```

## XML - Length

<hr>

```{r imp22, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Length'}
xml2::xml_length(books)
```

## XML - Root Node

<hr>

```{r imp23, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Root Node'}
xml2::xml_root(books)
```

## XML - Attributes

<hr>

```{r imp24, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Attributes'}
xml_find_all(books, './/book') %>% 
  map_chr(xml_attrs)
```

## XML (Web)

<hr>

```{r xmlread, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'XML (Web)'}
xml2::read_xml("http://www.xmlfiles.com/examples/cd_catalog.xml")
```

## JSON

<hr>

```{r imp1, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'JSON'}
jsonlite::fromJSON('mtcars.json')
```


## HTML

<hr>

```{r imp14, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'HTML'}
xml2::read_html("http://r-project.org/")
```