---
title: "Import Data in R - Part 4"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(jsonlite)
library(xml2)
library(XML)
library(tibble)
library(purrr)
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction

<hr>

## XML - Read Data

Reading xml data is the first step in converting it to a tibble or any other required format in R. We will use `read_xml()` from the [xml2](https://cran.r-project.org/package=xml2) package to read data from the xml file.

#### Example

<hr>

```{r imp15-eg, echo=TRUE, eval=FALSE, collapse=FALSE}
read_xml('file_name.xml')
```

<br>

#### Instructions

<hr>

- read data from `books.xml` 

```{r imp15, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Read XML', exercise.lines = 5}
books <- read_xml(________)
```

```{r imp15-solution}
books <- read_xml('books.xml')
```

## XML - Node Names

Alright! Now that we have read the data from the xml file, let us look at the root node.  Use `xml_name()` to get the root node.

#### Example

<hr>

```{r imp16-eg, echo=TRUE, eval=FALSE, collapse=FALSE}
xml_file <- read_xml('file_name.xml')
xml_name(xml_file)
```

<br>

#### Instructions

<hr>

In the previous section, we read data from xml file and stored it in `books`.

- use `xml_name()` to find the root node of `books` 

```{r imp16, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Node Names', exercise.lines = 5}
# find root node of books


```

```{r imp16-solution}
xml_name(books)
```

## XML - Child Nodes

Great! Now that we have identified the root node of the xml data, let us also take a look at the child nodes. Use `xml_child()`
to get the child nodes.

#### Example

<hr>

```{r imp18-eg, echo=TRUE, eval=FALSE, collapse=FALSE}
xml_file <- read_xml('file_name.xml')
xml_child(xml_file)
```

<br>

#### Instructions

<hr>

- use `xml_children()` to find the child nodes of `books`
- use `xml_child()` to examine the contents of a child node of `books`

```{r imp18, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Child Nodes', exercise.lines = 5}
# child nodes of books


# contents of a child node of books

```

```{r imp18-solution}
# child nodes of books
xml_children(books)

# contents of a child node of books
xml_child(books)
```

## XML - Structure

Use `xml_structure()` to view the structure of the xml document. It will not display the values though and is useful to 
get a high level overview.

#### Example

<hr>

```{r imp21-eg, echo=TRUE, eval=FALSE, collapse=FALSE}
xml_file <- read_xml('file_name.xml')
xml_structure(xml_file)
```

<br>

#### Instructions

<hr>

- use `xml_structure()` to view the structure of `books`

```{r imp21, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Structure', exercise.line = 5}
# view structure of books

```

```{r imp21-solution}
xml_structure(books)
```

## XML - Length

Use `xml_length()` to find the number of children nodes in xml document. 

#### Example

<hr>

```{r imp22-eg, echo=TRUE, eval=FALSE, collapse=FALSE}
xml_file <- read_xml('file_name.xml')
xml_length(xml_file)
```

<br>

#### Instructions

<hr>

- use `xml_length()` to find the number of children nodes in `books`

```{r imp22, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Length', exercise.lines = 5}
# find number of children nodes in books

```

```{r imp22-solution}
xml_length(books)
```

## XML - Root Node

Use `xml_root()` to find the root node of the xml document.

#### Example

<hr>

```{r imp23-eg, echo=TRUE, eval=FALSE, collapse=FALSE}
xml_file <- read_xml('file_name.xml')
xml_root(xml_file)
```

<br>

#### Instructions

<hr>

- use `xml_root()` to find the root node of `books`

```{r imp23, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Root Node', exercise.lines = 5}
# find the root node of books
```

```{r imp23-solution}
xml_root(books)
```

## JSON

We can read json data into R using `fromJSON` from the [jsonlite](package).

#### Example

<hr>

```{r imp1-eg, echo=TRUE, eval=FALSE, collapse=FALSE}
fromJSON('file_name.json')
```

#### Instructions

<hr>

- read `mtcars.json` using `fromJSON()` 

```{r imp1, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'JSON', exercise.lines =5}
# read mtcars.json
```

```{r imp1-solution}
fromJSON('mtcars.json')
```

## HTML

We can read html files using `read_html()`.

#### Example

<hr>

```{r imp14-eg, echo=TRUE, eval=FALSE, collapse=FALSE}
read_html('url')
```

#### Instructions

<hr>

- read the html data from [R Project](http://r-project.org/) website

```{r imp14, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'HTML', exercise.lines = 5}
# read html from http://r-project.org/
```

```{r imp14-solution}
xml2::read_html("http://r-project.org/")
```