---
title: "Legends - Part 2"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(ggplot2)
library(dplyr)
library(tidyr)
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction

If the aesthetics are mapped to variables, ggplot2 automatically creates legends wherever applicable. 
You may want to modify the appearance of legends. In this module, we will learn to modify the legends when
`fill` is mapped to categorical variables.

### Agenda

<hr>

Modify legend when `fill` is mapped to variables. Specifically

- title
- breaks
- limits
- labels
- values

## Plot

### Introduction

<hr>

```{r leg22, echo=TRUE, collapse=FALSE, fig.align='center'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, fill = factor(cyl)), shape = 22)
```

## Values

### Introduction

<hr>

### Example

<hr>

```{r leg24eg, echo=TRUE, collapse=FALSE, fig.align='center'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, fill = factor(cyl)), shape = 22) +
  scale_fill_manual(values = c("red", "blue", "green"))
```

### Instructions

<hr>

```{r leg24, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Legend Values'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, fill = factor(cyl)), shape = 22) +
  scale_fill_manual(values = c("red", "blue", "green"))
```

```{r leg24-solution}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, fill = factor(cyl)), shape = 22) +
  scale_fill_manual(values = c("red", "blue", "green"))
```

## Title

### Introduction

<hr>

### Example

<hr>

```{r leg23eg, echo=TRUE, collapse=FALSE, fig.align='center'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, fill = factor(cyl)), shape = 22) +
  scale_fill_manual(name = "Cylinders", 
    values = c("red", "blue", "green"))
```

### Instructions

<hr>

```{r leg23, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Legend Title'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, fill = factor(cyl)), shape = 22) +
  scale_fill_manual(name = "Cylinders", 
    values = c("red", "blue", "green"))
```

```{r leg23-solution}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, fill = factor(cyl)), shape = 22) +
  scale_fill_manual(name = "Cylinders", 
    values = c("red", "blue", "green"))
```

## Labels

### Introduction

<hr>

### Example

<hr>

```{r leg25eg, echo=TRUE, collapse=FALSE, fig.align='center'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, fill = factor(cyl)), shape = 22) +
  scale_fill_manual(values = c("red", "blue", "green"),
    labels = c('Four', 'Six', 'Eight'))
```

### Instructions

<hr>

```{r leg25, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Legend Labels'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, fill = factor(cyl)), shape = 22) +
  scale_fill_manual(values = c("red", "blue", "green"),
    labels = c('Four', 'Six', 'Eight'))
```

```{r leg25-solution}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, fill = factor(cyl)), shape = 22) +
  scale_fill_manual(values = c("red", "blue", "green"),
    labels = c('Four', 'Six', 'Eight'))
```

## Limits

### Introduction

<hr>

### Example

<hr>

```{r leg26eg, echo=TRUE, collapse=FALSE, fig.align='center'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, fill = factor(cyl)), shape = 22) +
  scale_fill_manual(values = c("red", "blue", "green"),
    limits = c(4, 6, 8))
```

### Instructions

<hr>

```{r leg26, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Legend Limits'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, fill = factor(cyl)), shape = 22) +
  scale_fill_manual(values = c("red", "blue", "green"),
    limits = c(4, 6, 8))
```

```{r leg26-solution}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, fill = factor(cyl)), shape = 22) +
  scale_fill_manual(values = c("red", "blue", "green"),
    limits = c(4, 6, 8))
```

## Breaks

### Introduction

<hr>

### Example

<hr>

```{r leg27eg, echo=TRUE, collapse=FALSE, fig.align='center'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, fill = factor(cyl)), shape = 22) +
  scale_fill_manual(values = c("red", "blue", "green"),
    breaks = c(4, 6, 8))
```

### Instructions

<hr>

```{r leg27, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Legend Breaks'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, fill = factor(cyl)), shape = 22) +
  scale_fill_manual(values = c("red", "blue", "green"),
    breaks = c(4, 6, 8))
```

```{r leg27-solution}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, fill = factor(cyl)), shape = 22) +
  scale_fill_manual(values = c("red", "blue", "green"),
    breaks = c(4, 6, 8))
```

## Summary

<hr>

```{r leg28, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Legend Fill'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, fill = factor(cyl)), shape = 22) +
  scale_fill_manual(name = "Cylinders", values = c("red", "blue", "green"),
    labels = c('Four', 'Six', 'Eight'), limits = c(4, 6, 8), breaks = c(4, 6, 8))
```
