---
title: "ggplot2: Legends - Part 2"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(ggplot2)
library(dplyr)
library(tidyr)
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction

### Agenda

<hr>

Learn to modify legend

- title
- label
- bar

## Title

### Introduction

<hr>

- position
    - top
    - bottom
    - left
    - right
- alignment
    - 0 (left)
    - 1 (right)


### Legend Title

<hr>

```{r leg1, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Title'}
ggplot(mtcars) + geom_point(aes(disp, mpg, color = factor(cyl))) +
  scale_color_manual(values = c("red", "blue", "green"),
    guide = guide_legend(title = "Cylinders"))
```

### Title Alignment

<hr>

```{r leg2, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Title Alignment'}
ggplot(mtcars) + geom_point(aes(disp, mpg, color = factor(cyl))) +
  scale_color_manual(values = c("red", "blue", "green"),
    guide = guide_legend(title = "Cylinders", title.hjust = 0.5))
```

### Title Position

<hr>

```{r leg3, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Title Position'}
ggplot(mtcars) + geom_point(aes(disp, mpg, color = factor(cyl))) +
  scale_color_manual(values = c("red", "blue", "green"),
    guide = guide_legend(title = "Cylinders", title.hjust = 0.5, 
      title.position = "top"))
```


## Label

### Introduction

<hr>

- position
    - top
    - bottom
    - left 
    - right
- alignment 
    - 0 (left)
    - 1 (right)
- direction
    - horizontal
    - vertical
- reverse
    - TRUE
    - FALSE
- rows

### Label Position

<hr>

```{r leg4, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Label Position'}
ggplot(mtcars) + geom_point(aes(disp, mpg, color = factor(cyl))) +
  scale_color_manual(values = c("red", "blue", "green"),
    guide = guide_legend(label.position = "right"))
```

### Label Alignment

<hr>

```{r leg5, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Label Alignment'}
ggplot(mtcars) + geom_point(aes(disp, mpg, color = factor(cyl))) +
  scale_color_manual(values = c("red", "blue", "green"),
    guide = guide_legend(label.hjust = 0.5))
```

### Direction

<hr>

```{r leg6, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Direction'}
ggplot(mtcars) + geom_point(aes(disp, mpg, color = factor(cyl))) +
  scale_color_manual(values = c("red", "blue", "green"),
    guide = guide_legend(direction = "horizontal"))
```

### Rows

<hr>

```{r leg7, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Rows'}
ggplot(mtcars) + geom_point(aes(disp, mpg, color = factor(cyl))) +
  scale_color_manual(values = c("red", "blue", "green"),
    guide = guide_legend(nrow = 2))
```

### Reverse

<hr>

```{r leg8, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Reverse'}
ggplot(mtcars) + geom_point(aes(disp, mpg, color = factor(cyl))) +
  scale_color_manual(values = c("red", "blue", "green"),
    guide = guide_legend(reverse = TRUE))
```

### Guides

<hr>

```{r leg20, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Guides'}
ggplot(mtcars) + geom_point(aes(disp, mpg, color = factor(cyl))) +
  scale_color_manual(values = c("red", "blue", "green"),
    guide = guide_legend(title = "Cylinders", title.hjust = 0.5, 
      title.position = "top", label.position = "right", 
      direction = "horizontal", label.hjust = 0.5, nrow = 2, reverse = TRUE)
  )
```

### Title Alignment (Vertical)

<hr>

```{r leg22, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Title Alignment'}
ggplot(mtcars) + geom_point(aes(disp, mpg, color = hp)) +
  scale_color_continuous(guide = guide_colorbar(
    title = "Horsepower", title.position = "top", title.vjust = 1))
```

### Labels Alignment (Vertical)

<hr>

```{r leg23, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Label Alignment'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, color = hp)) +
  scale_color_continuous(guide = guide_colorbar(
    label.vjust = 0.8))
```

## Legend Bar 

### Introduction

<hr>

- width
- height
- bins
- ticks
- limits


### Legend Bar Width

<hr>

```{r leg24, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Legend Bar Width'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, color = hp)) +
  scale_color_continuous(guide = guide_colorbar(
    barwidth = 10))
```

### Legend Bar Height

<hr>

```{r leg25, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Legend Bar Height'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, color = hp)) +
  scale_color_continuous(guide = guide_colorbar(
    barheight = 3))
```

### Legend Bar Bins

<hr>

```{r leg26, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Legend Bar Bins'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, color = hp)) +
  scale_color_continuous(guide = guide_colorbar(
    nbin = 4))
```

### Legend Bar Ticks

<hr>

```{r leg28, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Legend Bar Ticks'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, color = hp)) +
  scale_color_continuous(guide = guide_colorbar(
    ticks = FALSE))
```

### Legend Bar Upper/Lower Limits

<hr>

```{r leg29, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Legend Bar limits'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, color = hp)) +
  scale_color_continuous(guide = guide_colorbar(
    draw.ulim = TRUE, draw.llim = FALSE))
```

### Guides

<hr>

```{r leg34, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Guides'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, color = hp, 
    size = qsec, shape = factor(gear))) + 
  guides(color = "colorbar", shape = "legend", size = "legend")
```

### Guides: Color, Shape & Size

<hr>

```{r leg35, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Guides: Color, Shape & Size'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, color = hp, size = wt, shape = factor(gear))) + 
  guides(color = guide_colorbar(title = "Horsepower"),
    shape = guide_legend(title = "Weight"), size = guide_legend(title = "Gear")
  )
```