---
title: "Introduction to R"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
tutorial_options(exercise.timelimit = 0, exercise.cap = 'Sandbox')
knitr::opts_chunk$set(echo = FALSE)
```

## How It Works

In the editor on the right you should type R code to solve the exercises. When you hit the 'Submit Answer' button, every line of code is interpreted and executed by R and you get a message whether or not your code was correct. The output of your R code is shown in the console in the lower right corner.

R makes use of the # sign to add comments, so that you and others can understand what the R code is about. Just like Twitter! Comments are not run as R code, so they will not influence your result. For example, Calculate 3 + 4 in the editor on the right is a comment.

You can also execute R commands straight in the console. This is a good way to experiment with R code, as your submission is not checked for correctness.

#### Instructions

- In the editor on the right there is already some sample code. Can you see which lines are actual R code and which are comments?

- Add a line of code that calculates the sum of 6 and 12, and hit the 'Submit Answer' button.


```{r howit, exercise=TRUE, exercise.eval = TRUE, exercise.cap = 'How It Works'}
3 + 4  # calculate 3 + 4
```

```{r howitworks, exercise=TRUE, exercise.eval = FALSE, exercise.cap = 'How It Works'}
# calculate 6 + 12

```

```{r howitworks-hint}
Just add a line of R code that calculates the sum of 6 and 12, just like the example in the sample code!
```

```{r howitworks-solution}
6 + 12
```

## Arithmetic With R

In the most basic form, R can be used as a calculator. Consider the following arithmetic operations:

- Addition:`+`
- Subtraction:`-`
- Multiplication:`*`
- Division:`/`
- Exponentiation:`^`
- Modulo:`%%`

The last two might need some explaining:

- The `^` operator raises the number to its left to the power of the number to its right: for example `3 ^ 2` is 9.
- The modulo returns the remainder of the division of the number to the left by the number on its right, for example `5 modulo 3` or `5 %% 3` is 2.

```{r addition, exercise=TRUE, exercise.eval = TRUE, exercise.cap = 'Addition'}
5 + 5 
```

```{r subtraction, exercise=TRUE, exercise.eval = TRUE, exercise.cap = 'Subtraction'}
5 - 5 
```

```{r multiplication, exercise=TRUE, exercise.eval = TRUE, exercise.cap = 'Multiplication'}
3 * 5 
```

```{r division, exercise=TRUE, exercise.eval = TRUE, exercise.cap = 'Division'}
(5 + 5) / 2 
```

With this knowledge, follow the instructions below to complete the exercise.

#### Instructions

- Type `2 ^ 5` in the editor to calculate 2 to the power 5.
- Type `28 %% 6` to calculate 28 modulo 6.
- Click 'Run Code' and have a look at the R output in the console.
- Note how the # symbol is used to add comments on the R code.

### Exercise 

```{r exponentiation, exercise=TRUE, exercise.eval = TRUE, exercise.cap = 'Exercise'}
# Exponentiation

```

```{r exponentiation-hint}
Another example of the modulo operator: 5 ^ 2 equals 25
```

```{r exponentiation-solution}
2 ^ 5
```

```{r modulo, exercise=TRUE, exercise.eval = TRUE, exercise.cap = 'Exercise'}
# modulo

```

```{r modulo-hint}
Another example of the modulo operator: 9 %% 2 equals 1
```

```{r modulo-solution}
28 %% 6  
```

## Variable Assignment

A basic concept in (statistical) programming is called a variable.

A variable allows you to store a value (e.g. 4) or an object (e.g. a function description) in R. You can then later use this variable's name to easily access the value or the object that is stored within this variable.

You can assign a value 4 to a variable **my_var** with the command `my_var <- 4`.

#### Instructions

Over to you: complete the code in the editor such that it assigns the value 42 to the variable x in the editor. Click 'Run Code'. Notice that when you ask R to print x, the value 42 appears.


```{r assign, exercise=TRUE, exercise.eval = FALSE, exercise.cap = 'Assign'}
# Assign the value 42 to x
x <- 
```

```{r assign-hint}
Look at how the value 4 was assigned to my_variable in the exercise's assignment. Do the exact same thing in the editor, but now assign 42 to the variable x.
```

```{r assign-solution}
x <- 42
```

```{r print, exercise=TRUE, exercise.eval = FALSE, exercise.cap = 'Print'}
# Print out the value of the variable x
x
```

## Variable Assignment - 2

Suppose you have a fruit basket with five apples. As a data analyst in training, you want to store the number of apples in a variable with the name my_apples.

#### Instructions

- Type the following code in the editor: `my_apples <- 5`. This will assign the value 5 to my_apples.
- Type: my_apples below the second comment. This will print out the value of my_apples.
- Click 'Run Code', and look at the console: you see that the number 5 is printed. So R now links the variable my_apples to the value 5.


```{r assign2, exercise=TRUE, exercise.eval = FALSE, exercise.cap = 'Assign'}
# Assign the value 5 to the variable my_apples

```

```{r assign2-hint}
Remember that if you want to assign a number or an object to a variable in R, you can make use of the assignment operator <-. Alternatively, you can use =, but <- is widely preferred in the R community.
```

```{r assign2-solution}
my_apples <- 5
```


```{r assign3, exercise=TRUE, exercise.eval = FALSE, exercise.cap = 'Assign'}
# Print out the value of the variable my_apples

```

```{r assign3-hint}
Remember that if you want to print a variable, you just type the name of the variable in the console.
```

```{r assign3-solution}
my_apples
```

## Variable Assignment - 3

Every tasty fruit basket needs oranges, so you decide to add six oranges. As a data analyst, your reflex is to immediately create the variable `my_oranges` and assign the value 6 to it. Next, you want to calculate how many pieces of fruit you have in total. Since you have given meaningful names to these values, you can now code this in a clear way: `my_apples + my_oranges`.

#### Instructions

- Assign to `my_oranges` the value 6.
- Add the variables `my_apples` and `my_oranges` and have R simply print the result.
- Assign the result of adding `my_apples` and `my_oranges` to a new variable `my_fruit`.

```{r assign4, exercise=TRUE, exercise.eval = FALSE, exercise.cap = 'Assign'}
my_apples <- 5

# Assign to my_oranges the value 6.

# Add these two variables together

# Create the variable my_fruit 

```

```{r assign4-solution}
my_oranges <- 6
my_apples + my_oranges
myfruit <- my_apples + my_oranges
```

## Apples & Oranges

Common knowledge tells you not to add apples and oranges. But hey, that is what you just did, no :-)? The `my_apples` and `my_oranges` variables both contained a number in the previous exercise. The `+` operator works with numeric variables in R. If you really tried to add "apples" and "oranges", and assigned a text value to the variable `my_oranges` (see the editor), you would be trying to assign the addition of a numeric and a character variable to the variable `my_fruit`. This is not possible.

#### Instructions

- Click 'Run Code' and read the error message. Make sure to understand why this did not work.
- Adjust the code so that R knows you have 6 oranges and thus a fruit basket with 11 pieces of fruit.

```{r appanges, exercise=TRUE, exercise.eval = FALSE, exercise.cap = 'Data Types'}
# Assign a value to the variable my_apples
my_apples <- 5 

# Fix the assignment of my_oranges
my_oranges <- "six" 

# Create the variable my_fruit and print it out
my_fruit <- my_apples + my_oranges 
my_fruit
```

```{r appanges-solution}
my_oranges <- 6
```

## Data Types

R works with numerous data types. Some of the most basic types to get started are:

- Decimals values like `4.5` are called numerics.
- Natural numbers like `4` are called integers. Integers are also numerics.
- Boolean values (`TRUE` or `FALSE`) are called logical.
- Text (or string) values are called characters.

Note how the quotation marks on the right indicate that "some text" is a character.

#### Instructions

Change the value of the:

- `my_numeric` variable to `42`.
- `my_character` variable to `"universe"`. Note that the quotation marks indicate that `"universe"` is a character.
- `my_logical` variable to `FALSE`.

Note that R is case sensitive!

```{r dtypes, exercise=TRUE, exercise.eval = FALSE, exercise.cap = 'Data Types'}
# Change my_numeric to be 42
my_numeric <- 42.5
my_numeric

# Change my_character to be "universe"
my_character <- "some text"
my_character

# Change my_logical to be FALSE
my_logical <- TRUE
my_logical
```

```{r dtypes-solution}
my_numeric <- 42
my_character <- "universe"
my_logical <- FALSE
```

## Data Types - 2

Do you remember that when you added `5 + "six"`, you got an error due to a mismatch in data types? You can avoid such embarrassing situations by checking the data type of a variable beforehand. You can do this with the `class()` function, as the code on the right shows.

#### Instructions

Complete the code in the editor and also print out the classes of `my_character` and `my_logical`.

```{r dtypes2, exercise=TRUE, exercise.eval = FALSE, exercise.cap = 'Data Types'}
# Declare variables of different types
my_numeric <- 42
my_character <- "universe"
my_logical <- FALSE 

# Check class of my_numeric
class(my_numeric)

# Check class of my_character


# Check class of my_logical

```

```{r dtypes2-solution}
class(my_character)
class(my_logical)
```

### Quiz

```{r quiz-dplyr}
quiz(caption = 'Quiz 1',
  question("Which is the verb used to filter data in dplyr?",
    answer("select"),
    answer("mutate"),
    answer("filter", correct = TRUE),
    answer("slice"),
    incorrect = 'Incorrect. The verb is `filter`.',
    allow_retry = TRUE,
    random_answer_order = TRUE
  ),
  question("Which is the verb used to create and retain only new variables?",
    answer("transmute", correct = TRUE),
    answer("mutate", message = 'mutate retains variables. The correct verb is transmute.'),
    answer("select"),
    answer("slice"),
    incorrect = 'Incorrect. The verb is `transmute`.',
    allow_retry = TRUE,
    random_answer_order = TRUE
  )
)
```

