---
title: "Facet - Part 2"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction

At the core of the layout() function is a matrix. We communicate the structure in which the plots must be combined using a matrix. As such, the layout function is more flexible compared to the par() function.

|Option|Description|Value|
|:-------|:--------|:-----|
|matrix  |matrix specifying location of plants     |matrix|
|widths  |width of columns  |vector|
|heights  |height of rows  |vector|

Let us begin by combining 4 plots in a 2 row/2 column structure. We do this by creating a layout using the matrix function.

## Case Study 1

Combine 4 plots in 2 rows/2 columns filled by rows.

```{r facet1,fig.align='center',fig.height=7,fig.width=7, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Case Study 1'}
# specify the layout
# 4 plots to be combined in 2 row/ 2 columns and arranged by row
layout(matrix(c(1, 2, 3, 4), nrow = 2, byrow = TRUE))
 
# specify the 4 plots
plot(mtcars$disp, mtcars$mpg)
hist(mtcars$mpg)
boxplot(mtcars$mpg)
plot(mtcars$mpg)
```

## Case Study 2

Combine 4 plots in 2 rows/2 columns filled by columns

To fill the plots by column, we specify byrow = FALSE in the matrix.

```{r facet2,fig.align='center',fig.height=7,fig.width=7, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Case Study 2'}
# specify the layout
# 4 plots to be combined in 2 row/ 2 columns and filled by columns
layout(matrix(c(1, 2, 3, 4), nrow = 2, byrow = FALSE))
 
# specify the 4 plots
plot(mtcars$disp, mtcars$mpg)
hist(mtcars$mpg)
boxplot(mtcars$mpg)
plot(mtcars$mpg)
```

## Case Study 3

Combine 3 plots in 2 rows/2 columns filled by rows

The magic of the layout() function begins here. We want to combine 3 plots and the first plot should occupy both the columns in row 1 and the next 2 plots should be in row 2. If you look at the matrix below, 1 is specified twice and since the matrix is filled by row, it will occupy both the columns in the first row. Similarly the first plot will occupy the entire first row. It will be crystal clear when you see the plot.


```{r facet3,fig.align='center',fig.height=7,fig.width=7, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Case Study 3'}
# specify the matrix
> matrix(c(1, 1, 2, 3), nrow = 2, byrow = TRUE)
     [,1] [,2]
[1,]    1    1
[2,]    2    3

# 3 plots to be combined in 2 row/ 2 columns and arranged by row
layout(matrix(c(1, 1, 2, 3), nrow = 2, byrow = TRUE))
 
# specify the 3 plots
plot(mtcars$disp, mtcars$mpg)
hist(mtcars$mpg)
boxplot(mtcars$mpg)
```

## Case Study 4

Combine 3 plots in 2 rows/2 columns filled by rows

The plots must be filled by rows and the third plot must occupy both the columns of the second row while the other two plots will be placed in the first row. The matrix would look like this:

```{r facet4,fig.align='center',fig.height=7,fig.width=7, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Case Study 4'}
# specify the matrix
> matrix(c(1, 2, 3, 3), nrow = 2, byrow = TRUE)
     [,1] [,2]
[1,]    1    2
[2,]    3    3

# 3 plots to be combined in 2 row/ 2 columns and arranged by row
layout(matrix(c(1, 2, 3, 3), nrow = 2, byrow = TRUE))
 
# specify the 3 plots
hist(mtcars$mpg)
boxplot(mtcars$mpg)
plot(mtcars$disp, mtcars$mpg)
```

## Case Study 5

Combine 3 plots in 2 rows/2 columns filled by columns

The plots must be filled by columns and the first plot must occupy both the rows of the first column while the other two plots will be placed in the second column in two rows. The matrix would look like this:


```{r facet5,fig.align='center',fig.height=7,fig.width=7, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Case Study 5'}
# specify the matrix
> matrix(c(1, 1, 2, 3), nrow = 2, byrow = FALSE)
     [,1] [,2]
[1,]    1    2
[2,]    1    3

# 3 plots to be combined in 2 row/ 2 columns and arranged by columns
layout(matrix(c(1, 1, 2, 3), nrow = 2, byrow = FALSE))
 
# specify the 3 plots
hist(mtcars$mpg)
plot(mtcars$disp, mtcars$mpg)
boxplot(mtcars$mpg)
```

## Case Study 6

Combine 3 plots in 2 rows/2 columns filled by columns

The plots must be filled by columns and the first plot must occupy both the rows of the second column while the other two plots will be placed in the first column in two rows. The matrix would look like this:


```{r facet6,fig.align='center',fig.height=7,fig.width=7, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Case Study 6'}
# specify the matrix
> matrix(c(1, 2, 3, 3), nrow = 2, byrow = FALSE)
     [,1] [,2]
[1,]    1    3
[2,]    2    3

# 3 plots to be combined in 2 row/ 2 columns and arranged by columns
layout(matrix(c(1, 2, 3, 3), nrow = 2, byrow = FALSE))
 
# specify the 3 plots
boxplot(mtcars$mpg)
plot(mtcars$disp, mtcars$mpg)
hist(mtcars$mpg)
```

## Widths

In all the layouts created so far, we have kept the size of the rows and columns equal. What if you want to modify the width and height of the columns and rows? The widths and heights arguments in the layout() function address the above mentioned issue. Let us check them out one by one:
The widths argument is used for specifying the width of the columns. Based on the number of columns in the layout, you can specify the width of each column. Let us look at some examples.

## Case Study 7

Width of the 2nd column is twice the width of the 1st column

```{r facet7,fig.align='center',fig.height=7,fig.width=7, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Case Study 7'}
# specify the matrix
> matrix(c(1, 2, 3, 4), nrow = 2, byrow = TRUE)
     [,1] [,2]
[1,]    1    3
[2,]    2    4

# 4 plots to be combined in 2 row/ 2 columns and arranged by columns
layout(matrix(c(1, 2, 3, 4), nrow = 2, byrow = TRUE), widths = c(1, 3))
 
# specify the plots
plot(mtcars$disp, mtcars$mpg)
hist(mtcars$mpg)
boxplot(mtcars$mpg)
plot(mtcars$mpg)
```

## Case Study 8

Width of the 2nd column is twice that of the first and last column

```{r facet8,fig.align='center',fig.height=7,fig.width=7, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Case Study 8'}
# specify the matrix
> matrix(c(1, 2, 3, 4, 5, 6), nrow = 2, byrow = TRUE)
     [,1] [,2] [,3]
[1,]    1    2    3
[2,]    4    5    6


# 6 plots to be combined in 2 row/ 3 columns and filled by rows
layout(matrix(c(1, 2, 3, 4, 5, 6), nrow = 2, byrow = TRUE), widths = c(1, 2, 1))
 
# specify the plots
plot(mtcars$disp, mtcars$mpg)
hist(mtcars$mpg)
boxplot(mtcars$mpg)
plot(mtcars$mpg)
hist(mtcars$mpg)
boxplot(mtcars$mpg)
```

## Heights

The heights arguments is used to modify the height of the rows and based on the number of rows specified in the layout, we can specify the height of each row. 

## Case Study 9

Height of the 2nd row is twice that of the first row

```{r facet9,fig.align='center',fig.height=7,fig.width=7, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Case Study 9'}
# 4 plots to be combined in 2 row/ 2 columns and filled by rows
layout(matrix(c(1, 2, 3, 4), nrow = 2, byrow = TRUE), heights= c(1, 2))
 
# specify the 4 plots
plot(mtcars$disp, mtcars$mpg)
hist(mtcars$mpg)
boxplot(mtcars$mpg)
plot(mtcars$mpg)
```

## Putting it all together...

Before we end this section, let us combine plots using both the widths and heights option

```{r facet10,fig.align='center',fig.height=7,fig.width=7, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Case Study 10'}
# specify the matrix
> matrix(c(1, 2, 3, 4, 5, 6), nrow = 3, byrow = TRUE)
     [,1] [,2]
[1,]    1    2
[2,]    3    4
[3,]    5    6

# 6 plots to be combined in 3 row/ 2 columns and arranged by rows
layout(matrix(c(1, 2, 3, 4, 5, 6), nrow = 3, byrow = TRUE), heights= c(1, 2, 1),
widths = c(2, 1))
 
# specify the 6 plots
plot(mtcars$disp, mtcars$mpg)
hist(mtcars$mpg)
boxplot(mtcars$mpg)
plot(mtcars$mpg)
hist(mtcars$mpg)
boxplot(mtcars$mpg)
```
