---
title: "Themes - Part 2"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(ggplot2)
library(dplyr)
library(tidyr)
knitr::opts_chunk$set(echo = FALSE)
```
## Introduction

### Agenda

<hr>

Use `theme()` to modify the appearance of legend

- background
- margin
- spacing
- key
- text
- title
- position
- direction
- box

## Plot

### Introduction

<hr>

### Example

<hr>

```{r theme7eg, echo=TRUE, collapse=FALSE, fig.align='center'}
p <- ggplot(mtcars) +
  geom_point(aes(disp, mpg, color = factor(cyl), shape = factor(gear)))
p
```

### Instructions

<hr>

```{r theme7, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Legend'}
p <- ggplot(mtcars) +
  geom_point(aes(disp, mpg, color = factor(cyl), shape = factor(gear)))
p
```

```{r theme7-solution}
p <- ggplot(mtcars) +
  geom_point(aes(disp, mpg, color = factor(cyl), shape = factor(gear)))
p
```

## Background 

### Introduction

<hr>

### Example

<hr>

```{r theme30eg, echo=TRUE, collapse=FALSE, fig.align='center'}
p + theme(legend.background = element_rect(fill = 'gray', linetype = 3,  
          color = "black"))
```

### Instructions

<hr>

```{r theme30, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Background'}
p + theme(legend.background = element_rect(fill = 'gray', linetype = 3,  
          color = "black"))
```

```{r theme30-solution}
p + theme(legend.background = element_rect(fill = 'gray', linetype = 3,  
          color = "black"))
```

## Margin 

### Introduction

<hr>

### Example

<hr>

```{r theme31eg, echo=TRUE, collapse=FALSE, fig.align='center'}
p + theme(legend.margin = margin(4, 8, 4, 8))
```

### Instructions

<hr>

```{r theme31, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Margin'}
p + theme(legend.margin = margin(4, 8, 4, 8))
```

```{r theme31-solution}
p + theme(legend.margin = margin(4, 8, 4, 8))
```

## Spacing 

### Introduction

<hr>

### Example

<hr>

```{r theme32eg, echo=TRUE, collapse=FALSE, fig.align='center'}
p + theme(legend.spacing = unit(1.5, "cm"))
```

### Instructions

<hr>

```{r theme32, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Spacing'}
p + theme(legend.spacing = unit(1.5, "cm"))
```

```{r theme32-solution}
p + theme(legend.spacing = unit(1.5, "cm"))
```

## Key 

### Introduction

<hr>

### Example

<hr>

```{r theme33eg, echo=TRUE, collapse=FALSE, fig.align='center'}
p + theme(legend.key = element_rect(fill = 'red'),
          legend.key.size = unit(0.4, "cm"))
```

### Instructions

<hr>

```{r theme33, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Key'}
p + theme(legend.key = element_rect(fill = 'red'),
          legend.key.size = unit(0.4, "cm"))
```

```{r theme33-solution}
p + theme(legend.key = element_rect(fill = 'red'),
          legend.key.size = unit(0.4, "cm"))
```

## Text 

### Introduction

<hr>

### Example

<hr>

```{r theme34eg, echo=TRUE, collapse=FALSE, fig.align='center'}
p + theme(legend.text = element_text(color = 'green', face = 'italic'))
```

### Instructions

<hr>

```{r theme34, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Text'}
p + theme(legend.text = element_text(color = 'green', face = 'italic'))
```

```{r theme34-solution}
p + theme(legend.text = element_text(color = 'green', face = 'italic'))
```

## Title 

### Introduction

<hr>

### Example

<hr>

```{r theme35eg, echo=TRUE, collapse=FALSE, fig.align='center'}
p + theme(legend.title = element_text(color = 'blue', face = 'bold'),
          legend.title.align = 0.1)
```

### Instructions

<hr>

```{r theme35, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Title'}
p + theme(legend.title = element_text(color = 'blue', face = 'bold'),
          legend.title.align = 0.1)
```

```{r theme35-solution}
p + theme(legend.title = element_text(color = 'blue', face = 'bold'),
          legend.title.align = 0.1)
```

## Position 

### Introduction

<hr>

### Example

<hr>

```{r theme36eg, echo=TRUE, collapse=FALSE, fig.align='center'}
p + theme(legend.position = "top")
```

### Instructions

<hr>

```{r theme36, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Position'}
p + theme(legend.position = "top")
```

```{r theme36-solution}
p + theme(legend.position = "top")
```

## Direction 

### Introduction

<hr>

### Example

<hr>

```{r theme37eg, echo=TRUE, collapse=FALSE, fig.align='center'}
p + theme(legend.direction = "horizontal")
```

### Instructions

<hr>

```{r theme37, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Direction'}
p + theme(legend.direction = "horizontal")
```

```{r theme37-solution}
p + theme(legend.direction = "horizontal")
```

## Box 

### Introduction

<hr>

### Example

<hr>

```{r theme38eg, echo=TRUE, collapse=FALSE, fig.align='center'}
p + theme(legend.box = "horizontal",
  legend.box.background = element_rect(fill = "gray"),
  legend.box.spacing = unit(1, "cm"), legend.box.just = "left",
  legend.box.margin = margin(4, 8, 4, 8))
```

### Instructions

<hr>

```{r theme38, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Box'}
p + theme(legend.box = "horizontal",
  legend.box.background = element_rect(fill = "gray"),
  legend.box.spacing = unit(1, "cm"), legend.box.just = "left",
  legend.box.margin = margin(4, 8, 4, 8))
```

```{r theme38-solution}
p + theme(legend.box = "horizontal",
  legend.box.background = element_rect(fill = "gray"),
  legend.box.spacing = unit(1, "cm"), legend.box.just = "left",
  legend.box.margin = margin(4, 8, 4, 8))
```