---
title: "ggplot2: Bar Chart"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(ggplot2)
library(dplyr)
library(tidyr)
knitr::opts_chunk$set(echo = FALSE)
ecom <- readr::read_csv('https://raw.githubusercontent.com/rsquaredacademy/datasets/master/web.csv')
```

## Introduction

### Agenda

<hr>

- build 
    - simple bar plot
    - stacked bar plot
    - grouped bar plot
    - proportional bar plot
- map aesthetics to variables
- specify values for 
    - bar color
    - bar line color
    - bar line type
    - bar line size



## Data

### Introduction

<hr>

```{r import2, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Data'}
ecom
```

### Data Dictionary

<hr>

- id: row id
- referrer: referrer website/search engine
- os: operating system
- browser: browser
- device: device used to visit the website
- n_pages: number of pages visited
- duration: time spent on the website (in seconds)
- repeat: frequency of visits
- country: country of origin
- purchase: whether visitor purchased
- order_value: order value of visitor (in dollars)

## Aesthetics

### Introduction

<hr>

- `fill`
- `color`
- `linetype`
- `size`
- `position`

### Simple Bar Plot

<hr>

```{r bar2, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Bar Plot'}
ggplot(ecom) +
  geom_bar(aes(factor(device)))
```

### Bar Color

<hr>

```{r bar3, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Bar Color'}
ggplot(ecom) +
  geom_bar(aes(factor(device)),
           fill = c('red', 'blue', 'green'))
```

### Bar Line Color

<hr>

```{r bar4, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Bar Line Color'}
ggplot(ecom) +
  geom_bar(aes(factor(device)), fill = 'white',
           color = c('red', 'blue', 'green'))
```

### Bar Line Type

<hr>

```{r bar5, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Bar Line Type'}
ggplot(ecom) +
  geom_bar(aes(factor(device)), fill = 'white', 
          color = 'black', linetype = 2)
```

### Bar Line Size

<hr>

```{r bar6, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Bar Line Size'}
ggplot(ecom) +
  geom_bar(aes(factor(device)), fill = 'white', 
           color = 'black', size = 2)
```

### Stacked Bar Plot

<hr>

```{r bar7, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Stacked Bar Plot'}
ggplot(ecom) +
  geom_bar(aes(device, fill = factor(referrer)))
```

### Grouped Bar Plot

<hr>

```{r bar8, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Grouped Bar Plot'}
ggplot(ecom) +
  geom_bar(aes(device, fill = factor(referrer)), position = 'dodge')
```

### Proportional Bar Plot

<hr>

```{r bar10, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Proportional Bar Plot'}
ggplot(ecom) +
  geom_bar(aes(device, fill = factor(referrer)), position = 'fill')
```


### Horizontal Bar Plot

<hr>

```{r bar9, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Horizontal Bar Plot'}
ggplot(ecom) +
  geom_bar(aes(factor(device), fill = factor(referrer))) +
  coord_flip()
```

