---
title: "ggplot2: Statistical Plots"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(ggplot2)
library(dplyr)
library(tidyr)
knitr::opts_chunk$set(echo = FALSE)
ecom <- readr::read_csv('https://raw.githubusercontent.com/rsquaredacademy/datasets/master/web.csv')
```

## Introduction

So far we have used `geom_*()` functions to build plots. Now we will use a new set of functions `stat_*()`: 

- `stat_count()`
- `stat_boxplot()`
- `stat_identity()`
- `stat_bin()`
- `stat_unique()`

### Agenda

<hr>

Explore the following functions to build plots based on statistical transformation:

- `stat_count()`
- `stat_boxplot()`
- `stat_identity()`
- `stat_bin()`
- `stat_unique()`


## Data 

### Introduction

<hr>

```{r import, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Data'}
ecom
```

### Data Dictionary

<hr>

- id: row id
- referrer: referrer website/search engine
- os: operating system
- browser: browser
- device: device used to visit the website
- n_pages: number of pages visited
- duration: time spent on the website (in seconds)
- repeat: frequency of visits
- country: country of origin
- purchase: whether visitor purchased
- order_value: order value of visitor (in dollars)


## Bar Plots

<hr>

```{r stat2, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Bar Plot'}
ggplot(ecom) +
  stat_count(aes(device))
```

## Box Plots

<hr>

```{r stat3, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Box Plot'}
ggplot(ecom) +
  stat_boxplot(aes(factor(1), n_visit))
```

## Scatter Plots

<hr>

```{r stat4, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Scatter Plot'}
ggplot(ecom) +
  stat_identity(aes(n_pages, duration), position = 'jitter')
```

## Histogram

<hr>

```{r stat5, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Histogram'}
ggplot(ecom) +
  stat_bin(aes(n_visit), bins = 7, fill = 'blue', alpha = 0.3,
           color = 'black')
```

## Unique Values

<hr>

```{r stat6, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Unique Values'}
ggplot(ecom) +
  stat_unique(aes(n_pages, duration), 
              position = 'jitter')
```

