---
title: "ggplot2: Guides and Axes"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(ggplot2)
library(dplyr)
library(tidyr)
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction

### Agenda

<hr>

Modify X and Y axis

- title
- labels
- limits
- breaks
- position

In this module, we will learn how to modify the X and Y axis using the following functions:

- Continuous Axis
    - `scale_x_continuous()`
    - `scale_y_continuous()`

- Discrete Axis
    - `scale_x_discrete()`
    - `scale_y_discrete()`


## Continuous 

### X Axis

<hr>

`scale_x_continuous()` and `scale_y_continuous()` take the following arguments:

- name
- limits
- breaks
- labels
- position

### Scatter Plot

<hr>

```{r guide2, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Scatter Plot'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg))
```

### Axis Label

<hr>

```{r guide3, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Axis Label'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg)) +
  scale_x_continuous(name = "Displacement")
```

### Axis Limits

<hr>

```{r guide4, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Axis Limits'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg)) +
  scale_x_continuous(limits = c(0, 600))
```

### Axis Breaks

<hr>

```{r guide5, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Axis Breaks'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg)) +
  scale_x_continuous(breaks = c(0, 150, 300, 450, 600))
```

### Axis Tick Labels

<hr>

```{r guide6, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Axis Tick Labels'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg)) +
  scale_x_continuous(breaks = c(0, 150, 300, 450, 600),
    labels = c('0', '150', '300', '450', '600'))
```

### Axis Position

<hr>

```{r guide7, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Axis Position'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg)) +
  scale_x_continuous(position = 'top')
```

### X Axis 

<hr>

```{r guide8, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'X Axis'}
ggplot(mtcars) + geom_point(aes(disp, mpg)) +
  scale_x_continuous(name = "Displacement", limits = c(0, 600),
                     breaks = c(0, 150, 300, 450, 600), position = 'top',
                     labels = c('0', '150', '300', '450', '600'))
```


### Y Axis 

<hr>

```{r guide9, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Y Axis - Continuous'}
ggplot(mtcars) + geom_point(aes(disp, mpg)) +
  scale_y_continuous(name = "Miles Per Gallon", limits = c(0, 45),
                     breaks = c(0, 15, 30, 45), position = 'right',
                     labels = c('0', '15', '30', '45'))
```

## Discrete 

### Introduction

<hr>

`scale_x_discrete()` and `scale_y_discrete()` take the following arguments:

- name
- labels
- breaks
- position

### Axis Label

<hr>

```{r guide11, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Axis Label'}
ggplot(mtcars) +
  geom_bar(aes(factor(cyl))) +
  scale_x_discrete(name = "Number of Cylinders")
```

### Axis Tick Labels

<hr>

```{r guide12, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Axis Tick Labels'}
ggplot(mtcars) +
  geom_bar(aes(factor(cyl))) +
  scale_x_discrete(labels = c("4" = "Four", "6" = "Six", "8" = "Eight"))
```

### Axis Breaks

<hr>

```{r guide13, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Axis Breaks'}
ggplot(mtcars) +
  geom_bar(aes(factor(cyl))) +
  scale_x_discrete(breaks = c("4", "6", "8"))
```

### Axis Position

<hr>

```{r guide14, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Axis Position'}
ggplot(mtcars) +
  geom_bar(aes(factor(cyl))) +
  scale_x_discrete(position = 'bottom')
```

### X Axis - Discrete 

```{r guide15, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'X Axis - Discrete'}
ggplot(mtcars) + geom_bar(aes(factor(cyl))) +
  scale_x_discrete(name = "Number of Cylinders",
    labels = c("4" = "Four", "6" = "Six", "8" = "Eight"),
    breaks = c("4", "6", "8"), position = "bottom")
```
