---
title: "Import Data in R - Part 5"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(jsonlite)
library(xml2)
library(XML)
library(tibble)
library(purrr)
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction

<hr>

Importing data is the first step in any data analysis workflow. If you cannot import data from differernt sources or file formats, you cannot proceed with data analysis. R allows you to import data from several sources and a variety of file formats. In this module, we will focus on 

- XML
- JSON
- HTML

## XML - Book Author

<hr>

```{r imp25, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Book Author'}
xml_find_all(books, './/author') %>%
  xml_text()
```

## XML - Book Title

<hr>

```{r imp26, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Book Title'}
xml_find_all(books, './/title') %>%
  xml_text()
```

## XML - Book Genre

<hr>

```{r imp27, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Book Genre'}
xml_find_all(books, './/genre') %>%
  xml_text()
```

## XML - Book Price

<hr>

```{r imp28, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Book Price'}
xml_find_all(books, './/price') %>%
  xml_double()
```

## XML - Publishing Date

<hr>

```{r imp29, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Publishing Date'}
xml_find_all(books, './/publish_date') %>%
  xml_text()
```

## XML - Description

<hr>

```{r imp30, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Description'}
xml_find_all(books, './/description') %>%
  xml_text() %>%
  stringr::str_replace_all("[\n]", "") %>%
  stringr::str_replace_all(pattern = "      ", " ") %>%
  stringr::str_replace_all(pattern = "  ", " ")
```

## XML - tibble

<hr>

```{r imp31, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'tibble'}
book <- tibble::tibble(
  author = xml_find_all(books, './/author') %>%
    xml_text(),
  title = xml_find_all(books, './/title') %>%
    xml_text(),
  genre = xml_find_all(books, './/genre') %>%
    xml_text(),
  price = xml_find_all(books, './/price') %>%
    xml_double(),
  published = xml_find_all(books, './/publish_date') %>%
    xml_text(),
  description = xml_find_all(books, './/description') %>%
    xml_text() %>%
    stringr::str_replace_all("[\r\n]", "") %>%
    stringr::str_replace_all(pattern = "      ", " ") %>%
    stringr::str_replace_all(pattern = "  ", " ")
)
```

## XML - tibble

<hr>

```{r imp32, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Book'}
book
```
