---
title: "How to work with dates in R?"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(lubridate)
library(dplyr)
library(magrittr)
knitr::opts_chunk$set(echo = FALSE)
transact <- readr::read_csv('https://raw.githubusercontent.com/rsquaredacademy/datasets/master/transact.csv')
```

## Introduction

<hr>

 In this module, we will learn to work with date/time data in R using [lubridate]( https://CRAN.R-project.org/package=lubridate), an R package that makes it easy to work with dates and time. Let us begin by installing and loading the lubridate pacakge.

## Quarter

### Introduction

<hr>

```{r lubb8, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Quarter'}
# course start date
course_start

# quarter
course_start %>%
  quarter

# quarter with year
course_start %>%
  quarter(with_year = TRUE)
```


## Practice - I

### Introduction

<hr>

```{r lub8, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Quarter'}
transact %>%
  mutate(
    Quarter = quarter(Due)
  )
```

```{r lub14, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Quarter'}
transact %>%
  mutate(
    Quarter = quarter(Due, with_year = TRUE)
  )
```

## Duration

### Introduction

<hr>

```{r lub9, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Duration'}
course_duration %>%
  as.numeric() %>%
  duration(units = 'days')
```

## Practice - II

### Introduction

<hr>

```{r lub15, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Duration'}
interval(course_start, course_end) / dseconds()

interval(course_start, course_end) / dminutes()

interval(course_start, course_end) / dhours()

interval(course_start, course_end) / dweeks()

interval(course_start, course_end) / dyears()
```

## Interval: Time Length

### Introduction

<hr>

```{r lub10, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Interval'}
interval(course_start, course_end) %>%
  time_length(unit = "seconds")

interval(course_start, course_end) %>%
  time_length(unit = "minutes")

interval(course_start, course_end) %>%
  time_length(unit = "hours")
```

## Interval: Period

### Introduction

<hr>

```{r lubb10, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Period'}
interval(course_start, course_end) %>%
  as.period(unit = "seconds")

interval(course_start, course_end) %>%
  as.period(unit = "minutes")

interval(course_start, course_end) %>%
  as.period(unit = "hours")
```

## Practice III

### Introduction

<hr>

```{r lub11, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Days'}
transact %>%
  mutate(
    inv_pay_days = inv_pay_int / ddays()
  )
```

## Practice IV

### Introduction

<hr>

```{r lub16, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Time Length'}
transact %>%
  mutate(
    inv_pay_days = time_length(inv_pay_int, unit = "days")
  )
```

## Practice - V

### Introduction

<hr>

```{r lub17, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Period'}
transact %>%
  mutate(
    inv_pay_days = as.period(inv_pay_int)
  )
```
