---
title: "Legend - Part 3"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(ggplot2)
library(dplyr)
library(tidyr)
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction

If the aesthetics are mapped to variables, ggplot2 automatically creates legends wherever applicable. 
You may want to modify the appearance of legends. In this module, we will learn to modify the legends when
`shape` is mapped to categorical variables. If you have mapped shape/size to a discrete variable which has 
less than six categories, you can use `scale_shape()`


### Agenda

<hr>

Modify legend when `shape` is mapped to variables. Specifically

- title
- breaks
- limits
- range
- labels
- values
- symbol type


## Plot

### Introduction

<hr>

### Example

<hr>

```{r leg50eg, echo=TRUE, collapse=FALSE, fig.align='center'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, shape = factor(cyl))) +
  scale_shape()
```

### Instructions

<hr>

```{r leg50, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Shape'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, shape = factor(cyl))) +
  scale_shape()
```

```{r leg50-solution}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, shape = factor(cyl))) +
  scale_shape()
```

## Values

### Introduction

<hr>

### Example

<hr>

```{r leg31eg, echo=TRUE, collapse=FALSE, fig.align='center'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, shape = factor(cyl))) +
  scale_shape_manual(values = c(4, 12, 24))
```

### Instructions

<hr>

```{r leg31, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Legend Values'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, shape = factor(cyl))) +
  scale_shape_manual(values = c(4, 12, 24))
```

```{r leg31-solution}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, shape = factor(cyl))) +
  scale_shape_manual(values = c(4, 12, 24))
```

## Title

### Introduction

<hr>

### Example

<hr>

```{r leg30eg, echo=TRUE, collapse=FALSE, fig.align='center'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, shape = factor(cyl))) +
  scale_shape_manual(name = "Cylinders",values = c(4, 12, 24))
```

### Instructions

<hr>

```{r leg30, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Legend Title'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, shape = factor(cyl))) +
  scale_shape_manual(name = "Cylinders", values = c(4, 12, 24))
```

```{r leg30-solution}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, shape = factor(cyl))) +
  scale_shape_manual(name = "Cylinders", values = c(4, 12, 24))
```

## Labels

### Introduction

<hr>

### Example

<hr>

```{r leg32eg, echo=TRUE, collapse=FALSE, fig.align='center'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, shape = factor(cyl))) +
  scale_shape_manual(values = c(4, 12, 24), labels = c('Four', 'Six', 'Eight'))
```

### Instructions

<hr>

```{r leg32, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Legend Labels'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, shape = factor(cyl))) +
  scale_shape_manual(values = c(4, 12, 24), labels = c('Four', 'Six', 'Eight'))
```

```{r leg32-solution}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, shape = factor(cyl))) +
  scale_shape_manual(values = c(4, 12, 24), labels = c('Four', 'Six', 'Eight'))
```

## Limits

### Introduction

<hr>

### Example

<hr>

```{r leg33eg, echo=TRUE, collapse=FALSE, fig.align='center'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, shape = factor(cyl))) +
  scale_shape_manual(values = c(4, 12, 24), limits = c(4, 6, 8))
```

### Instructions

<hr>

```{r leg33, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Legend Limits'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, shape = factor(cyl))) +
  scale_shape_manual(values = c(4, 12, 24), limits = c(4, 6, 8))
```

```{r leg33-solution}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, shape = factor(cyl))) +
  scale_shape_manual(values = c(4, 12, 24), limits = c(4, 6, 8))
```

## Breaks

### Introduction

<hr>

### Example

<hr>

```{r leg34eg, echo=TRUE, collapse=FALSE, fig.align='center'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, shape = factor(cyl))) +
  scale_shape_manual(values = c(4, 12, 24), breaks = c(4, 6, 8))
```

### Instructions

<hr>

```{r leg34, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Legend Breaks'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, shape = factor(cyl))) +
  scale_shape_manual(values = c(4, 12, 24), breaks = c(4, 6, 8))
```

```{r leg34-solution}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, shape = factor(cyl))) +
  scale_shape_manual(values = c(4, 12, 24), breaks = c(4, 6, 8))
```

## Symbol

### Introduction

<hr>

### Example

<hr>

```{r leg55eg, echo=TRUE, collapse=FALSE, fig.align='center'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, shape = factor(cyl))) +
  scale_shape(solid = FALSE)
```

### Instructions

<hr>

```{r leg55, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Legend Types'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, shape = factor(cyl))) +
  scale_shape(solid = FALSE)
```

```{r leg55-solution}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, shape = factor(cyl))) +
  scale_shape(solid = FALSE)
```

## Summary



