---
title: "Legend - Part 3"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(ggplot2)
library(dplyr)
library(tidyr)
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction

If the aesthetics are mapped to variables, ggplot2 automatically creates legends wherever applicable. 
You may want to modify the appearance of legends. In this module, we will learn to modify the legends when
`shape` is mapped to categorical variables. If you have mapped shape/size to a discrete variable which has 
less than six categories, you can use `scale_shape()`


### Agenda

<hr>

Modify legend when `shape` is mapped to variables. Specifically

- title
- breaks
- limits
- range
- labels
- values
- symbol type


## Plot

### Introduction

<hr>

```{r leg29, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Shape'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, shape = factor(cyl)))
```

```{r leg50, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Shape'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, shape = factor(cyl))) +
  scale_shape()
```

## Title

<hr>

```{r leg30, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Legend Title'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, shape = factor(cyl))) +
  scale_shape_manual(name = "Cylinders",values = c(4, 12, 24))
```

<hr>

```{r leg51, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Legend Title'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, shape = factor(cyl))) +
  scale_shape(name = 'Cylinders')
```


## Values

<hr>

```{r leg31, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Legend Values'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, shape = factor(cyl))) +
  scale_shape_manual(values = c(4, 12, 24))
```

## Labels

<hr>

```{r leg32, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Legend Labels'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, shape = factor(cyl))) +
  scale_shape_manual(values = c(4, 12, 24), labels = c('Four', 'Six', 'Eight'))
```

<hr>

```{r leg52, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Legend Labels'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, shape = factor(cyl))) +
  scale_shape(labels = c('Four', 'Six', 'Eight'))
```

## Limits

<hr>

```{r leg33, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Legend Limits'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, shape = factor(cyl))) +
  scale_shape_manual(values = c(4, 12, 24), limits = c(4, 6, 8))
```

<hr>

```{r leg53, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Legend Limits'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, shape = factor(cyl))) +
  scale_shape(limits = c(4, 6, 8))
```

## Breaks

<hr>

```{r leg34, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Legend Breaks'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, shape = factor(cyl))) +
  scale_shape_manual(values = c(4, 12, 24), breaks = c(4, 6, 8))
```

<hr>

```{r leg54, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Legend Breaks'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, shape = factor(cyl))) +
  scale_shape(breaks = c(4, 6, 8))
```

## Symbol

<hr>

```{r leg55, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Legend Types'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, shape = factor(cyl))) +
  scale_shape(solid = FALSE)
```


## Summary

<hr>

```{r leg35, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Shape Discrete'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, shape = factor(cyl))) +
  scale_shape_manual(name = "Cylinders", labels = c('Four', 'Six', 'Eight'),  
     values = c(4, 12, 24), limits = c(4, 6, 8), breaks = c(4, 6, 8))
```

<hr>

```{r leg56, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Shape'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, shape = factor(cyl))) +
  scale_shape(solid = FALSE, name = 'Cylinders', limits = c(4, 6, 8),
    labels = c('Four', 'Six', 'Eight'), breaks = c(4, 6, 8))
```


