---
title: "forcats: Working with Categorical Data"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(forcats)
library(tibble)
library(magrittr)
library(purrr)
library(dplyr)
library(ggplot2)
knitr::opts_chunk$set(echo = FALSE)
ecom <- readr::read_csv('https://raw.githubusercontent.com/rsquaredacademy/datasets/master/web.csv')
traffic <- readr::read_csv('https://raw.githubusercontent.com/rsquaredacademy/datasets/master/web_traffic.csv')
```

## Introduction

<hr>

In this module, we will learn to work with categorical/qualitative data in R using [forcats](http://forcats.tidyverse.org). Let us begin by installing and loading forcats and a set of other pacakges we will be using.

## Case Study 

### Introduction

<hr>

## Data 

### Introduction

<hr>

```{r import2, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Data'}
traffic
```

## Collapse Categories

### Collapse Referrer Categories

<hr>

```{r cat7, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Collapse Referrer Categories'}
traffic2 <- fct_collapse(traffic$traffics,
  social = c("facebook", "twitter", "instagram"),
  search = c("google", "bing", "yahoo")
)

traffic2 %>% fct_count() 
```

## Lump Categories - Introduction

### Lump Infrequent Referrer Types

<hr>

```{r cat8, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Lump Infrequent Referrer Types'}
traffic$traffics %>% fct_count()

traffic$traffics %>% fct_lump() %>% table()
```

## Lump Categories - Part 1

### Introduction

<hr>

```{r cat9, echo=FALSE, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Referrers'}
traffic$traffics %>% fct_count() %>% arrange(desc(n))
```

```{r cat17, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Retain Top 3 Referrers'}
traffic$traffics %>% fct_lump(n = 3) %>% table()
```

## Lump Categories - Part 2

### Lump Referrer Types with less than 10% traffic

<hr>

```{r cat12, echo=FALSE, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Referrer Percentages'}
traffic$traffics %>% 
  fct_count() %>%
  mutate(
    percent = round((n / sum(n)) * 100, 2)
  )
```

```{r cat16, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Lump Referrer Types'}
traffic$traffics %>% fct_lump(prop = 0.1) %>% table()
```

## Lump Categories - Part 3

### Lump Referrer Types with less than 15% traffic

<hr>

```{r cat13, echo=FALSE, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Referrer Percentage'}
traffic$traffics %>% 
  fct_count() %>%
  mutate(
    percent = round((n / sum(n)) * 100, 2)
  )
```

```{r cat18, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Lump Referrer Types'}
traffic$traffics %>% fct_lump(prop = 0.15) %>% table()
```

## Lump Categories - Part 4

### Retain 3 Referrer Types with lowest traffic

<hr>

```{r cat14, echo=FALSE, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Traffic Sources'}
traffic$traffics %>% fct_count() %>% arrange(n)
```

```{r cat19, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Retain Top 3 Referrers'}
traffic$traffics %>% fct_lump(n = -3) %>% table()
```

## Lump Categories - Part 5

### Retain 3 Referrer Types with less than 10% traffic

<hr>

```{r cat15, echo=FALSE, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Referrer Percentage'}
traffic$traffics %>% 
  fct_count() %>%
  mutate(
    percent = round((n / sum(n)) * 100, 2)
  )
```

```{r cat20, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Retain Top 3 Referrers'}
traffic$traffics %>% fct_lump(prop = -0.1) %>% table()
```

