---
title: "forcats: Working with Categorical Data"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(forcats)
library(tibble)
library(magrittr)
library(purrr)
library(dplyr)
library(ggplot2)
knitr::opts_chunk$set(echo = FALSE)
ecom <- readr::read_csv('https://raw.githubusercontent.com/rsquaredacademy/datasets/master/web.csv')
traffic <- readr::read_csv('https://raw.githubusercontent.com/rsquaredacademy/datasets/master/web_traffic.csv')
```

## Introduction

<hr>

In this module, we will learn to work with categorical/qualitative data in R using [forcats](http://forcats.tidyverse.org). Let us begin by installing and loading forcats and a set of other pacakges we will be using.

## Case Study

### Introduction

<hr>

We will use a case study to explore the various features of the forcats package. You can download the data for the case study from [here](https://raw.githubusercontent.com/rsquaredacademy/datasets/master/web.csv) or directly import the data using the readr package. We will do the following in this case study:

- compute the frequency of different referrers
- plot average number of pages browsed for different referrers
- collapse referrers with low sample size into a single group
- club traffic from social media websites into a new category
- group referrers with traffic below a threshold into a single category


## Data

### Introduction

<hr>

```{r show, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Data'}
hsb <- readr::read_csv('/www/hsb2.csv')
hsb
```

### Data Dictionary

<hr>

- id: row id
- referrer: referrer website/search engine
- os: operating system
- browser: browser
- device: device used to visit the website
- n_pages: number of pages visited
- duration: time spent on the website (in seconds)
- repeat: frequency of visits
- country: country of origin
- purchase: whether visitor purchased
- order_value: order value of visitor (in dollars)

 
## Tabulate Referrers - Part 1

### Introduction

<hr>

```{r cat2, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Tabulate Referrers'}
# using dplyr
ecom %>%
  count(referrer)

# using forcats
ecom %>%
  use_series(referrer) %>%
  fct_count()
```

## Reorder Referrers - Part 1

### Visualize 

<hr>

```{r cat10, fig.align='center', fig.width=6, fig.height=4, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Avg. Page Visits by Referrer Type'}
ggplot(refer_summary, aes(page, referrer)) + geom_point()
```

## Reorder Referrers - Part 2

<hr>

```{r cat11, fig.align='center', fig.width=6, fig.height=4, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Reorder Referrers'}
ggplot(refer_summary, aes(page, fct_reorder(referrer, page))) + geom_point()
```

## Referrer Frequency - Part 1

### Plot Referrer Frequency (Descending Order)

<hr>

```{r cat4, fig.align='center', fig.width=6, fig.height=4, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Referrer Frequency'}
ecom %>%
  mutate(ref = referrer %>% fct_infreq()) %>%
  ggplot(aes(ref)) +
  geom_bar()
```

## Referrer Frequency - Part 2

### Plot Referrer Frequency (Ascending Order)

<hr>

```{r cat5, fig.align='center', fig.width=6, fig.height=4, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Referrer Frequency'}
ecom %>%
  mutate(ref = referrer %>% fct_infreq() %>% fct_rev()) %>%
  ggplot(aes(ref)) +
  geom_bar()
```

