---
title: "qplot"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(ggplot2)
knitr::opts_chunk$set(echo = FALSE)
```

## Agenda

<hr>

Learn to quickly build a set of plots that are routinely used to explore data:

- Scatter Plot
- Bar Plot
- Box Plot
- Line Chart
- Histogram

## Introduction

<hr>

Shortcut designed for those familiar with base plots. You can quickly produce a number of different
types of plots. Below are the key arguments:

- `x`    : data for X axis
- `y`    : data for Y axis
- `data` : a data frame or a tibble
- `geom` : symbols to represent data
- `fill` : color for filled symbols
- `color`: color for other symbols
- `shape`: shape of the geom
- `size` : size of the symbol

## Scatter Plot

### Introduction

<hr>

### Instructions

<hr>

- map `x` to `disp`
- map `y` to `mpg`
- map `data` to `mtcars`

```{r gg2, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Scatter Plot'}
# scatter plot using qplot
qplot(x = ___, y = ___, data = ___)
```

### Point & Line

<hr>

### Instructions

<hr>

- map `geom` to `point` and `line`

```{r gg3, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Point & Line'}
qplot(disp, mpg, data = mtcars, geom = c('____', '____'))
```

### Color

<hr>

### Instructions

<hr>

- map `color` to `cyl`

```{r gg4, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Point Color'}
qplot(disp, mpg, data = mtcars, color = ____)
```


## Bar Plot

### Introduction

<hr>

### Instructions

<hr>

- map `x` to `cyl`
- map `geom` to `bar`

```{r gg7, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Bar Plot'}
qplot(x = ____, data = mtcars, geom = c('____'))
```

### Color

<hr>

### Instructions

<hr>

- map `x` to `cyl`
- map `fill` to `am`

```{r gg8, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Color'}
qplot(x = ____, data = mtcars, geom = c('bar'), fill = ____)
```

## Box Plot

### Introduction

<hr>

### Instructions

<hr>

- map `x` to `gear`
- map `y` to `mpg`
- map `geom` to `boxplot`


```{r gg9, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Box Plot'}
qplot(x = ____, y = ____, data = mtcars, geom = c('______'))
```


## Line Chart

### Introduction

<hr>

### Instructions

<hr>

- map `x` to `date`
- map `y` to `umemploy`
- map `geom` to `line`

```{r gg12, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Line Chart'}
qplot(x = ____, y = ____, data = economics, geom = c('____'))
```

## Histogram

### Introduction

<hr>

### Instructions

<hr>

- map `x` to `mpg`
- set `bins` to 5

```{r gg14, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Histogram'}
qplot(x = ____, data = mtcars, bins = ____)
```

