---
title: "ggplot2: Quick Tour"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(ggplot2)
knitr::opts_chunk$set(echo = FALSE)
```

## Agenda

<hr>

Learn to quickly build a set of plots that are routinely used to explore data:

- Scatter Plot
- Bar Plot
- Box Plot
- Line Chart
- Histogram

## qplot

<hr>

Shortcut designed for those familiar with base plots. You can quickly produce a number of different
types of plots. Below are the key arguments:

- `x`    : data for X axis
- `y`    : data for Y axis
- `geom` : symbols to represent data
- `data` : a data frame or a tibble

## Scatter Plot

### Introduction

<hr>

```{r gg2, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Scatter Plot'}
qplot(disp, mpg, data = mtcars)
```

### Point & Line

<hr>

```{r gg3, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Point & Line'}
qplot(disp, mpg, data = mtcars, geom = c('point', 'line'))
```

### Color

<hr>

```{r gg4, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Point Color'}
qplot(disp, mpg, data = mtcars, color = factor(cyl))
```

### Shape

<hr>

```{r gg5, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Point Shape'}
qplot(disp, mpg, data = mtcars, shape = factor(cyl))
```

### Size

<hr>

```{r gg6, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Point Size'}
qplot(disp, mpg, data = mtcars, size = qsec)
```

## Bar Plot

### Introduction

<hr>

```{r gg7, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Bar Plot'}
qplot(factor(cyl), data = mtcars, geom = c('bar'))
```

### Color

<hr>

```{r gg8, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Color'}
qplot(factor(cyl), data = mtcars, geom = c('bar'), fill = factor(am))
```

## Box Plot

### Introduction

<hr>

```{r gg9, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Box Plot'}
qplot(factor(cyl), mpg, data = mtcars, geom = c('boxplot'))
```

### Univariate Box Plot

<hr>

```{r gg10, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Univariate Box Plot'}
qplot(factor(1), mpg, data = mtcars, geom = c('boxplot'))
```

### Jitter

<hr>

```{r gg11, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Jitter'}
qplot(factor(cyl), mpg, data = mtcars, geom = c('boxplot', 'jitter'))
```

## Line Chart

### Introduction

<hr>

```{r gg12, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Line Chart'}
qplot(x = date, y = unemploy, data = economics, geom = c('line'))
```

### Color

<hr>

```{r gg13, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Color'}
qplot(x = date, y = unemploy, data = economics, geom = c('line'),
      color = 'red')
```

## Histogram

### Introduction

<hr>

```{r gg14, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Histogram'}
qplot(mpg, data = mtcars, bins = 5)
```

