---
title: "Themes - Part 4"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(ggplot2)
library(dplyr)
library(tidyr)
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction

### Agenda

<hr>

Use `theme()` to modify the appearance of 

- plot background
- plot title
- plot margin
- facet strip background
- facet strip text

## Plot

<hr>

```{r theme13, echo=TRUE, collapse=FALSE, fig.align='center'}
p <- ggplot(mtcars) +
  geom_point(aes(disp, mpg)) + 
  ggtitle('Theme Modification')
p
```

## Background

### Introduction

<hr>

### Example

<hr>

```{r theme14eg, echo=TRUE, collapse=FALSE, fig.align='center'}
p + theme(plot.background = element_rect(color = 'blue', 
          fill = '#4682B4'))
```

### Instructions

<hr>

```{r theme14, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Plot Background'}
p + theme(plot.background = element_rect(color = 'blue', 
          fill = '#4682B4'))
```

```{r theme14-solution}
p + theme(plot.background = element_rect(color = 'blue', 
          fill = '#4682B4'))
```

## Title

### Introduction

<hr>

### Example

<hr>

```{r theme27eg, echo=TRUE, collapse=FALSE, fig.align='center'}
p + theme(plot.title = element_text(color = 'red'))
```

### Instructions

<hr>

```{r theme27, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Plot Title'}
p + theme(plot.title = element_text(color = 'red'))
```

```{r theme27-solution}
p + theme(plot.title = element_text(color = 'red'))
```

## Margin

### Introduction

<hr>

### Example

<hr>

```{r theme28eg, echo=TRUE, collapse=FALSE, fig.align='center'}
p + theme(plot.margin = unit(c(1, 1, 1, 1), "cm"))
```

### Instructions

<hr>

```{r theme28, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Plot Margin'}
p + theme(plot.margin = unit(c(1, 1, 1, 1), "cm"))
```

```{r theme28-solution}
p + theme(plot.margin = unit(c(1, 1, 1, 1), "cm"))
```

## Facets

### Introduction

<hr>

### Example

<hr>

```{r theme15eg, echo=TRUE, collapse=FALSE, fig.align='center'}
p <- ggplot(mtcars) +
  geom_point(aes(disp, mpg)) + 
  facet_grid(~cyl)
p
```

### Instructions

<hr>

```{r theme15, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Facets'}
p <- ggplot(mtcars) +
  geom_point(aes(disp, mpg)) + 
  facet_grid(~cyl)
p
```

```{r theme15-solution}
p <- ggplot(mtcars) +
  geom_point(aes(disp, mpg)) + 
  facet_grid(~cyl)
p
```

## Strip Background

### Introduction

<hr>

### Example

<hr>

```{r theme16eg, echo=TRUE, collapse=FALSE, fig.align='center'}
p + theme(strip.background = element_rect(color = 'red', 
          fill = '#4682B4'))
```

### Instructions

<hr>

```{r theme16, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Strip Background'}
p + theme(strip.background = element_rect(color = 'red', 
          fill = '#4682B4'))
```

```{r theme16-solution}
p + theme(strip.background = element_rect(color = 'red', 
          fill = '#4682B4'))
```

## Strip Text

### Introduction

<hr>

### Example

<hr>

```{r theme29eg, echo=TRUE, collapse=FALSE, fig.align='center'}
p + theme(strip.text = element_text(face = 'italic', size = 8,
          color = 'red'))
```

### Instructions

<hr>

```{r theme29, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Strip Text'}
p + theme(strip.text = element_text(face = 'italic', size = 8,
          color = 'red'))
```

```{r theme29-solution}
p + theme(strip.text = element_text(face = 'italic', size = 8,
          color = 'red'))
```
