---
title: "Import Data in R - Part 3"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(haven)
library(foreign)
library(sas7bdat)
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction

<hr>

Importing data is the first step in any data analysis workflow. If you cannot import data from differernt sources or file formats, you cannot proceed with data analysis. R allows you to import data from several sources and a variety of file formats. In this module, we will focus on 

- SAS
- SPSS
- STATA

## haven

<hr>

- `read_dta()`
- `read_stata()`
- `read_sav()`
- `read_spss()`
- `read_sas()`


## Other Libraries

<hr>

- SAS: sas7bdat (last updated in 2014; version 0.5)
- STATA, SPSS: foreign (maintained; version 0.8)

## STATA

<hr>

```{r import67, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Introduction'}
haven::read_dta('airline.dta')    
```

## STATA

<hr>

```{r import69, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Introduction'}
foreign::read.dta('airline.dta')  
```

## SPSS

<hr>

```{r import70, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Introduction'}
read_sav('employee.sav')   
```

## SPSS

<hr>

```{r import72, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Introduction'}
foreign::read.spss('employee.sav', use.value.labels = FALSE,
                   to.data.frame = TRUE)
```


## SAS

<hr>

```{r import73, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Introduction'}
read_sas('airline.sas7bdat')
```

## SAS

<hr>

```{r import74, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Introduction'}
sas7bdat::read.sas7bdat('airline.sas7bdat')
```
