---
title: "Readable Code with Pipes"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(dplyr)
library(magrittr)
knitr::opts_chunk$set(echo = FALSE)
ecom <- readr::read_csv('https://raw.githubusercontent.com/rsquaredacademy/datasets/master/web.csv')
```

## Introduction

<hr>

When you are dealing with a sequence of multiple operations, R code can get a bit cramped and not so easy on the eyes. The [magrittr](https://CRAN.R-project.org/package=magrittr) package by Stefan Milton Bache provides pipes enabling us to write R code that is readable.

- especially useful when you have nested functions
- similar in spirit to javascript's method chaining
- functions taking multiple arguments can be confusing and messy to read
- with magrittr, you program from left to right


## Get Started

### Introduction

<hr>


### Instructions

<hr>

- use `%>%` and `tail()` to get the last 10 rows of `mtcars`

```{r mag1, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'View Data'}
head(ecom, 10)

# using pipe
ecom %>% head(10)

# tail

```

```{r mag1-solution}
mtcars %>% tail(10)
```

## Square Root 

### Introduction

<hr>

```{r mag3, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Square Root'}
y <- ecom$n_pages
y <- sqrt(y)
y
```

## Square Root - Using Pipe 1

<hr>

Now let us learn how to compute square root using pipe operators. In the above example, we have done two things:

- assign `n_pages` to `y` using `$`
- compuate square root of `y` and assign the result to `y` itself

We can assign expose a column from a data set using the `%$%` operator. For example, `y <- mtcars %$% mpg` will assign `mpg` to `y`.
Similarly, we can assign the result of an operation performed on a variable to itself using `%<>%` operator. Let us assume you want to  assign the absolute value of a variable to itself. This is how you would do it normally:

`y <- abs(y)`

Using `%<>%` operator, this is how you will achieve it:

`y %<>% abs()`

### Instructions

<hr>

- use `%$%` to assing `n_pages` from `ecom` to `y`
- use `%<>%` to compute square root of `y` and assign it to `y`

```{r mag4, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Square Root'}
# select n_pages variable and assign it to y
y <- ecom 

# compute square root of y and assign it to y 
y 
```

```{r mag4-solution}
# select n_pages variable and assign it to y
y <- ecom %$% n_pages

# compute square root of y and assign it to y 
y %<>% sqrt()
```


## Square Root - Using Pipe 2

<hr>

In the first example, we computed the square root of `y` in two steps while we could have achieved it in a single step like this:

`y <- sqrt(econ$n_pages)`

What we are doing above is:

- select `n_pages` from `econ`
- pass it on to `sqrt()`
- assign the result to `y`

### Instructions

<hr>

Let us try to do this using pipes:

- expose `n_pages` from `econ` using `%$%`
- pass it on to `sqrt()` using `%>%`
- assign the result to `y`

We have written the first part for you.

```{r mag5, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Square Root'}
y <- ecom %$% 
  n_pages
```

```{r mag5-solution}
y <- ecom %$% 
  n_pages %>% 
  sqrt()
```

## Correlation

### Introduction

<hr>

From the ecommerce data, we want to explore the relationship between number of visits and time spent on the site for those who
purchase/convert. We can achieve this in the following steps:

- filter data for those who have purchased/converted
- compute correlation by selecting `n_visit` and `duration`

```{r mag32, eval=FALSE, echo=TRUE}
ecom1 <- subset(ecom, purchase == 'true')
cor(ecom1$n_visit, ecom1$duration)
```

## Correlation - Using pipe

We can chain functions using pipe operators. For example, using `mtcars`, to compute the average miles per gallon for cars with eight cylinders we will write:

```{r mag33, eval=FALSE, echo=TRUE}
mtcars %>% 
  subset(cyl == 8) %$% 
  mean(mpg)
```

This is how you can read the above code:

- filter data from `mtcars` where `cyl == 8` using `subset()`
- from the filtered data set expose `mpg` using `%$%` and pass it into `mean()`

### Instructions

Let us use pipe operators to compute the correlation between `n_visit` and `duration`:

- filter data for those who have purchased (`purchase == 'true'`) using `subset()` and `%>%`
- expose `n_visit` and `duration` using `%$%` and pass them onto `cor()`


```{r mag6, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Correlation'}
# with pipe
ecom %>%
  subset(purchase == 'true') 
```

```{r mag6-solution}
# with pipe
ecom %>%
  subset(purchase == 'true') %$% 
  cor(n_visit, duration)
```

