---
title: "Line Chart"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)
data <- head(AirPassengers)
data1 <- c(7.2, 7.6, 6.8, 6.5, 7)
data2 <- c(6.8, 7.2, 7.8, 7, 6.2)
```

## Introduction

### Agenda

<hr>

- create line plots
- add color to lines
- modify line type/style
- modify line width
- add points to the lines
- modify axis range
- add additional lines to the plot

## Data

### Introduction

<hr>

```{r airpas, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Data'}
head(AirPassengers)
```

## Line Chart

### Introduction

<hr>

```{r line1, fig.align='center', fig.height=5, fig.width=5, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Line Chart'}
data <- head(AirPassengers)
plot(data, type = 'l')
```

### Lines & Points

<hr>

```{r line2, fig.align='center', fig.height=5, fig.width=5, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Lines & Points'}
plot(data, type = 'b')
```

### Overplotted

<hr>

```{r line3, fig.align='center', fig.height=5, fig.width=5, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Overplotted'}
plot(data, type = 'o')
```

### Lines with Breaks

<hr>

```{r line4, fig.align='center', fig.height=5, fig.width=5, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Lines With Breaks'}
plot(data, type = 'c')
```

## Line Color

### Introduction

<hr>

```{r line5, fig.align='center', fig.height=5, fig.width=5, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Line Color'}
plot(data, type = 'l', col = 'blue')
```

### Color

<hr>

```{r line6, fig.align='center', fig.height=5, fig.width=5, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Line Color'}
plot(data, type = 'b', col = 'blue')
```

## Line Types

### Introduction

<hr>

- 1: solid
- 2: dashed
- 3: dotted
- 4: dotdash
- 5: longdash
- 6: twodash


### Line Types

<hr>

```{r line9, fig.align='center', fig.height=5, fig.width=5, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Line Types'}
plot(data, type = 'l', lty = 3)
```

### Line Types

<hr>

```{r lin7, echo=FALSE, fig.align='center', fig.height=7, fig.width=10, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Line Types'}
init <- par(no.readonly = TRUE)
par(mfrow = c(3, 2))
values <- 1:6
for (i in values) {
    plot(data, type = "l", lty = i, col ="red")
    mtext(paste("lty = ", i), side = 3, col = "blue", line = 1)
}
```

### Line Types

<hr>

```{r lin8, echo=FALSE, fig.align='center', fig.height=7, fig.width=10, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Line Types'}
init <- par(no.readonly = TRUE)
par(mfrow = c(3, 2))
values <- c("solid", "dashed", "dotted", "dotdash", "longdash", "twodash")
for (i in values) {
    plot(data, type = "l", lty = i, col ="red")
    mtext(paste("lty = ", i), side = 3, col = "blue", line = 1)
}
```

## Line Width

### Introduction

<hr>

```{r line10, fig.align='center', fig.height=5, fig.width=5, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Line Width'}
plot(data, type = 'l', lwd = 2.5)
```

### Line Width

<hr>

```{r lin11, echo=FALSE, fig.align='center', fig.height=7, fig.width=10, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Line Width'}
init <- par(no.readonly = TRUE)
par(mfrow = c(2, 2))
values <- c(0.5, 1, 1.5, 2)
for (i in values) {
    plot(data, type = "l", lwd = i, col ="red")
    mtext(paste("lwd = ", i), side = 3, col = "blue", line = 1)
}
```

## Points

### Enhance Points

<hr>

```{r line12, fig.align='center', fig.height=5, fig.width=5, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Points'}
plot(data, type = 'b', pch = 23, col = 'red', cex = 1.5)
```

### Add Points

<hr>

```{r line13, fig.align='center', fig.height=5, fig.width=5, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Add Points'}
plot(data, type = 'l', col = 'red')
points(data, pch = 23, col = 'blue', bg = 'green', cex = 1.5)
```

## Additional Lines

### Introduction

<hr>

```{r line14, fig.align='center', fig.height=5, fig.width=5, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Additional Lines'}
data1 <- c(7.2, 7.6, 6.8, 6.5, 7)
data2 <- c(6.8, 7.2, 7.8, 7, 6.2)
plot(data1, type = "b", col = "blue")
lines(data2, type = "b", col = "red")
```

### Modify Axis Range

<hr>

```{r line15, fig.align='center', fig.height=5, fig.width=5, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Modify Axis Ranges'}
plot(data1, type = "b", col = "blue", ylim = c(5, 9))
lines(data2, type = "b", col = "red")
```

### Line Plot

<hr>

```{r line16, fig.align='center', fig.height=5, fig.width=5, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Line Chart'}
plot(data1, type = "b", col = "blue", 
     ylim = c(5, 9), main = 'Line Graph',
     xlab = 'Index', ylab = 'Data')
lines(data2, type = "b", col = "red")
```
