---
title: "Hacking strings with stringr"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(stringr)
library(tibble)
library(magrittr)
library(purrr)
library(dplyr)
knitr::opts_chunk$set(echo = FALSE)
mockstring <- readr::read_csv("https://raw.githubusercontent.com/rsquaredacademy/datasets/master/mock_strings.csv")
```

## Introduction

<hr>

In this module, we will learn to work with string data in R using [stringr](http://stringr.tidyverse.org). As we did in the earlier modules, we will use a case study to explore the various features of the stringr package. You can
download the data for the case study from [here](https://raw.githubusercontent.com/rsquaredacademy/datasets/master/mock_strings.csv) or directly import the data using the readr package.  Let us begin by installing and loading stringr and a set of other pacakges we will be using.

## Subset Strings

## Locate Patterns

## Extract Image Type - Introduction

### Introduction

<hr>

### Instructions

<hr>

## Extract Image Type - Step 1

### Image URL

<hr>

### Instructions

<hr>


```{r str_case3_1, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Image Type'}
img <- mockstring %>%
  pull(imageurl) %>%
  head
img
```

## Extract Image Type - Step 2

### Introduction

<hr>

### Instructions

<hr>

```{r str_case3_2, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Image Type'}
img %>%
  str_split(pattern = '\\.')
```

## Extract Image Type - Step 3

### Introduction

<hr>

### Instructions

<hr>

```{r str_case3_3, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Image Type'}
img %>%
  str_split(pattern = '\\.') %>%
  map_chr(extract(3))
```

## Extract Image Type - Step 4

### Introduction

<hr>

### Instructions

<hr>

```{r str_case3_4, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Image Type'}
img %>%
  str_split(pattern = '\\.') %>%
  map_chr(extract(3)) %>%
  str_sub(start = 1, end = 3)
```

## Extract Image Type - Step 5

### Introduction

<hr>

### Instructions

<hr>

```{r str_case3_5, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Image Type'}
img %>%
  str_split(pattern = '\\.') %>%
  map_chr(extract(3)) %>%
  str_split(pattern = '/') %>%
  map_chr(extract(1))
```



