---
title: "Legend - Part 5"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(ggplot2)
library(dplyr)
library(tidyr)
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction

If the aesthetics are mapped to variables, ggplot2 automatically creates legends wherever applicable. 
You may want to modify the appearance of legends. In this module, we will learn to modify the legends when
`alpha` is mapped to categorical variables.

### Agenda

<hr>

Modify legend when `alpha` is mapped to variables. Specifically

- title
- breaks
- limits
- range
- labels
- values
- symbol type


## Plot

### Introduction

<hr>

```{r leg2, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Map Color'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, alpha = hp), color = 'blue')
```

## Title

<hr>

```{r leg3, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Legend Title'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, alpha = hp), color = 'blue') +
  scale_alpha_continuous("Horsepower")
```

## Breaks

<hr>

```{r leg4, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Legend Breaks'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, alpha = hp), color = 'blue') +
  scale_alpha_continuous(breaks = c(0, 100, 200, 300, 400))
```

## Limits

<hr>

```{r leg5, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Legend Limits'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, alpha = hp), color = 'blue') +
  scale_alpha_continuous(limits = c(0, 400))
```

## Range

<hr>

```{r leg6, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Legend Range'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, alpha = hp), color = 'blue') +
  scale_alpha_continuous(range = c(0.4, 0.8))
```

## Labels

<hr>

```{r leg7, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Legend Labels'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, alpha = hp), color = 'blue') +
  scale_alpha_continuous(breaks = c(0, 100, 200, 300, 400),
    labels = c("Zero", "Hundred", "2 Hundred", 
      "3 Hundred", "4 Hundred"))
```

## Summary

<hr>

```{r leg8, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Alpha Continuous'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, alpha = hp), color = 'blue') +
  scale_alpha_continuous("Horsepower", breaks = c(0, 100, 200, 300, 400),
    limits = c(0, 400), range = c(0.4, 0.8),
    labels = c("Zero", "Hundred", "2 Hundred", 
      "3 Hundred", "4 Hundred"))
```

## Alpha - Discrete

### Introduction

<hr>

```{r leg9, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Alpha Discrete'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, alpha = factor(cyl)), color = 'blue')
```

### Legend Title

<hr>

```{r leg10, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Legend Title'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, alpha = factor(cyl)), color = 'blue') +
  scale_alpha_discrete(name = "Cylinders")
```

### Legend Breaks

<hr>

```{r leg11, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Legend Breaks'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, alpha = factor(cyl)), color = 'blue') +
  scale_alpha_discrete(breaks = c("4", "6", "8"))
```

### Legend Range

<hr>

```{r leg12, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Legend Range'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, alpha = factor(cyl)), color = 'blue') +
  scale_alpha_discrete(range = c(0.4, 0.8))
```

### Legend Labels

<hr>

```{r leg13, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Legend Labels'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, alpha = factor(cyl)), color = 'blue') +
  scale_alpha_discrete(labels = c("Four", "Six", "Eight"))
```

### Summary

<hr>

```{r leg14, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Alpha'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, alpha = factor(cyl)), color = 'blue') +
  scale_alpha_discrete(name = "Cylinders", range = c(0.4, 0.8),
    breaks = c("4", "6", "8"), labels = c("Four", "Six", "Eight"))
```

