---
title: "Import Data in R - Part 1"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(readr)
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction

### Introduction

<hr>

Importing data is the first step in any data analysis workflow. If you cannot import data from differernt sources or file formats, you cannot proceed with data analysis. R allows you to import data from several sources and a variety of file formats. In this module, we will focus on 

  - csv
  - tsv
  - txt

## CSV 

### Introduction

<hr>

- `read_csv()`
- `read_delim()`
- `read.csv()`

### Options

<hr>

- `col_names`
- `skip`
- `n_max`
- `col_types`

## readr

### Introduction

<hr>

```{r import2, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Introduction'}
read_csv('C:/hsb2.csv')
```

### Delimiter 

<hr>

```{r import3, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Delimiter'}
read_delim('C:/hsb2.csv', delim = ',')
```

## Column Names 

### Introduction

<hr>

```{r import4, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Column Names'}
read_csv('C:/hsb2.csv', col_names = FALSE)
```

## Skip Lines 

### Introduction

<hr>

```{r import6, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Skip Lines'}
read_csv('C:/hsb2.csv', skip = 5)
```

## Maximum Lines 

<hr>

```{r import8, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Maximum Lines'}
read_csv('C:/hsb2.csv', n_max = 50)
```

## Column Types

<hr>

```{r import55, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Column Types'}
spec_csv('C:/hsb2.csv')
```

## Specify Column Types 

<hr>

```{r import10, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Specify Column Types'}
read_csv('C:/hsb2.csv', col_types = list(col_integer(), col_factor(levels = c(0, 1)), 
  col_factor(levels = c(1, 2, 3, 4)), col_factor(levels = c(1, 2, 3)), 
  col_factor(levels = c(1, 2)), col_factor(levels = c(1, 2, 3)),
  col_integer(), col_integer(), col_integer(), col_integer(), col_integer())            
)
```

## Read Specific Columns 

<hr>

```{r import11, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Read Specific Columns'}
read_csv('C:/hsb2.csv', col_types = cols_only(id = col_integer(),
  prog = col_factor(levels = c(1, 2, 3)), read = col_integer())
)
```

## Base R

<hr>

```{r import1, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Base R'}
read.csv('C:/hsb2.csv', header = TRUE)
```
