---
title: "How to work with dates in R?"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(lubridate)
library(dplyr)
library(magrittr)
knitr::opts_chunk$set(echo = FALSE)
transact <- readr::read_csv('https://raw.githubusercontent.com/rsquaredacademy/datasets/master/transact.csv')
```

## Introduction

<hr>

 In this module, we will learn to work with date/time data in R using [lubridate]( https://CRAN.R-project.org/package=lubridate), an R package that makes it easy to work with dates and time. Let us begin by installing and loading the lubridate pacakge.

## Quick Tour

### Origin, Current Date/Time

<hr>

```{r origin, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Orign'}
# origin
lubridate::origin

# current time
now()

# current date and time
today()

# AM or PM
am(now())  
pm(now())
```

## Data

### Data

<hr>

```{r show, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Data Overview'}
transact
```

### Data Dictionary

<hr>

The data set has 3 columns. All the dates are in the format (yyyy-mm-dd).

- Invoice: invoice date 
- Due: due date
- Payment: payment date

## Case Study

<hr>

We will use the functions in the lubridate package to answer a few 
questions we have about the transact data.

- extract date, month and year from Due
- compute the number of days to settle invoice
- compute days over due
- check if due year is a leap year
- check when due day in february is 29, whether it is a leap year
- how many invoices were settled within due date
- how many invoices are due in each quarter
- what is the average duration between invoice date and payment date


## Day, Month & Year

### Introduction

<hr>

```{r lubb1, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Extract - Part 1'}
this_day <- as_date('2017-03-23')

# extract day
day(this_day)

# extract month
month(this_day)

# extract year
year(this_day)
```

## Day, Month & Year - Practice 1

<hr>

```{r lub2, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Extract - Part 1'}
transact %>%
  mutate(
    due_day = day(Due),
    due_month = month(Due),
    due_year = year(Due)
  )
```

## Date Difference

```{r lubb3, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Compute - Part 1'}
course_start <- as_date('2017-04-12')
course_end <- as_date('2017-04-21')
course_duration <- course_end - course_start
course_duration
```


## Date Difference - Practice 1

```{r lub3, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Compute - Part 1'}
transact %>%
  mutate(
    days_to_pay = Payment - Invoice
  )
```

## Date Difference - Practice 2

```{r lub4, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Compute - Part 2'}
transact %>%
  mutate(
    delay = Payment - Due
  )
```

