---
title: "Title & Axis Labels"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)
```

## Agenda

<hr>

- Learn to add
    - title
    - subtitle
    - axis Labels

- learn to modify
    - axis range


## Introduction


## Syntax

<hr>

|Feature|Argument|Value|Example|
|:-------|:--------|:-----|:-------|
|Title  |main    |string|"Scatter Plot"|
|Subtitle  |sub    |string|"Displacement vs Miles Per Gallon"|
|X Axis Label  |xlab    |string|"Displacement"|
|Y Axis Label  |ylab    |string|"Miles Per Gallon"|


## Title

<hr>

```{r title, fig.align='center',fig.height=5,fig.width=5, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Title'}
plot(mtcars$disp, mtcars$mpg, 
     main = 'Displacement vs Miles Per Gallon')
```

## Subtitle

<hr>

```{r subtitle, fig.align='center',fig.height=5,fig.width=5, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Subtitle'}
plot(mtcars$disp, mtcars$mpg, 
     main = 'Displacement vs Miles Per Gallon',
     sub = 'Mileage is inversely related to Displacement')
```

## Axis Labels

<hr>

```{r axis, fig.align='center',fig.height=5,fig.width=5, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Axis Labels'}
plot(mtcars$disp, mtcars$mpg, 
     main = 'Displacement vs Miles Per Gallon',
     sub = 'Mileage is inversely related to Displacement',
     xlab = 'Displacement', ylab = 'Miles Per Gallon')
```

## title()

### Introduction

<hr>

```{r title1, fig.align='center',fig.height=5,fig.width=5, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Title, Axis & Labels'}
plot(mtcars$disp, mtcars$mpg) 

title(main = 'Displacement vs Miles Per Gallon',
      sub = 'Mileage is inversely related to Displacement',
      xlab = 'Displacement', ylab = 'Miles Per Gallon')
```

### Annotate

<hr>

```{r title2, fig.align='center',fig.height=5,fig.width=5, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Annotate'}
plot(mtcars$disp, mtcars$mpg, ann = FALSE) 

title(main = 'Displacement vs Miles Per Gallon',
      sub = 'Mileage is inversely related to Displacement',
      xlab = 'Displacement', ylab = 'Miles Per Gallon')
```

## Axis Range

<hr>

```{r axisrange, fig.align='center',fig.height=5,fig.width=5, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Axis Range'}
plot(mtcars$disp, mtcars$mpg, 
     xlim = c(0, 600), ylim = c(0, 50))
```
